### 2022-02-04 paper/main.tex
add paper folder

% CVPR 2022 Paper Template
% based on the CVPR template provided by Ming-Ming Cheng (https://github.com/MCG-NKU/CVPR_Template)
% modified and extended by Stefan Roth (stefan.roth@NOSPAMtu-darmstadt.de)

\documentclass[10pt,twocolumn,letterpaper]{article}

%%%%%%%%% PAPER TYPE  - PLEASE UPDATE FOR FINAL VERSION
%\usepackage[review]{cvpr}      % To produce the REVIEW version
\usepackage{cvpr}              % To produce the CAMERA-READY version
%\usepackage[pagenumbers]{cvpr} % To force page numbers, e.g. for an arXiv version

% Include other packages here, before hyperref.
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{booktabs}

% It is strongly recommended to use hyperref, especially for the review version.
% hyperref with option pagebackref eases the reviewers' job.
% Please disable hyperref *only* if you encounter grave issues, e.g. with the
% file validation for the camera-ready version.
%
% If you comment hyperref and then uncomment it, you should delete
% ReviewTempalte.aux before re-running LaTeX.
% (Or just hit 'q' on the first LaTeX run, let it finish, and you
%  should be clear).
\usepackage[pagebackref,breaklinks,colorlinks]{hyperref}

% Support for easy cross-referencing
\usepackage[capitalize]{cleveref}
\crefname{section}{Sec.}{Secs.}
\Crefname{section}{Section}{Sections}
\Crefname{table}{Table}{Tables}
\crefname{table}{Tab.}{Tabs.}

%%%%%%%%% PAPER ID  - PLEASE UPDATE
\def\cvprPaperID{*****} % *** Enter the CVPR Paper ID here
\def\confName{CVPR}
\def\confYear{2022}

\begin{document}

%%%%%%%%% TITLE - PLEASE UPDATE
\title{Open-Set Domain Adaptation through Self-Supervision}

\author{Andrea Protopapa, Matteo Quarta, Giuseppe Ruggeri, Alessandro Versace\\
Politecnico di Torino\\
Italy\\
{\tt\small \{s286302,s292477,s292459,s292477\}@studenti.polito.it}
% For a paper whose authors are all at the same institution,
% omit the following lines up until the closing ``}''.
% Additional authors and addresses can be added with ``\and'',
% just like the second author.
% To save space, use either the email address or home page, not both
}
\maketitle

%%%%%%%%% ABSTRACT
\begin{abstract}

\end{abstract}

%%%%%%%%% BODY TEXT
\section{Introduction}
\label{sec:intro}

Start write here

%-------------------------------------------------------------------------
\subsection{Notes}
%---------- LANGUAGE ----------
All manuscripts must be in English.
%---------- PAPER LENGTH ----------
Papers, excluding the references section, must be no longer than eight pages in length.
The references section will not be included in the page count, and there is no limit on the length of the references section.
%---------- MATH ----------
Please number all of your sections and displayed equations as in these examples:
\begin{equation}
  E = m\cdot c^2
  \label{eq:important}
\end{equation}
and
\begin{equation}
  v = a\cdot t.
  \label{eq:also-important}
\end{equation}
All authors will benefit from reading Mermin's description of how to write mathematics:
\url{http://www.pamitc.org/documents/mermin.pdf}.
%---------- BLIND VIEW ----------
Blind review means that you do not use the words ``my'' or ``our'' when citing previous work.

Saying ``this builds on the work of Lucy Smith [1]'' does not say that you are Lucy Smith;
it says that you are building on her work.
If you are Smith and Jones, do not say ``as we show in [7]'', say ``as Smith and Jones show in [7]'' and at the end of the paper, include reference 7 as you would any other cited work.

An example of a bad paper just asking to be rejected:
\begin{quote}
\begin{center}
    An analysis of the frobnicatable foo filter.
\end{center}

   In this paper we present a performance analysis of our previous paper [1], and show it to be inferior to all previously known methods.
   Why the previous paper was accepted without this analysis is beyond me.

   [1] Removed for blind review
\end{quote}

An example of an acceptable paper:
\begin{quote}
\begin{center}
     An analysis of the frobnicatable foo filter.
\end{center}

   In this paper we present a performance analysis of the  paper of Smith \etal [1], and show it to be inferior to all previously known methods.
   Why the previous paper was accepted without this analysis is beyond me.

   [1] Smith, L and Jones, C. ``The frobnicatable foo filter, a fundamental contribution to human knowledge''. Nature 381(12), 1-213.
\end{quote}

Finally, you may feel you need to tell the reader that more details can be found elsewhere, and refer them to a technical report.
For conference submissions, the paper must stand on its own, and not {\em require} the reviewer to go to a tech report for further details.
Thus, you may say in the body of the paper ``further details may be found in~\cite{Authors14b}''.
Then submit the tech report as supplemental material.
Again, you may not assume the reviewers will read this material.
%---------- CAPTION EXAMPLE ----------
\begin{figure}[t]
  \centering
  \fbox{\rule{0pt}{2in} \rule{0.9\linewidth}{0pt}}
   %\includegraphics[width=0.8\linewidth]{egfigure.eps}

   \caption{Example of caption.
   It is set in Roman so that mathematics (always set in Roman: $B \sin A = A \sin B$) may be included without an ugly clash.}
   \label{fig:onecol}
\end{figure}
%---------- MISCELLANEOUS: E.G., ET AL. ----------
The space after \eg, meaning ``for example'', should not be a sentence-ending space.
So \eg is correct, {\em e.g.} is not.
The provided \verb'\eg' macro takes care of this.

When citing a multi-author paper, you may save space by using ``et alia'', shortened to ``\etal'' (not ``{\em et.\ al.}'' as ``{\em et}'' is a complete word).
If you use the \verb'\etal' macro provided, then you need not worry about double periods when used at the end of a sentence as in Alpher \etal.
However, use it only when there are three or more authors.
%---------- SUB-FIGURES EXAMPLE ----------
\begin{figure*}
  \centering
  \begin{subfigure}{0.68\linewidth}
    \fbox{\rule{0pt}{2in} \rule{.9\linewidth}{0pt}}
    \caption{An example of a subfigure.}
    \label{fig:short-a}
  \end{subfigure}
  \hfill
  \begin{subfigure}{0.28\linewidth}
    \fbox{\rule{0pt}{2in} \rule{.9\linewidth}{0pt}}
    \caption{Another example of a subfigure.}
    \label{fig:short-b}
  \end{subfigure}
  \caption{Example of a short caption, which should be centered.}
  \label{fig:short}
\end{figure*}
%---------- FORMATTING ----------
All text must be in a two-column format.
%---------- FOOTNOTES ----------
Please use footnotes\footnote{This is what a footnote looks like.
It often distracts the reader from the main flow of the argument.} sparingly.
Indeed, try to avoid footnotes altogether and include necessary peripheral observations in the text (within parentheses, if you prefer, as in this sentence).
If you wish to use a footnote, place it at the bottom of the column on the page on which it is referenced.
Use Times 8-point type, single-spaced.
%---------- CROSS-REFERENCES ----------
For the benefit of author(s) and readers, please use the
{\small\begin{verbatim}
  \cref{...}
\end{verbatim}}  command for cross-referencing to figures, tables, equations, or sections.
This will automatically insert the appropriate label alongside the cross-reference as in this example:
\begin{quotation}
  To see how our method outperforms previous work, please see \cref{fig:onecol} and \cref{tab:example}.
  It is also possible to refer to multiple targets as once, \eg~to \cref{fig:onecol,fig:short-a}.
  You may also return to \cref{sec:formatting} or look at \cref{eq:also-important}.
\end{quotation}
If you do not wish to abbreviate the label, for example at the beginning of the sentence, you can use the
{\small\begin{verbatim}
  \Cref{...}
\end{verbatim}}
command. Here is an example:
\begin{quotation}
  \Cref{fig:onecol} is also quite important.
\end{quotation}
%---------- CAPTION REFERENCES ----------
% Update the cvpr.cls to do the following automatically.
% For this citation style, keep multiple citations in numerical (not
% chronological) order, so prefer \cite{Alpher03,Alpher02,Authors14} to
% \cite{Alpher02,Alpher03,Authors14}.
List and number all bibliographical references at the end of your paper.
When referenced in the text, enclose the citation number in square brackets, for
example~\cite{Authors14}.
Where appropriate, include page numbers and the name(s) of editors of referenced books.
When you cite multiple papers at once, please make sure that you cite them in numerical order like this \cite{Alpher02,Alpher03,Alpher05,Authors14b,Authors14}.
If you use the template as advised, this will be taken care of automatically.
%---------- TABLE EXAMPLE ----------
\begin{table}
  \centering
  \begin{tabular}{@{}lc@{}}
    \toprule
    Method & Frobnability \\
    \midrule
    Theirs & Frumpy \\
    Yours & Frobbly \\
    Ours & Makes one's heart Frob\\
    \bottomrule
  \end{tabular}
  \caption{Results.   Ours is better.}
  \label{tab:example}
\end{table}
%---------- CENTERING GRAPHICS ----------
All graphics should be centered.
In \LaTeX, avoid using the \texttt{center} environment for this purpose, as this adds potentially unwanted whitespace.
Instead use
{\small\begin{verbatim}
  \centering
\end{verbatim}}
at the beginning of your figure.

When placing figures in \LaTeX, it's almost always best to use \verb+\includegraphics+, and to specify the figure width as a multiple of the line width as in the example below
{\small\begin{verbatim}
   \usepackage{graphicx} ...
   \includegraphics[width=0.8\linewidth]
                   {myfile.pdf}
\end{verbatim}
}
%---------- COLOR ----------
If you use color in your plots, please keep in mind that a significant subset of reviewers and readers may have a color vision deficiency; red-green blindness is the most frequent kind.
Hence avoid relying only on color as the discriminative feature in plots (such as red \vs green lines), but add a second discriminative feature to ease disambiguation.

%------------------------------------------------------------------------
\section{Related Work}
\label{sec:relatedwork}

%------------------------------------------------------------------------
\section{Method - Write name of proposal approach}
\label{sec:method}
%------------------------------------------------------------------------
\subsection{Subsection 1}
%------------------------------------------------------------------------
\subsection{Subsection 2}

%------------------------------------------------------------------------
\section{Experiments}
\label{sec:experiments}
%------------------------------------------------------------------------
\subsection{Subsection 1 - Setup}
%------------------------------------------------------------------------
\subsection{Subsection 2 - Implementation Details}
%------------------------------------------------------------------------
\subsection{Subsection 3 - Results}

%------------------------------------------------------------------------
\section{Conclusions (and Future Work)}
\label{sec:conclusions}

%%%%%%%%% APPENDIX - TAKEN FROM ANOTHER TEMPLATE!!
\appendix
\section{Appendices}
\label{sec:appendix}
Appendices are material that can be read, and include lemmas, formulas, proofs, and tables that are not critical to the reading and understanding of the paper. 
Appendices should be \textbf{uploaded as supplementary material} when submitting the paper for review.
Upon acceptance, the appendices come after the references, as shown here.

\paragraph{\LaTeX-specific details:}
Use {\small\verb|\appendix|} before any appendix section to switch the section numbering over to letters.

\section{Supplemental Material}
\label{sec:supplemental}
Submissions may include non-readable supplementary material used in the work and described in the paper.
Any accompanying software and/or data should include licenses and documentation of research review as appropriate.
Supplementary material may report preprocessing decisions, model parameters, and other details necessary for the replication of the experiments reported in the paper.
Seemingly small preprocessing decisions can sometimes make a large difference in performance, so it is crucial to record such decisions to precisely characterize state-of-the-art methods.

Nonetheless, supplementary material should be supplementary (rather than central) to the paper.
\textbf{Submissions that misuse the supplementary material may be rejected without review.}
Supplementary material may include explanations or details of proofs or derivations that do not fit into the paper, lists of
features or feature templates, sample inputs and outputs for a system, pseudo-code or source code, and data.
(Source code and data should be separate uploads, rather than part of the paper).

The paper should not rely on the supplementary material: while the paper may refer to and cite the supplementary material and the supplementary material will be available to the reviewers, they will not be asked to review the supplementary material.

%%%%%%%%% REFERENCES
{\small
\bibliographystyle{ieee_fullname}
\bibliography{egbib}
}

\end{document}

### 2022-02-04 paper/main.tex
aux files added to gitignore and removed

@@
 
-\author{Andrea Protopapa, Matteo Quarta, Giuseppe Ruggeri, Alessandro Versace\\
+\author{Protopapa Andrea, Quarta Matteo, Ruggeri Giuseppe, Versace Alessandro\\
 Politecnico di Torino\\

### 2022-02-04 ROS_AMLProject/eval_target.py
logger and save plots

@@ -74,22 +74,22 @@ def target_separation(args, E, C, R, target_loader_eval, device, rand):
 
     # Compute AUC-ROC value
     auc = roc_auc_score(ground_truths, normality_scores)
-    print("\n")
-    print(f"Computed ROC AUC: {auc:.4f}")
-    print()
+    args.logger.info("\n")
+    args.logger.info(f"Computed ROC AUC: {auc:.4f}")
+    args.logger.info()
 
     # Perform the separation using the given threshold
     mask_sep_known = normality_scores >= args.threshold
     mask_sep_unknw = normality_scores < args.threshold
 
-    print(f"Separation performed using threshold: {args.threshold:.3f}")
-    print(f"Target samples identified as known: {mask_sep_known.sum()} - Actual known samples: {mask_known.sum()}")
-    print(f"Target samples identified as unknown: {mask_sep_unknw.sum()} - Actual unknown samples: {mask_unknw.sum()}")
+    args.logger.info(f"Separation performed using threshold: {args.threshold:.3f}")
+    args.logger.info(f"Target samples identified as known: {mask_sep_known.sum()} - Actual known samples: {mask_known.sum()}")
+    args.logger.info(f"Target samples identified as unknown: {mask_sep_unknw.sum()} - Actual unknown samples: {mask_unknw.sum()}")
 
     known_accuracy = (mask_sep_known == mask_known).sum() / mask_sep_known.shape[0]
 
-    print(f"Separation accuracy: {known_accuracy*100:.2f} %")
-    print()
+    args.logger.info(f"Separation accuracy: {known_accuracy*100:.2f} %")
+    args.logger.info("")
 
     # We now must build and save two datasets
     # New Source Dataset, with Source + Target Unknown Samples
@@ -119,8 +119,8 @@ def target_separation(args, E, C, R, target_loader_eval, device, rand):
     source_and_target_unknown_file.close()
     target_known_file.close()
 
-    print(f"New source file containing known source and unknown target (according to the separation) written in {stu_fname}")
-    print(f"New target file containing known target (according to the separation) written in {tk_fname}")
+    args.logger.info(f"New source file containing known source and unknown target (according to the separation) written in {stu_fname}")
+    args.logger.info(f"New target file containing known target (according to the separation) written in {tk_fname}")
 
     return auc, known_accuracy
 
[…]

### 2022-02-04 ROS_AMLProject/main.py

@@ -1,6 +1,4 @@
 import argparse
-import copy
-
 import torch
 import data_helper
 from resnet import resnet18_feat_extractor, Classifier, RotationDiscriminator
@@ -9,16 +7,25 @@ from step1_KnownUnknownSep import step1
 from eval_target import target_separation, target_evaluation
 from step2_SourceTargetAdapt import step2
 from random import randint
-import pickle
 import os
 from step1_KnownUnknownSep import plot_step1_accuracy_loss
 from step2_SourceTargetAdapt import plot_step2_accuracy_loss, plot_eval_performance
+import logging
+import sys
 
 SCRIPT_PATH = os.path.dirname(__file__)
 MODEL_PATH = os.path.join(SCRIPT_PATH, "models")
+LOG_PATH = os.path.join(SCRIPT_PATH, "logs")
+PLOT_PATH = os.path.join(SCRIPT_PATH, "plots")
 
 if not os.path.exists(MODEL_PATH):
     os.mkdir(MODEL_PATH)
+
+if not os.path.exists(LOG_PATH):
+    os.mkdir(LOG_PATH)
+
+if not os.path.exists(PLOT_PATH):
+    os.mkdir(PLOT_PATH)
 
 
 def get_args():
@@ -161,14 +168,38 @@ class Trainer:
         data_helper.visualize_img(self.target_loader_eval)
         # ----------------- #
 
+        # LOGGER
+        logger = logging.getLogger()
+        conf_name = self.get_config_file_name()
+        conf_name = conf_name[:-4]
+        conf_name += ".log"
+        f_path = os.path.join(LOG_PATH, conf_name)
+        filehand = logging.FileHandler(f_path, mode='a')
+        filehand.setLevel(logging.INFO)
+        fmt = logging.Formatter('%(message)s')
+        filehand.setFormatter(fmt)
+        stdout_handler = logging.StreamHandler(sys.stdout)
+        stdout_handler.setFormatter(fmt)
+        stdout_handler.setLevel(logging.INFO)
+        logger.addHandler(stdout_handler)
+        logger.addHandler(filehand)
+        logger.setLevel(logging.DEBUG)
+        args.logger = logger
+        self.logger = logger
+
+        # PLOT
+        conf_name = self.get_config_file_name()
+        conf_name = conf_name[:-4]
+        plot_path = os.path.join(PLOT_PATH, conf_name)
+        args.plot_path = plot_path
 
     def trainer_step1(self):
-        print("Step One -- Training")
[…]

### 2022-02-04 ROS_AMLProject/step1_KnownUnknownSep.py

@@ -111,15 +111,15 @@ def step1(args, E, C, R, source_loader, device, optimizer, scheduler, optimizer_
     history['R_acc'] = []
 
     for epoch in range(args.epochs_step1):
-        print(f'Epoch {epoch+1}/{args.epochs_step1}')
+        args.logger.info(f'Epoch {epoch+1}/{args.epochs_step1}')
         tot_loss, C_loss, R_loss, CL_loss, C_accuracy, R_accuracy = _do_epoch(args, E, C, R, source_loader, device, optimizer, optimizer_CL=optimizer_CL, criterion_CL=criterion_CL)
-        print(f"\tTotal Loss: {tot_loss:.4f}")
-        print(f"\tClass Loss: {C_loss:.4f}")
-        print(f"\tRot Loss: {R_loss:.4f}")
+        args.logger.info(f"\tTotal Loss: {tot_loss:.4f}")
+        args.logger.info(f"\tClass Loss: {C_loss:.4f}")
+        args.logger.info(f"\tRot Loss: {R_loss:.4f}")
         if args.center_loss:
-            print(f"\tCenterLoss: {CL_loss:.4f}")
-        print(f"\tClass Accuracy: {C_accuracy*100:.2f} %")
-        print(f"\tRot Accuracy: {R_accuracy*100:.2f} %")
+            args.logger.info(f"\tCenterLoss: {CL_loss:.4f}")
+        args.logger.info(f"\tClass Accuracy: {C_accuracy*100:.2f} %")
+        args.logger.info(f"\tRot Accuracy: {R_accuracy*100:.2f} %")
 
         history['tot_loss'].append(tot_loss)
         history['C_loss'].append(C_loss)
@@ -150,6 +150,8 @@ def plot_step1_accuracy_loss(args, history):
     plt.plot(epochs, C_accuracy, 'b', label='Object classifier accuracy')
     plt.plot(epochs, R_accuracy, 'r', label='Rotation classifier accuracy')
     plt.legend()
+    fig_path = args.plot_path + "_s1_acc"
+    plt.savefig(fig_path)
 
     # Loss plot
     plt.figure()
@@ -161,6 +163,8 @@ def plot_step1_accuracy_loss(args, history):
         plt.plot(epochs, CL_loss, 'g', label='Center Loss')
 
     plt.legend()
+    fig_path = args.plot_path + "_s1_loss"
+    plt.savefig(fig_path)
 
     plt.show()
 

### 2022-02-04 ROS_AMLProject/step2_SourceTargetAdapt.py

@@ -149,13 +149,13 @@ def step2(args, E, C, R, source_loader, target_loader_train, target_loader_eval,
 
         scheduler.step()
 
-        print("Train Stats:")
-        print(f"\tTotal Loss: {tot_loss:.4f}")
-        print(f"\tClass Loss: {C_loss:.4f}")
-        print(f"\tRot Loss: {R_loss:.4f}")
-        print(f"\tClass Accuracy: {C_accuracy * 100:.2f} %")
-        print(f"\tRot Accuracy: {R_accuracy * 100:.2f} %")
-        print()
+        args.logger.info("Train Stats:")
+        args.logger.info(f"\tTotal Loss: {tot_loss:.4f}")
+        args.logger.info(f"\tClass Loss: {C_loss:.4f}")
+        args.logger.info(f"\tRot Loss: {R_loss:.4f}")
+        args.logger.info(f"\tClass Accuracy: {C_accuracy * 100:.2f} %")
+        args.logger.info(f"\tRot Accuracy: {R_accuracy * 100:.2f} %")
+        args.logger.info("")
 
         # EVAL EPOCH
         HOS, OS, UNK, C_loss = target_evaluation(args, E, C, target_loader_eval, device)
@@ -164,12 +164,12 @@ def step2(args, E, C, R, source_loader, target_loader_train, target_loader_eval,
         history['eval_UNK'].append(UNK)
         history['eval_C_loss'].append(C_loss)
 
-        print()
-        print("Target Evaluation Stats")
-        print(f"\tClass Loss: {C_loss:.2f}")
-        print(f"\tOS : {OS * 100:.2f} %")
-        print(f"\tUNK: {UNK * 100:.2f} %")
-        print(f"\tHOS: {HOS * 100:.2f} %")
+        args.logger.info("")
+        args.logger.info("Target Evaluation Stats")
+        args.logger.info(f"\tClass Loss: {C_loss:.2f}")
+        args.logger.info(f"\tOS : {OS * 100:.2f} %")
+        args.logger.info(f"\tUNK: {UNK * 100:.2f} %")
+        args.logger.info(f"\tHOS: {HOS * 100:.2f} %")
 
     return history
 
@@ -188,6 +188,8 @@ def plot_step2_accuracy_loss(args, history):
     plt.plot(epochs, C_accuracy, 'b', label='Object classifier accuracy')
     plt.plot(epochs, R_accuracy, 'r', label='Rotation classifier accuracy')
[…]

### 2022-02-04 paper/main.tex
Updated bibliography

@@
 Italy\\
-{\tt\small \{s286302,s292477,s292459,s292477\}@studenti.polito.it}
+{\tt\small \{s286302,s292477,s292459,s292477\}@studenti.polito.it <- Riordinare}
 % For a paper whose authors are all at the same institution,
@@
 \label{sec:supplemental}
-Submissions may include non-readable supplementary material used in the work and described in the paper.
+Submissions may include\cite{GeoTran}\cite{CenterLoss}\cite{BucciROS}\cite{OldROS}\cite{CarlucciJigsaw} non-readable supplementary material used in the work and described in the paper.
 Any accompanying software and/or data should include licenses and documentation of research review as appropriate.

### 2022-02-04 ROS_AMLProject/eval_target.py
fix logger

@@ -76,7 +76,7 @@ def target_separation(args, E, C, R, target_loader_eval, device, rand):
     auc = roc_auc_score(ground_truths, normality_scores)
     args.logger.info("\n")
     args.logger.info(f"Computed ROC AUC: {auc:.4f}")
-    args.logger.info()
+    args.logger.info("")
 
     # Perform the separation using the given threshold
     mask_sep_known = normality_scores >= args.threshold
@@ -168,7 +168,7 @@ def target_evaluation(args, E, C, target_loader_eval, device):
             tot_predicted_known += (C_preds < 45).sum().item()
             tot_predicted_unknown += (C_preds > 44).sum().item()
 
-    args.logger.info()
+    args.logger.info("")
     args.logger.info(f"Tot predicted known (in general): {tot_predicted_known}")
     args.logger.info(f"Tot predicted unknown (in general): {tot_predicted_unknown}")
     args.logger.info(f"Total real known samples: {tot_known}")

### 2022-02-04 ROS_AMLProject/main.py
fix logger

@@ -215,7 +215,7 @@ class Trainer:
         self.logger.info("Target Known/Unknown Separation")
         self.auc, self.separation_accuracy = target_separation(self.args, self.E1, self.C1, self.R1, self.target_loader_eval, self.device, self.rand)
 
-        self.logger.info("Adding known source samples to the newly generated file... ", end="")
+        self.logger.info("Adding known source samples to the newly generated file... ")
         filepath = f'new_txt_list/{self.args.source}_known_{str(self.rand)}.txt'
         with open(filepath, "a") as f:
             pairs = zip(self.source_loader.dataset.names, self.source_loader.dataset.labels)

### 2022-02-04 ROS_AMLProject/main.py
fix

@@ -173,6 +173,7 @@ class Trainer:
         conf_name = self.get_config_file_name()
         conf_name = conf_name[:-4]
         conf_name += ".log"
+        print(conf_name)
         f_path = os.path.join(LOG_PATH, conf_name)
         filehand = logging.FileHandler(f_path, mode='a')
         filehand.setLevel(logging.INFO)
@@ -190,6 +191,7 @@ class Trainer:
         # PLOT
         conf_name = self.get_config_file_name()
         conf_name = conf_name[:-4]
+        print(conf_name)
         plot_path = os.path.join(PLOT_PATH, conf_name)
         args.plot_path = plot_path
 

### 2022-02-04 ROS_AMLProject/step1_KnownUnknownSep.py
added extension for plots

@@ -150,7 +150,7 @@ def plot_step1_accuracy_loss(args, history):
     plt.plot(epochs, C_accuracy, 'b', label='Object classifier accuracy')
     plt.plot(epochs, R_accuracy, 'r', label='Rotation classifier accuracy')
     plt.legend()
-    fig_path = args.plot_path + "_s1_acc"
+    fig_path = args.plot_path + "_s1_acc.png"
     plt.savefig(fig_path)
 
     # Loss plot
@@ -163,7 +163,7 @@ def plot_step1_accuracy_loss(args, history):
         plt.plot(epochs, CL_loss, 'g', label='Center Loss')
 
     plt.legend()
-    fig_path = args.plot_path + "_s1_loss"
+    fig_path = args.plot_path + "_s1_loss.png"
     plt.savefig(fig_path)
 
     plt.show()

### 2022-02-04 ROS_AMLProject/step2_SourceTargetAdapt.py

@@ -188,7 +188,7 @@ def plot_step2_accuracy_loss(args, history):
     plt.plot(epochs, C_accuracy, 'b', label='Object classifier accuracy')
     plt.plot(epochs, R_accuracy, 'r', label='Rotation classifier accuracy')
     plt.legend()
-    fig_path = args.plot_path + "_s2_acc"
+    fig_path = args.plot_path + "_s2_acc.png"
     plt.savefig(fig_path)
 
     # Loss plot
@@ -198,7 +198,7 @@ def plot_step2_accuracy_loss(args, history):
     plt.plot(epochs, C_loss, 'b', label='Object classifier loss')
     plt.plot(epochs, R_loss, 'r', label='Rotation classifier loss')
     plt.legend()
-    fig_path = args.plot_path + "_s2_loss"
+    fig_path = args.plot_path + "_s2_loss.png"
     plt.savefig(fig_path)
 
     plt.show()
@@ -218,7 +218,7 @@ def plot_eval_performance(args, history):
     plt.plot(epochs, OS, 'r', label='OS')
     plt.plot(epochs, UNK, 'm', label='UNK')
     plt.legend()
-    fig_path = args.plot_path + "_eval_hos"
+    fig_path = args.plot_path + "_eval_hos.png"
     plt.savefig(fig_path)
 
     # Loss plot
@@ -226,7 +226,7 @@ def plot_eval_performance(args, history):
     plt.title(f'Evaluation - Object classifier loss (MH: {args.multihead} - CL: {args.center_loss})')
     plt.plot(epochs, C_loss, 'b', label='Object classifier loss')
     plt.legend()
-    fig_path = args.plot_path + "_eval_loss"
+    fig_path = args.plot_path + "_eval_loss.png"
     plt.savefig(fig_path)
 
     plt.show()

### 2022-02-04 ROS_AMLProject/main.py
unuseful prints

@@ -173,7 +173,6 @@ class Trainer:
         conf_name = self.get_config_file_name()
         conf_name = conf_name[:-4]
         conf_name += ".log"
-        print(conf_name)
         f_path = os.path.join(LOG_PATH, conf_name)
         filehand = logging.FileHandler(f_path, mode='a')
         filehand.setLevel(logging.INFO)
@@ -191,7 +190,6 @@ class Trainer:
         # PLOT
         conf_name = self.get_config_file_name()
         conf_name = conf_name[:-4]
-        print(conf_name)
         plot_path = os.path.join(PLOT_PATH, conf_name)
         args.plot_path = plot_path
 

### 2022-02-04 ROS_AMLProject/step2_SourceTargetAdapt.py
fix log

@@ -132,7 +132,7 @@ def step2(args, E, C, R, source_loader, target_loader_train, target_loader_eval,
     history['eval_C_loss'] = []
 
     for epoch in range(args.epochs_step2):
-        print(f"Epoch {epoch+1}/{args.epochs_step2}")
+        args.logger.info(f"Epoch {epoch+1}/{args.epochs_step2}")
 
         # TRAINING EPOCH
         # Set the training mode

### 2022-02-04 ROS_AMLProject/main.py
improved logging

@@ -193,6 +193,20 @@ class Trainer:
         plot_path = os.path.join(PLOT_PATH, conf_name)
         args.plot_path = plot_path
 
+        self.logger.info(f"CONFIGURATION:")
+        self.logger.info(f"Source: {args.source}")
+        self.logger.info(f"Target: {args.target}")
+        self.logger.info(f"Multihead: {args.multihead}")
+        self.logger.info(f"Centerloss: {args.center_loss}")
+        self.logger.info(f"Alfa1: {args.weight_RotTask_step1}")
+        self.logger.info(f"Weight CL: {args.weight_CL}")
+        self.logger.info(f"Threshold: {args.threshold}")
+        self.logger.info(f"Alfa2: {args.weight_RotTask_step2}")
+        self.logger.info(f"Batch size: {args.batch_size}")
+        self.logger.info(f"Learning rate: {args.learning_rate}")
+        self.logger.info(f"Learning rate CL: {args.learning_rate_CL}")
+        self.logger.info("")
+
     def trainer_step1(self):
         self.logger.info("Step One -- Training")
 

### 2022-02-05 ROS_AMLProject/eval_target.py
added best HOS, TPR, TNR

@@ -82,13 +82,35 @@ def target_separation(args, E, C, R, target_loader_eval, device, rand):
     mask_sep_known = normality_scores >= args.threshold
     mask_sep_unknw = normality_scores < args.threshold
 
+    assignments = np.zeros(normality_scores.shape, dtype=np.int)
+    assignments[mask_sep_known] = 1
+    assignments[mask_sep_unknw] = 0
+
     args.logger.info(f"Separation performed using threshold: {args.threshold:.3f}")
     args.logger.info(f"Target samples identified as known: {mask_sep_known.sum()} - Actual known samples: {mask_known.sum()}")
     args.logger.info(f"Target samples identified as unknown: {mask_sep_unknw.sum()} - Actual unknown samples: {mask_unknw.sum()}")
 
-    known_accuracy = (mask_sep_known == mask_known).sum() / mask_sep_known.shape[0]
+    separation_accuracy = (assignments == ground_truths).sum() / ground_truths.shape[0]
+    correct_known = 0
+    tot_known = 0
+    correct_unknown = 0
+    tot_unknown = 0
+    for pred, actual in zip(assignments, ground_truths):
+        if actual == 1:
+            tot_known += 1
+            if pred == actual:
+                correct_known += 1
+        else:
+            tot_unknown += 1
+            if pred == actual:
+                correct_unknown += 1
 
-    args.logger.info(f"Separation accuracy: {known_accuracy*100:.2f} %")
+    known_accuracy = correct_known / tot_known
+    unknown_accuracy = correct_unknown / tot_unknown
+
+    args.logger.info(f"Separation accuracy: {separation_accuracy * 100:.2f} %")
+    args.logger.info(f"Known accuracy (TPR): {known_accuracy * 100:.2f} %")
+    args.logger.info(f"Unknown accuracy (TNR): {unknown_accuracy * 100:.2f} %")
     args.logger.info("")
 
     # We now must build and save two datasets
@@ -122,7 +144,7 @@ def target_separation(args, E, C, R, target_loader_eval, device, rand):
     args.logger.info(f"New source file containing known source and unknown target (according to the separation) written in {stu_fname}")
     args.logger.info(f"New target file containing known target (according to the separation) written in {tk_fname}")
 
-    return auc, known_accuracy
+    return auc, separation_accuracy
 
 def target_evaluation(args, E, C, target_loader_eval, device):
     # Final evaluation on the target using only C2

### 2022-02-05 ROS_AMLProject/main.py

@@ -277,6 +277,9 @@ class Trainer:
         self.history2['eval_UNK'].extend(hist2['eval_UNK'])
         self.history2['eval_C_loss'].extend(hist2['eval_C_loss'])
 
+        best_hos = max(hist2['eval_HOS'])
+        self.logger.info(f"Best HOS: {best_hos:.3f}")
+
     def trainer_target_evaluation(self):
         HOS, OS, UNK, C_loss = target_evaluation(self.args, self.E2, self.C2, self.target_loader_eval, self.device)
         self.logger.info("")

### 2022-02-05 ROS_AMLProject/step2_SourceTargetAdapt.py

@@ -167,7 +167,7 @@ def step2(args, E, C, R, source_loader, target_loader_train, target_loader_eval,
         args.logger.info("")
         args.logger.info("Target Evaluation Stats")
         args.logger.info(f"\tClass Loss: {C_loss:.2f}")
-        args.logger.info(f"\tOS : {OS * 100:.2f} %")
+        args.logger.info(f"\tOS*: {OS * 100:.2f} %")
         args.logger.info(f"\tUNK: {UNK * 100:.2f} %")
         args.logger.info(f"\tHOS: {HOS * 100:.2f} %")
 
@@ -213,9 +213,9 @@ def plot_eval_performance(args, history):
 
     # Accuracy plot
     plt.figure()
-    plt.title(f'Evaluation - HOS, OS, UNK over the target dataset (MH: {args.multihead} - CL: {args.center_loss})')
+    plt.title(f'Evaluation - HOS, OS*, UNK over the target dataset (MH: {args.multihead} - CL: {args.center_loss})')
     plt.plot(epochs, HOS, 'b', label='HOS')
-    plt.plot(epochs, OS, 'r', label='OS')
+    plt.plot(epochs, OS, 'r', label='OS*')
     plt.plot(epochs, UNK, 'm', label='UNK')
     plt.legend()
     fig_path = args.plot_path + "_eval_hos.png"

### 2022-02-06 ROS_AMLProject/main.py
best hos now is expressed as %

@@ -278,7 +278,7 @@ class Trainer:
         self.history2['eval_C_loss'].extend(hist2['eval_C_loss'])
 
         best_hos = max(hist2['eval_HOS'])
-        self.logger.info(f"Best HOS: {best_hos:.3f}")
+        self.logger.info(f"Best HOS: {best_hos*100:.4f} %")
 
     def trainer_target_evaluation(self):
         HOS, OS, UNK, C_loss = target_evaluation(self.args, self.E2, self.C2, self.target_loader_eval, self.device)

### 2022-02-06 ROS_AMLProject/eval_target.py
added roc

@@ -7,6 +7,8 @@ from tqdm import tqdm
 import numpy as np
 from torch import nn
 
+import matplotlib.pyplot as plt
+
 softmax = torch.nn.Softmax(dim=1)
 
 def target_separation(args, E, C, R, target_loader_eval, device, rand):
@@ -144,7 +146,61 @@ def target_separation(args, E, C, R, target_loader_eval, device, rand):
     args.logger.info(f"New source file containing known source and unknown target (according to the separation) written in {stu_fname}")
     args.logger.info(f"New target file containing known target (according to the separation) written in {tk_fname}")
 
+    draw_ROC(normality_scores, ground_truths)
+
     return auc, separation_accuracy
+
+def get_confusion_matrix(predicted_labels, true_labels, all_labels=None):
+    labels = all_labels
+    if all_labels is None:
+        labels = set(true_labels)
+        extended = set(predicted_labels)
+        labels = labels.union(extended)
+
+    label_to_index = {l: i for i, l in enumerate(labels)}
+    conf_matr = np.zeros((len(labels), len(labels)))
+    for p, t in zip(predicted_labels, true_labels):
+        p_i = label_to_index[p]
+        t_i = label_to_index[t]
+        conf_matr[p_i, t_i] = conf_matr[p_i, t_i] + 1
+
+    return conf_matr
+
+def bayes_binary_optimal_classifier(llr, threshold=None):
+    if (llr.ndim > 1):
+        llr = llr.flatten()
+    predictions = [1 if l >= threshold else 0 for l in llr]
+    return predictions
+
+def draw_ROC(llr, labels, color=None, recognizer_name=""):
+    if llr.ndim > 1:
+        llr = llr.flatten()
+
+    llr_sorted = np.sort(llr)
+    FPRs = []
+    TPRs = []
+    for t in llr_sorted:
+        predictions = bayes_binary_optimal_classifier(llr, threshold=t)
+        conf_matr = get_confusion_matrix(predictions, labels)
+        FNR = conf_matr[0, 1] / (conf_matr[0, 1] + conf_matr[1, 1])
+        TPR = 1 - FNR
+        FPR = conf_matr[1, 0] / (conf_matr[1, 0] + conf_matr[0, 0])
+        FPRs.append(FPR)
+        TPRs.append(TPR)
+    plt.figure()
+    plt.title("ROC")
+    plt.xlabel("FPR")
+    plt.ylabel("TPR")
[…]

### 2022-02-06 ROS_AMLProject/eval_target.py
added roc plot

@@ -146,7 +146,7 @@ def target_separation(args, E, C, R, target_loader_eval, device, rand):
     args.logger.info(f"New source file containing known source and unknown target (according to the separation) written in {stu_fname}")
     args.logger.info(f"New target file containing known target (according to the separation) written in {tk_fname}")
 
-    draw_ROC(normality_scores, ground_truths)
+    draw_ROC(args, normality_scores, ground_truths)
 
     return auc, separation_accuracy
 
@@ -172,7 +172,7 @@ def bayes_binary_optimal_classifier(llr, threshold=None):
     predictions = [1 if l >= threshold else 0 for l in llr]
     return predictions
 
-def draw_ROC(llr, labels, color=None, recognizer_name=""):
+def draw_ROC(args, llr, labels, color=None, recognizer_name=""):
     if llr.ndim > 1:
         llr = llr.flatten()
 
@@ -199,6 +199,8 @@ def draw_ROC(llr, labels, color=None, recognizer_name=""):
         plt.plot(FPRs, TPRs, label=f"{recognizer_name}")
 
     plt.legend(loc="lower right")
+    fig_path = args.plot_path + "_sep_roc.png"
+    plt.savefig(fig_path)
     plt.show()
 
 

### 2022-02-06 ROS_AMLProject/step2_SourceTargetAdapt.py
unk rebalance step2

@@ -7,13 +7,13 @@ import matplotlib.pyplot as plt
 
 def _do_epoch(args, E, C, R, source_loader, target_loader_train, optimizer, device):
 
-    # Double the learning rate for the unknown class
-    # w = [ 1.0 for _ in range(args.n_classes_known + 1) ]
-    # w[-1] = 2.0
-    # w = torch.tensor(w).to(device)
+    # Adjust the learning rate for the unknown class
+    w = [ 1.0 for _ in range(args.n_classes_known + 1) ]
+    w[-1] = 1/45
+    w = torch.tensor(w).to(device)
 
-    # C_criterion = nn.CrossEntropyLoss(weight=w)
-    C_criterion = nn.CrossEntropyLoss()
+    C_criterion = nn.CrossEntropyLoss(weight=w)
+    # C_criterion = nn.CrossEntropyLoss()
     R_criterion = nn.CrossEntropyLoss()
 
     C_correct_preds, R_correct_preds, C_tot_preds, R_tot_preds = 0, 0, 0, 0

### 2022-02-07 ROS_AMLProject/optimizer_helper.py
add: optimizer step

@@ -16,7 +16,7 @@ def get_optim_and_scheduler(E, C, R, epochs, lr, train_all):
         params = list(C.parameters()) + R_params
         optimizer = optim.SGD(params, weight_decay=.0005, momentum=.9, lr=lr)
 
-    step_size = int(epochs * 10)
+    step_size = int(epochs * 0.9)
     scheduler = optim.lr_scheduler.StepLR(optimizer, step_size=step_size)
 
     return optimizer, scheduler
@@ -24,7 +24,7 @@ def get_optim_and_scheduler(E, C, R, epochs, lr, train_all):
 def get_optim_scheduler_loss_center_loss(lr, epochs, device):
     criterion_center = CenterLoss(num_classes=4, feat_dim=256, use_gpu=True, device=device)
     optimizer_center = optim.SGD(criterion_center.parameters(), weight_decay=.0005, momentum=.9, lr=lr)
-    step_size = int(epochs * 10)
+    step_size = int(epochs * 0.9)
     scheduler = optim.lr_scheduler.StepLR(optimizer_center, step_size=step_size)
 
     return optimizer_center, scheduler, criterion_center

### 2022-02-07 ROS_AMLProject/main.py
Pairs label-count from source added

@@ -250,6 +250,15 @@ class Trainer:
 
             self.logger.info("Step 2 will start from the Feature Extractor (E1) and the Object Classifier (C1) from the step 1..")
 
+        # Compute avg samples_label
+        source_path_file = f"txt_list/{self.args.source}_known.txt"
+        self.source_loader = data_helper.get_train_dataloader(self.args, source_path_file)
+        label_nsample = dict()
+        pairs = zip(self.source_loader.dataset.names, self.source_loader.dataset.labels)
+        for (_, label) in pairs:
+            label_nsample[label] = label_nsample.get(label,0) + 1
+        print(f"Pairs label-count:\n{label_nsample}") #debug
+        
         # Build new dataloaders
         # New source (source + target unknown according to separation)
         source_path_file   = f"new_txt_list/{self.args.source}_known_{str(self.rand)}.txt"

### 2022-02-07 ROS_AMLProject/eval_target.py
weight den update

@@ -171,7 +171,7 @@ def target_separation(args, E, C, R, target_loader_eval, device, rand):
 
     draw_ROC(args, normality_scores, ground_truths)
 
-    return auc, separation_accuracy
+    return auc, separation_accuracy, mask_sep_unknw.sum()
 
 def get_confusion_matrix(predicted_labels, true_labels, all_labels=None):
     labels = all_labels

### 2022-02-07 ROS_AMLProject/main.py

@@ -119,6 +119,8 @@ class Trainer:
         # Separation performance
         self.auc = None
         self.separation_accuracy = None
+        self.n_unk_identified = None 
+        self.avg_source_for_label = None
 
         # Used for naming the known target dataset and the new source dataset after the separation
         self.rand = randint(0, 1e6)
@@ -227,7 +229,7 @@ class Trainer:
 
     def trainer_target_separation(self):
         self.logger.info("Target Known/Unknown Separation")
-        self.auc, self.separation_accuracy = target_separation(self.args, self.E1, self.C1, self.R1, self.target_loader_eval, self.device, self.rand)
+        self.auc, self.separation_accuracy, self.n_unk_identified = target_separation(self.args, self.E1, self.C1, self.R1, self.target_loader_eval, self.device, self.rand)
 
         self.logger.info("Adding known source samples to the newly generated file... ")
         filepath = f'new_txt_list/{self.args.source}_known_{str(self.rand)}.txt'
@@ -257,7 +259,13 @@ class Trainer:
         pairs = zip(self.source_loader.dataset.names, self.source_loader.dataset.labels)
         for (_, label) in pairs:
             label_nsample[label] = label_nsample.get(label,0) + 1
+        avg_source_for_label = sum(label_nsample.values())/len(label_nsample)
         print(f"Pairs label-count:\n{label_nsample}") #debug
+        print(f"Avg:{avg_source_for_label}") #debug
+        self.avg_source_for_label = avg_source_for_label
+        den_w = self.n_unk_identified/self.avg_source_for_label
+        print(f"N. unk identified: {self.n_unk_identified}")
+        print(f"Den weight: {den_w}\n")
         
         # Build new dataloaders
         # New source (source + target unknown according to separation)
@@ -274,7 +282,7 @@ class Trainer:
 
         self.logger.info("Step 2 -- Domain Adaptation")
         hist2 = step2(self.args, self.E2, self.C2, self.R2, self.source_loader, self.target_loader_train,
-                                       self.target_loader_eval, self.device, self.O2, self.scheduler2)
+                                       self.target_loader_eval, self.device, self.O2, self.scheduler2,den_w)
 
         self.history2['tot_loss'].extend(hist2['tot_loss'])
         self.history2['C_loss'].extend(hist2['C_loss'])

### 2022-02-07 ROS_AMLProject/step2_SourceTargetAdapt.py

@@ -5,11 +5,11 @@ from itertools import cycle
 from tqdm import tqdm
 import matplotlib.pyplot as plt
 
-def _do_epoch(args, E, C, R, source_loader, target_loader_train, optimizer, device):
+def _do_epoch(args, E, C, R, source_loader, target_loader_train, optimizer, device, den_w):
 
     # Adjust the learning rate for the unknown class
     w = [ 1.0 for _ in range(args.n_classes_known + 1) ]
-    w[-1] = 1/20
+    w[-1] = 1/den_w
     w = torch.tensor(w).to(device)
 
     C_criterion = nn.CrossEntropyLoss(weight=w)
@@ -110,7 +110,7 @@ def _do_epoch(args, E, C, R, source_loader, target_loader_train, optimizer, devi
     return tot_avg_loss, C_avg_loss, R_avg_loss, C_accuracy, R_accuracy
 
 
-def step2(args, E, C, R, source_loader, target_loader_train, target_loader_eval, device, optimizer, scheduler):
+def step2(args, E, C, R, source_loader, target_loader_train, target_loader_eval, device, optimizer, scheduler, den_w):
     """
     Performs the domain alignment through R2 while learning the unknown class using C2.
     After each epoch, we evaluate the performance of C2 on the evaluation target dataset.
@@ -140,7 +140,7 @@ def step2(args, E, C, R, source_loader, target_loader_train, target_loader_eval,
         C.train()
         R.train()
 
-        tot_loss, C_loss, R_loss, C_accuracy, R_accuracy = _do_epoch(args, E, C, R, source_loader, target_loader_train, optimizer, device)
+        tot_loss, C_loss, R_loss, C_accuracy, R_accuracy = _do_epoch(args, E, C, R, source_loader, target_loader_train, optimizer, device, den_w)
         history['tot_loss'].append(tot_loss)
         history['C_loss'].append(C_loss)
         history['R_loss'].append(R_loss)

### 2022-02-07 ROS_AMLProject/step2_SourceTargetAdapt.py
bug fixed

@@ -9,7 +9,7 @@ def _do_epoch(args, E, C, R, source_loader, target_loader_train, optimizer, devi
 
     # Adjust the learning rate for the unknown class
     w = [ 1.0 for _ in range(args.n_classes_known + 1) ]
-    w[-1] = 1/den_w
+    w[-1] = 1/float(den_w)
     w = torch.tensor(w).to(device)
 
     C_criterion = nn.CrossEntropyLoss(weight=w)

### 2022-02-07 ROS_AMLProject/step2_SourceTargetAdapt.py
bug fixed v2

@@ -9,7 +9,7 @@ def _do_epoch(args, E, C, R, source_loader, target_loader_train, optimizer, devi
 
     # Adjust the learning rate for the unknown class
     w = [ 1.0 for _ in range(args.n_classes_known + 1) ]
-    w[-1] = 1/float(den_w)
+    w[-1] = float(1/den_w)
     w = torch.tensor(w).to(device)
 
     C_criterion = nn.CrossEntropyLoss(weight=w)

### 2022-02-08 ROS_AMLProject/main.py
minor fix to reload pre-trained models

@@ -157,6 +157,11 @@ class Trainer:
         # -------------- #
 
         # ---- DATA LOADERS ---- #
+        # Source loader for the step 1 (known source in train mode)
+        source_path_file = f"txt_list/{self.args.source}_known.txt"
+        self.source_loader = data_helper.get_train_dataloader(self.args, source_path_file)
+        self.logger.info(f"Source known: {self.args.source} [{len(self.source_loader.dataset)} samples]")
+
         # This must remain untouched and it should be used only for the separation and for the final evaluation (whole target in eval mode)
         target_path_file = f"txt_list/{args.target}.txt"
         self.target_loader_eval = data_helper.get_val_dataloader(args, target_path_file)

### 2022-02-08 ROS_AMLProject/main.py
minor fix v2 for reloading pre-trained models

@@ -160,7 +160,6 @@ class Trainer:
         # Source loader for the step 1 (known source in train mode)
         source_path_file = f"txt_list/{self.args.source}_known.txt"
         self.source_loader = data_helper.get_train_dataloader(self.args, source_path_file)
-        self.logger.info(f"Source known: {self.args.source} [{len(self.source_loader.dataset)} samples]")
 
         # This must remain untouched and it should be used only for the separation and for the final evaluation (whole target in eval mode)
         target_path_file = f"txt_list/{args.target}.txt"

### 2022-02-08 ROS_AMLProject/main.py
minor fix to print best HOS overall

@@ -298,7 +298,7 @@ class Trainer:
         self.history2['eval_UNK'].extend(hist2['eval_UNK'])
         self.history2['eval_C_loss'].extend(hist2['eval_C_loss'])
 
-        best_hos = max(hist2['eval_HOS'])
+        best_hos = max(self.history2['eval_HOS'])
         self.logger.info(f"Best HOS: {best_hos*100:.4f} %")
 
     def trainer_target_evaluation(self):

### 2022-02-08 paper/main.tex
add paper introduction and update bib

@@
 \begin{abstract}
-
+  Lorem ipsum dolor sit amet, consectetur adipisci elit, sed do eiusmod tempor incidunt ut labore et dolore magna aliqua.
+  Ut enim ad minim veniam, quis nostrum exercitationem ullamco laboriosam, nisi ut aliquid ex ea commodi consequatur.
+  Duis aute irure reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur.
+  Excepteur sint obcaecat cupiditat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.
 \end{abstract}
@@
 %%%%%%%%% BODY TEXT
-\section{Introduction}
-\label{sec:intro}
+\section{Notes}
+\label{sec:notes}
 
-Start write here
-
-%-------------------------------------------------------------------------
-\subsection{Notes}
 %---------- LANGUAGE ----------
+\subsection{Language}
 All manuscripts must be in English.
 %---------- PAPER LENGTH ----------
+\subsection{Paper length}
 Papers, excluding the references section, must be no longer than eight pages in length.
@@
 %---------- MATH ----------
+\subsection{Math}
 Please number all of your sections and displayed equations as in these examples:
@@
 %---------- BLIND VIEW ----------
+\subsection{Blind View}
 Blind review means that you do not use the words ``my'' or ``our'' when citing previous work.
@@
 %---------- CAPTION EXAMPLE ----------
+\subsection{Caption Example}
 \begin{figure}[t]
@@
 %---------- MISCELLANEOUS: E.G., ET AL. ----------
+\subsection{Miscellaneous: e.g., et al.}
 The space after \eg, meaning ``for example'', should not be a sentence-ending space.
@@
 %---------- SUB-FIGURES EXAMPLE ----------
+\subsection{Sub-Figures examples}
 \begin{figure*}
@@
 %---------- FORMATTING ----------
+\subsection{Formatting}
 All text must be in a two-column format.
 %---------- FOOTNOTES ----------
+\subsection{Footnotes}
 Please use footnotes\footnote{This is what a footnote looks like.
@@
 %---------- CROSS-REFERENCES ----------
+\subsection{Cross-references}
 For the benefit of author(s) and readers, please use the
@@
 %---------- CAPTION REFERENCES ----------
+\subsection{Caption References}
 % Update the cvpr.cls to do the following automatically.
@@
 %---------- TABLE EXAMPLE ----------
+\subsection{Table Example}
 \begin{table}
@@
 %---------- CENTERING GRAPHICS ----------
+\subsection{Cenetring Graphics}
 All graphics should be centered.
@@
 %---------- COLOR ----------
+\subsection{Color}
 If you use color in your plots, please keep in mind that a significant subset of reviewers and readers may have a color vision deficiency; red-green blindness is the most frequent kind.
 Hence avoid relying only on color as the discriminative feature in plots (such as red \vs green lines), but add a second discriminative feature to ease disambiguation.
+
+%------------------------------------------------------------------------
+\section{Introduction}
+\label{sec:intro}
+Classical Machine Learning in the past years have made some oversimplified assumptions actually detached 
+from the usage of Artificial Intelligent systems in everyday real world and the problems they bring.
+
+The firt assumption is that the training and test sets come from the same distributions.
+Therefore, a model learned from the labeled training data is expected to perform well on the test data.
+However, this assumption may not always hold in real-world applications where the training and the 
+test data fall from different distributions and in this case naively applying the trained model on 
+the new dataset may cause degradation in the performance. To solve this problem we can make use of 
+Domain Adaptation, where our goal is to train a neural network on a source dataset for which labels 
+are available, and test a good accuracy on the target dataset, which is related but
+significantly different from the source dataset, and whose label or annotation is not available. 
+Generally it seeks to learn a model from a source labeled data that can be generalized to a target domain
+by minimizing the difference between domain distributions and enforcing feature extractor to extract 
+similar features for source and target domain images.
+As underlined in \cite{domainAdaptFarahani}, feature-based adaptation approaches aim to map the source data into the target data
+by learning a transformation that extracts invariant feature representation across domains, transforming
+the original features into a new feature space and then minimize the gap between domains in the new
+representation space in an optimization procedure, while preserving the underlying structure of the
+original data.
+
+Secondly, in real-world recognition/classification tasks it is usually difficult to collect 
+training samples to exhaust all classes when training a recognizer or classifier.
+A more realistic scenario is open set recognition (OSR) \cite{OSRsurvey}, where incomplete knowledge
+of the world exists at training time, and unknown classes can be submitted to an algorithm
+during testing, requiring the classifiers to not only accurately classify the seen classes
+but also effectively deal with unseen ones, which otherwise drastically weakens the robustness
+of the methods. On the contrary this system should reject unknown/unseen classes at test time and separate
+the known and unknown samples.
+As underlined by \cite{OSRclassRec}, existing open-set classifiers rely on deep networks trained in 
+a supervised manner on known classes in the training set; this causes specialization of learned
+representations to known classes and makes it hard to distinguish unknowns from knowns.
+
+To solve these significant issues this method is focused on a self-supervised task. 
+Self-supervised Learning is an unsupervised learning method where the supervised learning 
+task is created out of the unlabelled input data. This task could be as simple as given 
+the upper-half of the image, predict the lower-half of the same image.
+Supervised learning requires usually a lot of labelled data and getting good quality labelled 
+data is an expensive and time-consuming task. On the other hand, the unlabelled data is readily
+available in abundance.
+The fundamental idea for self-supervised learning is to create some auxiliary pre-text task
+for the model from the input data itself such that while solving the auxiliary task,
+the model learns the underlying structure of the data (for instance the high-level knowledge, correlations,
+metadata embedded in the data).
+This type of learning was recently used for Domain Adaptation, learning robust cross-domain features
+and supporting generalization \cite{CarlucciJigsaw,SelfSupervisedXu}, and also for some Open Set problems specialized for anomaly detection
+and discriminate normal and anomalous data \cite{bergman2020classificationbased,dectionGeometric}.
+
+The approach presented in this paper brings these topics together in the so called Open-Set Domain 
+Adaptation (OSDA) problem. A two-stage method is hence proposed, aiming to identify and isolate unknown
+class samples in the first stage, before reducing in the second stage the domain shift between the source 
+domain and the knwon target domain to avoid negative transfer.
+All this is done in both stages using a modified version of the rotation task as self-supervised model,
+predicting the relative rotation between an image and its rotated version.
+Finally a classifier is used to predict if each target sample belongs either to one of the knwon classes
+or to an unknown class, being in the latter case rejected.
+
+The method was evaluated on the Office-Home benchmark \cite{venkateswara2017deep} with a specific OSDA metric.
+
+ADD HERE RESULTS AND A BRIEF OF CONCLUSIVE IDEAS (ALSO POSSIBLE FUTURE WORKS)!!
 

### 2022-02-08 paper/main.tex
Some additions

@@
 
+\section{Method}
+\label{sec:method}
+
+\subsection{Problem Formulation}
+\label{sec:problemformulation}
+Our starting point is the source dataset, defined as $\mathcal{D}_s = \{({\bf x}_i^s, y_i^s)\}_{i=1}^{N_S} \sim p_s$, where each element ${\bf x}_i^s$ belonging to any $y_i^s$ is a sample from the source domain $S$.
+This dataset has a target counterpart, $\mathcal{D}_t = \{{\bf x}_i^t\}_{i=1}^{N_t} \sim p_t$ which is unlabeled.
+In OSDA we have that $p_s \neq p_t$.
+The source dataset $\mathcal{D}_s$ is associated with a set of known classes, $\mathcal{C}_s$, which can also be found in the target dataset $\mathcal{D}_t$, but is supposedly smaller.
+Hence we have that $|\mathcal{C}_s| < |\mathcal{C}_t|$ and that $\mathcal{C}_s \subset \mathcal{C}_t$.
+In a setting of domain adaptation, we further have that $p_t^s \neq p_s$, the target distribution of the known source classes
+A metric for measuring how different two domain are is the openness betweeen source and target domain\cite{bendale2015open}, defined as $\displaystyle \mathbb{O} = 1-\frac{\mathcal{C}_s}{\mathcal{C}_t}$.
+When $\mathbb{O} > 0$, we're dealing with an OSDA problem.
+
+\subsection{Approach}
+\label{sec:apporach}
+To tackle the task, we chose to split it in two different steps.
+First we have to train the model to separate between the known classes ($\mathcal{C}_s$) and the unknown classes ($\mathcal{C}_{t\setminus s})$ in a reliable enough way.
+This is achieved by using a semi-supervised task, by training to model to both recognize a sample class and its correct orientation.
+The second step is similar to a classic CSDA problem, where we train the model on a union of both source and target datasets.
+
+\subsection{Rotation Recognition}
+
+Let's denote with $rot({\bf x}, i)$ the rotation of the sample image {\bf x} by $i\times 90$ degrees clockwise.
+This is the self-supervised part of our proposed model as rotations $i \in [0, 3]$ can be randomly generated and then predicted.
+To avoid situations where the objective orientation of a sample would be a too complicated task, even for a human being, we also feed in input to the model the un-rotated image features.
+Alternatively, instead to have the model predict the rotation of a sample for any class, we also try using a different head for each one of the known classes $\mathcal{C_s}$, along with different loss functions.
+
+\subsection{Step I: Sample Separation}
+
+To separate samples we train the model on an enhanced version of $\mathcal{D}_s$, $\tilde{\mathcal{D}_s} = \{({\bf x}_i^s, \tilde{\bf x}_i^s, z)\}$ where $\tilde{\bf x}_i^s$ is the rotated version of ${\bf x}_i^s$ and $z$ is the rotation index.
+The network is composed by an extractor $E$ and two heads, $R_1$ and $C_1$ in its standard form.
+When using a multi-head rotation predictor, it is composed of $|\mathcal{C}_s|+1$ heads for the rotation task, and an additional one for the classification task.
+The features of both the original and rotated image are used to predict the rotation as $\tilde{z}_s = softmax(R_1([E({\bf x}^s), E(\tilde{\bf x}^s)]))$ while classes are predicted solely on un-rotated features $\tilde{\bf y}^s = softmax(C_1(E({\bf x}^s)))$.
+The model is training by minimizing an objective function defined as $\mathcal{L}_1 = \mathcal{L}_{C_1} + \mathcal{L}_{R_1}$.
+Both heads use a Cross-Entropy loss function:
+
+\begin{equation}
+  \mathcal{L}_{C_1} = -\sum_{i\in\mathcal{D}_s} {\bf y}_i^s \log \tilde{\bf y}_i^s
+\end{equation}
+\label{eq:baseloss_class}
+
+\begin{equation}
+  \mathcal{L}_{R_1} = -\alpha_1\sum_{i\in\mathcal{\tilde{D}}_s} {\bf y}_i^s \log \tilde{{\bf z}}_i^s
+\end{equation}
+\label{eq:baseloss_rot}
+
+We also try using a different loss function for the rotation classifier, which is:
+
+\begin{equation}
+  \mathcal{L}_{R_1} = -\alpha_1\sum_{i\in\mathcal{D}_s} {\bf y}_i^s \log \tilde{{\bf z}}_i^s+\lambda_1||{\bf v}_i^s-\gamma({\bf z}_i^s)||_2^2
+\end{equation}
+\label{eq:center_loss}
+
+In both versions $\alpha_1$ is the weight of the rotation task, $v_i$ is the penultimate layer of the rotation classifier $R_1$ and $\gamma({\bf z}_i)$ is the centroid of the features of class of ${\bf v}_i$.
+
 %------------------------------------------------------------------------

### 2022-02-09 paper/main.tex
Added remaining chapter 4

@@
 To avoid situations where the objective orientation of a sample would be a too complicated task, even for a human being, we also feed in input to the model the un-rotated image features.
-Alternatively, instead to have the model predict the rotation of a sample for any class, we also try using a different head for each one of the known classes $\mathcal{C_s}$, along with different loss functions.
+Alternatively, instead to have the model predict the rotation of a sample for any class, we also try using a different head for each one of the known classes $\mathcal{C}_s$, along with different loss functions.
 
@@
 
-To separate samples we train the model on an enhanced version of $\mathcal{D}_s$, $\tilde{\mathcal{D}_s} = \{({\bf x}_i^s, \tilde{\bf x}_i^s, z)\}$ where $\tilde{\bf x}_i^s$ is the rotated version of ${\bf x}_i^s$ and $z$ is the rotation index.
+To separate samples we train the model on an enhanced version of $\mathcal{D}_s$, $\tilde{\mathcal{D}_s} = \{({\bf x}_i^s, {\bf \tilde x}_i^s, z_i^s)\}_{i=1}^{N_s}$ where ${\bf \tilde x}_i^s$ is the rotated version of ${\bf x}_i^s$ and $z_i^s$ is the rotation index associated to image $i$.
 The network is composed by an extractor $E$ and two heads, $R_1$ and $C_1$ in its standard form.
 When using a multi-head rotation predictor, it is composed of $|\mathcal{C}_s|+1$ heads for the rotation task, and an additional one for the classification task.
-The features of both the original and rotated image are used to predict the rotation as $\tilde{z}_s = softmax(R_1([E({\bf x}^s), E(\tilde{\bf x}^s)]))$ while classes are predicted solely on un-rotated features $\tilde{\bf y}^s = softmax(C_1(E({\bf x}^s)))$.
+For the roation index prediction, we both use the single-head and multi-head architecture.
+The features of both original and rotated image are used to predict the rotation as ${\bf \tilde z}_s = softmax(R_1([E({\bf x}^s), E({\bf\tilde x}^s)]))$ in the single-head case and using the $j$-th head as ${\bf\tilde{z}}_s = softmax(R_{1,j}[E({\bf x}^s), E({\bf\tilde{x}}^s)])$ in the multi-head case.
+Classes are predicted only using un-rotated features as $\tilde{\bf y}^s = softmax(C_1(E({\bf x}^s)))$.
 The model is training by minimizing an objective function defined as $\mathcal{L}_1 = \mathcal{L}_{C_1} + \mathcal{L}_{R_1}$.
-Both heads use a Cross-Entropy loss function:
+This is the sum of two cross-entropy loss functions as in:
 
@@
 
-We also try using a different loss function for the rotation classifier, which is:
+Where $\alpha_1$ is a weight associated to the rotation task.
+We also try using an extended rotation objective function $\mathcal{L}_{R_1}^*$ also implementing a center loss function\cite{CenterLoss}:
 
 \begin{equation}
-  \mathcal{L}_{R_1} = -\alpha_1\sum_{i\in\mathcal{D}_s} {\bf y}_i^s \log \tilde{{\bf z}}_i^s+\lambda_1||{\bf v}_i^s-\gamma({\bf z}_i^s)||_2^2
+  \mathcal{L}_{R_1}^* = -\alpha_1\sum_{i\in\mathcal{D}_s} {\bf y}_i^s \log \tilde{{\bf z}}_i^s+\lambda_1||{\bf v}_i^s-\gamma({\bf z}_i^s)||_2^2
 \end{equation}
@@
 
-In both versions $\alpha_1$ is the weight of the rotation task, $v_i$ is the penultimate layer of the rotation classifier $R_1$ and $\gamma({\bf z}_i)$ is the centroid of the features of class of ${\bf v}_i$.
+Here {\bf $v_i$} is the penultimate layer of the rotation classifier, called {\it features}, and $\gamma({\bf z}_i)$ gives the center of the features ${\bf v}_i$ associated to class $i$ and $||\cdot||_2^2$ is the $l$-2 norm and $\lambda_1$ is the weight associated with this extension of the loss function.
+
+When training is completed, we can start separating samples.
+To do so, we get the normality score $\mathcal{N}(\cdot)$ which is defined as the maximum prediction of the rotation classifier, $\mathcal{N}({\bf\tilde{x}}_i^s) = \max({\bf\tilde{z}}_i^t)$.
+To tell wheter a sample belongs to the known samples of the target domain $\mathcal{D}_t^{knw}$ or the unknown one $\mathcal{D}_t^{unk}$ requires choosing a threshold $\tilde{\mathcal{N}}$.
+Then we can simply separate as:
+
+\begin{equation}
+  \begin{cases}
+    {\bf\tilde x}_i^t \in \mathcal{D}_t^{knw} & \text{ if } \mathcal{N}({\bf\tilde x}_i^s) \geq \tilde{\mathcal{N}} \\
+    {\bf\tilde x}_i^t \in \mathcal{D}_t^{unk} & \text{ if } \mathcal{N}({\bf\tilde x}_i^s) < \tilde{\mathcal{N}}
+  \end{cases}
+\end{equation}
+\label{eq:sample_separation}
+
+When employing a multi-head architecture, we need to choose which one of the $|\mathcal{C}_s|$ heads to use for the classification task.
+Head $R_{1,j}$ is used by picking $j$ as $\displaystyle j = \arg\max_j {\bf\tilde{y}}_i^s$.
+
+\subsection{Performance Metric}
+\label{sec:performance_metric}
+
+Evaluating model perfomance requires finding a balance between two metrics:
+the first one is {\it OS*}, the share of correctly classified samples;
+the second one is {\it UNK}, the share of correclty rejected samples.
+One common problem is a model never confident enough to reject a sample as unknown, thus possibly achieving high {\it OS*} scores but near-zero {\it UNK}, and the opposite one, a model rejecting every given sample achieving perfect {\it UNK} but zero {\it OS*} scores.
+To compare models in a robust manner, we picked an harmonic mean between {\it OS*} and {\it UNK}, defined as $HOS = 2\frac{OS^*\times UNK}{OS^*+UNK}$.
+This type of mean is more biased towards the lowest of the two scores, resulting in a more severe evaluation of models.
+
+\section{Experiments}
+\label{sec:experiments}
 

### 2022-02-09 paper/main.tex
Mockup tables

@@
 When employing a multi-head architecture, we need to choose which one of the $|\mathcal{C}_s|$ heads to use for the classification task.
-Head $R_{1,j}$ is used by picking $j$ as $\displaystyle j = \arg\max_j {\bf\tilde{y}}_i^s$.
+Head $R_{1,j}$ is used by picking $j$ as $\displaystyle j = \arg\max_j {\bf\tilde{y}}_i^t$.
 
@@
 \label{sec:experiments}
+
+\subsection{Dataset}
+\label{sec:dataset}
+
+Our model is tested on the {\it Office-Home} dataset\cite{OfficeHomeDataset}, which features $65$ classes of images over four different domains: Art (A), Clipart (C), Product (P) and Real World (R).
+We set the first $45$ classes to be known while the remaining $20$ are unknown.
+After each epoch performed during the domain alignment phase, a validation run is performed on the entire original target dataset.
+For each experiment, we report both the best achieved {\it HOS} as $HOS_{Best}$ and the one achieved by the last epoch as $HOS$.
+As separation is crucial for the model effectiveness, we also report the computer AUROC score for the first part.
+
+\subsection{Results}
+\label{sec:results}
+All the 12 source-to-target $S\to T$ shift are considered.
+Results are reported separately for each possible mode of execution, Multi-Head ON/OFF and Center-Loss ON/OFF.
+Each mode has a specific configuration, please refer to \ref{sec:implementation_and_ablation}.
+
+\begin{center}
+  \begin{table}
+    \begin{tabular}[h]{||c|c|c||c|c||}
+      \hline
+      \multicolumn{5}{||c||}{Single-Head, CE Loss} \\
+      \hline
+      Source & Target & $AUC_{ROC}$ & $HOS$ & $HOS_{Best}$ \\
+      S & T & 50\% & 30\% & 30\% \\
+      S & T & 50\% & 30\% & 30\% \\
+      S & T & 50\% & 30\% & 30\% \\
+      \hline
+      \hline
+      \multicolumn{5}{||c||}{Multi-Head, CE Loss} \\
+      \hline
+      Source & Target & $AUC_{ROC}$ & $HOS$ & $HOS_{Best}$ \\
+      S & T & 50\% & 30\% & 30\% \\
+      S & T & 50\% & 30\% & 30\% \\
+      S & T & 50\% & 30\% & 30\% \\
+      \hline
+      \hline
+      \multicolumn{5}{||c||}{Single-Head, CE+C Loss} \\
+      \hline
+      Source & Target & $AUC_{ROC}$ & $HOS$ & $HOS_{Best}$ \\
+      S & T & 50\% & 30\% & 30\% \\
+      S & T & 50\% & 30\% & 30\% \\
+      S & T & 50\% & 30\% & 30\% \\
+      \hline
+      \hline
+      \multicolumn{5}{||c||}{Multi-Head, CE+C Loss} \\
+      \hline
+      Source & Target & $AUC_{ROC}$ & $HOS$ & $HOS_{Best}$ \\
+      S & T & 50\% & 30\% & 30\% \\
+      S & T & 50\% & 30\% & 30\% \\
+      S & T & 50\% & 30\% & 30\% \\
+      \hline
+
+    \end{tabular}
+    \caption{\label{tab:resoffoff}Test Caption}
+  \end{table}
+\end{center}
 

### 2022-02-09 paper/main.tex
Further Work

@@
 \usepackage[pagebackref,breaklinks,colorlinks]{hyperref}
+\usepackage{multirow}
 
@@
 
-%%%%%%%%% BODY TEXT
-\section{Notes}
-\label{sec:notes}
-
-%---------- LANGUAGE ----------
-\subsection{Language}
-All manuscripts must be in English.
-%---------- PAPER LENGTH ----------
-\subsection{Paper length}
-Papers, excluding the references section, must be no longer than eight pages in length.
-The references section will not be included in the page count, and there is no limit on the length of the references section.
-%---------- MATH ----------
-\subsection{Math}
-Please number all of your sections and displayed equations as in these examples:
-\begin{equation}
-  E = m\cdot c^2
-  \label{eq:important}
-\end{equation}
-and
-\begin{equation}
-  v = a\cdot t.
-  \label{eq:also-important}
-\end{equation}
-All authors will benefit from reading Mermin's description of how to write mathematics:
-\url{http://www.pamitc.org/documents/mermin.pdf}.
-%---------- BLIND VIEW ----------
-\subsection{Blind View}
-Blind review means that you do not use the words ``my'' or ``our'' when citing previous work.
-
-Saying ``this builds on the work of Lucy Smith [1]'' does not say that you are Lucy Smith;
-it says that you are building on her work.
-If you are Smith and Jones, do not say ``as we show in [7]'', say ``as Smith and Jones show in [7]'' and at the end of the paper, include reference 7 as you would any other cited work.
-
-An example of a bad paper just asking to be rejected:
-\begin{quote}
-\begin{center}
-    An analysis of the frobnicatable foo filter.
-\end{center}
-
-   In this paper we present a performance analysis of our previous paper [1], and show it to be inferior to all previously known methods.
-   Why the previous paper was accepted without this analysis is beyond me.
-
-   [1] Removed for blind review
-\end{quote}
-
-An example of an acceptable paper:
-\begin{quote}
-\begin{center}
-     An analysis of the frobnicatable foo filter.
-\end{center}
-
-   In this paper we present a performance analysis of the  paper of Smith \etal [1], and show it to be inferior to all previously known methods.
-   Why the previous paper was accepted without this analysis is beyond me.
-
-   [1] Smith, L and Jones, C. ``The frobnicatable foo filter, a fundamental contribution to human knowledge''. Nature 381(12), 1-213.
-\end{quote}
-
-Finally, you may feel you need to tell the reader that more details can be found elsewhere, and refer them to a technical report.
-For conference submissions, the paper must stand on its own, and not {\em require} the reviewer to go to a tech report for further details.
-Thus, you may say in the body of the paper ``further details may be found in~\cite{Authors14b}''.
-Then submit the tech report as supplemental material.
-Again, you may not assume the reviewers will read this material.
-%---------- CAPTION EXAMPLE ----------
-\subsection{Caption Example}
-\begin{figure}[t]
-  \centering
-  \fbox{\rule{0pt}{2in} \rule{0.9\linewidth}{0pt}}
-   %\includegraphics[width=0.8\linewidth]{egfigure.eps}
-
-   \caption{Example of caption.
-   It is set in Roman so that mathematics (always set in Roman: $B \sin A = A \sin B$) may be included without an ugly clash.}
-   \label{fig:onecol}
-\end{figure}
-%---------- MISCELLANEOUS: E.G., ET AL. ----------
-\subsection{Miscellaneous: e.g., et al.}
-The space after \eg, meaning ``for example'', should not be a sentence-ending space.
-So \eg is correct, {\em e.g.} is not.
-The provided \verb'\eg' macro takes care of this.
-
-When citing a multi-author paper, you may save space by using ``et alia'', shortened to ``\etal'' (not ``{\em et.\ al.}'' as ``{\em et}'' is a complete word).
-If you use the \verb'\etal' macro provided, then you need not worry about double periods when used at the end of a sentence as in Alpher \etal.
-However, use it only when there are three or more authors.
-%---------- SUB-FIGURES EXAMPLE ----------
-\subsection{Sub-Figures examples}
-\begin{figure*}
-  \centering
-  \begin{subfigure}{0.68\linewidth}
-    \fbox{\rule{0pt}{2in} \rule{.9\linewidth}{0pt}}
-    \caption{An example of a subfigure.}
-    \label{fig:short-a}
-  \end{subfigure}
-  \hfill
-  \begin{subfigure}{0.28\linewidth}
-    \fbox{\rule{0pt}{2in} \rule{.9\linewidth}{0pt}}
-    \caption{Another example of a subfigure.}
-    \label{fig:short-b}
-  \end{subfigure}
-  \caption{Example of a short caption, which should be centered.}
-  \label{fig:short}
-\end{figure*}
-%---------- FORMATTING ----------
-\subsection{Formatting}
-All text must be in a two-column format.
-%---------- FOOTNOTES ----------
-\subsection{Footnotes}
-Please use footnotes\footnote{This is what a footnote looks like.
-It often distracts the reader from the main flow of the argument.} sparingly.
-Indeed, try to avoid footnotes altogether and include necessary peripheral observations in the text (within parentheses, if you prefer, as in this sentence).
-If you wish to use a footnote, place it at the bottom of the column on the page on which it is referenced.
-Use Times 8-point type, single-spaced.
-%---------- CROSS-REFERENCES ----------
-\subsection{Cross-references}
-For the benefit of author(s) and readers, please use the
-{\small\begin{verbatim}
-  \cref{...}
-\end{verbatim}}  command for cross-referencing to figures, tables, equations, or sections.
-This will automatically insert the appropriate label alongside the cross-reference as in this example:
-\begin{quotation}
-  To see how our method outperforms previous work, please see \cref{fig:onecol} and \cref{tab:example}.
-  It is also possible to refer to multiple targets as once, \eg~to \cref{fig:onecol,fig:short-a}.
-  You may also return to \cref{sec:formatting} or look at \cref{eq:also-important}.
-\end{quotation}
-If you do not wish to abbreviate the label, for example at the beginning of the sentence, you can use the
-{\small\begin{verbatim}
-  \Cref{...}
-\end{verbatim}}
-command. Here is an example:
-\begin{quotation}
-  \Cref{fig:onecol} is also quite important.
-\end{quotation}
-%---------- CAPTION REFERENCES ----------
-\subsection{Caption References}
-% Update the cvpr.cls to do the following automatically.
-% For this citation style, keep multiple citations in numerical (not
-% chronological) order, so prefer \cite{Alpher03,Alpher02,Authors14} to
-% \cite{Alpher02,Alpher03,Authors14}.
-List and number all bibliographical references at the end of your paper.
-When referenced in the text, enclose the citation number in square brackets, for
-example~\cite{Authors14}.
-Where appropriate, include page numbers and the name(s) of editors of referenced books.
-When you cite multiple papers at once, please make sure that you cite them in numerical order like this \cite{Alpher02,Alpher03,Alpher05,Authors14b,Authors14}.
-If you use the template as advised, this will be taken care of automatically.
-%---------- TABLE EXAMPLE ----------
-\subsection{Table Example}
-\begin{table}
-  \centering
-  \begin{tabular}{@{}lc@{}}
-    \toprule
-    Method & Frobnability \\
-    \midrule
-    Theirs & Frumpy \\
-    Yours & Frobbly \\
-    Ours & Makes one's heart Frob\\
-    \bottomrule
-  \end{tabular}
-  \caption{Results.   Ours is better.}
-  \label{tab:example}
-\end{table}
-%---------- CENTERING GRAPHICS ----------
-\subsection{Cenetring Graphics}
-All graphics should be centered.
-In \LaTeX, avoid using the \texttt{center} environment for this purpose, as this adds potentially unwanted whitespace.
-Instead use
-{\small\begin{verbatim}
-  \centering
-\end{verbatim}}
-at the beginning of your figure.
-
-When placing figures in \LaTeX, it's almost always best to use \verb+\includegraphics+, and to specify the figure width as a multiple of the line width as in the example below
-{\small\begin{verbatim}
-   \usepackage{graphicx} ...
-   \includegraphics[width=0.8\linewidth]
-                   {myfile.pdf}
-\end{verbatim}
-}
-%---------- COLOR ----------
-\subsection{Color}
-If you use color in your plots, please keep in mind that a significant subset of reviewers and readers may have a color vision deficiency; red-green blindness is the most frequent kind.
-Hence avoid relying only on color as the discriminative feature in plots (such as red \vs green lines), but add a second discriminative feature to ease disambiguation.
-
-%------------------------------------------------------------------------
 \section{Introduction}
@@
 To separate samples we train the model on an enhanced version of $\mathcal{D}_s$, $\tilde{\mathcal{D}_s} = \{({\bf x}_i^s, {\bf \tilde x}_i^s, z_i^s)\}_{i=1}^{N_s}$ where ${\bf \tilde x}_i^s$ is the rotated version of ${\bf x}_i^s$ and $z_i^s$ is the rotation index associated to image $i$.
-The network is composed by an extractor $E$ and two heads, $R_1$ and $C_1$ in its standard form.
-When using a multi-head rotation predictor, it is composed of $|\mathcal{C}_s|+1$ heads for the rotation task, and an additional one for the classification task.
-For the roation index prediction, we both use the single-head and multi-head architecture.
+The network is composed by an extractor $E$ and two classifiers, $R_1$ and $C_1$ in its standard form.
+When using a multi-head rotation classifier, it is composed of $|\mathcal{C}_s|+1$ heads for the rotation task, and an additional one for the classification task.
+When using a multi-head predictor, which head to use during separation is chosen by the object classifier $C_1$.
 The features of both original and rotated image are used to predict the rotation as ${\bf \tilde z}_s = softmax(R_1([E({\bf x}^s), E({\bf\tilde x}^s)]))$ in the single-head case and using the $j$-th head as ${\bf\tilde{z}}_s = softmax(R_{1,j}[E({\bf x}^s), E({\bf\tilde{x}}^s)])$ in the multi-head case.
-Classes are predicted only using un-rotated features as $\tilde{\bf y}^s = softmax(C_1(E({\bf x}^s)))$.
+Classes are predicted only using un-rotated features as $\tilde{\bf y}^s = softmax(C_1(E({\bf x}_i^s)))$.
 The model is training by minimizing an objective function defined as $\mathcal{L}_1 = \mathcal{L}_{C_1} + \mathcal{L}_{R_1}$.
@@
 
+\subsection{Step II: Domain Alignment}
+\label{sec:domain_alignment}
+
 \subsection{Performance Metric}
@@
 After each epoch performed during the domain alignment phase, a validation run is performed on the entire original target dataset.
-For each experiment, we report both the best achieved {\it HOS} as $HOS_{Best}$ and the one achieved by the last epoch as $HOS$.
+For each experiment, we report both the best achieved HOS and the last reported HOS.
 As separation is crucial for the model effectiveness, we also report the computer AUROC score for the first part.
@@
 \label{sec:results}
-All the 12 source-to-target $S\to T$ shift are considered.
-Results are reported separately for each possible mode of execution, Multi-Head ON/OFF and Center-Loss ON/OFF.
-Each mode has a specific configuration, please refer to \ref{sec:implementation_and_ablation}.
+Table \ref{tab:results} contains the results for all 12 (ne abbiamo provati davvero 12???) possible domain shifts, as well as perfomance differences when using multi-head rotation classifiers and center loss.
+Each mode has a specific configuration further discussed in \ref{sec:ablation_study}.
 
-\begin{center}
 \begin{table}
-    \begin{tabular}[h]{||c|c|c||c|c||}
+  \centering
+  \begin{tabular}[t]{||c|c|c||c|c||}
     \hline
@@
     \hline
-      Source & Target & $AUC_{ROC}$ & $HOS$ & $HOS_{Best}$ \\
+    Source & Target & AUROC & HOS & HOS$_{Best}$ \\
     S & T & 50\% & 30\% & 30\% \\
@@
     \hline 
+    \hline
+    \multicolumn{5}{||c||}{No Rotation} \\
+    \hline
+    Source & Target & AUROC & HOS & HOS$_{Best}$ \\
+    S & T & 50\% & 30\% & 30\% \\
+    S & T & 50\% & 30\% & 30\% \\
+    S & T & 50\% & 30\% & 30\% \\
+    \hline
+  \end{tabular}
+  \caption{\label{tab:results}Test Caption}
+\end{table}
 
+\section{Implementation Details}
+\subsection{Model Parameters}
+\label{sec:model_parameters}
+
+All models were run using a Stochastic Gradient Descent with batch size 32, a weight decay of 0.0005 and momentum set to 0.9.
+For single-headed models, the base learning rate is set to 0.001 and for multi-headed models it is set to 0.003.
+This is because multi-headed models take a longer time to converge.
+All rotation classifier have the learning rate set to a tenth of the base learning rate.
+Learning rates are reduced by a factor of 10 after 90\% of epochs.
+All models are run for 50 epochs for the first step described in \ref{eq:sample_separation} and for 25 epochs for the second step described in \ref{sec:domain_alignment}.
+For model using the center loss, a centroid learning rate of 0.5 is used.
+Other parameters are configuration-sepcific and reported in table \ref{tab:params}.
+When considering a "No Rotation" model, it is meant that $\alpha_2 = 0$ is used.
+
+\begin{table}
+  \centering
+  \begin{tabular}[b]{||c|c|c|c|c|c||}
+    \hline
+    MH & CL & $\alpha_1$ & $\alpha_2$ & $\lambda_1$ & $\mathcal{\tilde N}$ \\
+    \hline
+    Off & Off & 0.0 & 0.0 & 0.0 & 0.0 \\
+    On & Off & 0.0 & 0.0 & 0.0 & 0.0 \\
+    Off & On & 0.0 & 0.0 & 0.0 & 0.0 \\
+    On & On & 0.0 & 0.0 & 0.0 & 0.0 \\
+    \hline
   \end{tabular}
-    \caption{\label{tab:resoffoff}Test Caption}
+  \caption{\label{tab:params}Model Parameters}
 \end{table}
-\end{center}
 
-%------------------------------------------------------------------------
-\section{Method - Write name of proposal approach}
-\label{sec:method}
-%------------------------------------------------------------------------
-\subsection{Subsection 1}
-%------------------------------------------------------------------------
-\subsection{Subsection 2}
+\subsection{Ablation Study}
+\label{sec:ablation_study}
+As shown by table \ref{tab:results}, different architectures greatly improve performance, and as shown by table \ref{tab:params} each one has its set of optimal parameters.
+To choose the best parameters, a sequential approach is followed, by optimizing one parameter at the time.
+The order of optimization followed is: $\alpha_1$, $\lambda_1$, $\mathcal{\tilde N}$, $\alpha_2$.
+Models not using center loss skip the $\lambda_1$ optimization.
+Ablation study were run on two domain shift, Art $\to$ Clipart and Clipart $\to$ Art.
+In table \ref{tab:ablation_params} we report the steps followed, picking the parameter that gives the highest mean HOS between the two shifts.
+All other settings follow what is reported in \ref{sec:model_parameters}.
+For compactness, here are the final results of the data otherwise reported from \ref{tab:ablationoffoff} on.
 
-%------------------------------------------------------------------------
-\section{Experiments}
-\label{sec:experiments}
-%------------------------------------------------------------------------
-\subsection{Subsection 1 - Setup}
-%------------------------------------------------------------------------
-\subsection{Subsection 2 - Implementation Details}
-%------------------------------------------------------------------------
-\subsection{Subsection 3 - Results}
+\begin{table}
+  \centering
+  \begin{tabular}[h]{||c|c|c|c||c||}
+    \hline
+    \multicolumn{5}{||c||}{MH OFF CL OFF} \\
+    \hline
+    $\alpha_1$ & $\mathcal{\tilde N}$ & $\alpha_2$  & AUROC & HOS$_{mean}$\\    
+    \hline
+    \hline
+    \multicolumn{5}{||c||}{Picking $\alpha_1$} \\
+    \hline
+    1.0 & \multirow{4}{*}{0.5} & \multirow{4}{*}{3.0} & 0.5 & 30\% \\
+    3.0 & & & 0.5 & 30\% \\
+    5.0 & & & 0.5 & 30\% \\
+    10.0 & & & 0.5 & 30\% \\
+    \hline
+    \hline
+    \multicolumn{5}{||c||}{Picking $\mathcal{\tilde N}$} \\
+    \hline
+    \multirow{4}{*}{1.0} & 0.40 & \multirow{4}{*}{3.0} & 0.5 & 50\%\\
+    & 0.50 && 0.5 & 50\% \\
+    & 0.55 && 0.5 & 50\% \\
+    & 0.60 && 0.5 & 50\% \\
+    \hline
+    \hline
+    \multicolumn{5}{||c||}{Picking $\alpha_2$} \\
+    \hline
+    \multirow{4}{*}{1.0} & \multirow{4}{*}{0.6} & 1.0 & 0.5 & 50\%\\
+    && 3.0 & 0.5 & 50\% \\
+    && 5.0 & 0.5 & 50\% \\
+    && 10.0 & 0.5 & 50\% \\
+    \hline
+    \hline
+    \multicolumn{5}{||c||}{Final Parameters} \\
+    \hline
+    1.0 & 0.6 & 3.0 & 0.5 & 50\%\\
+    \hline
+  \end{tabular}
+  \caption{\label{tab:ablationoffoff} Ablation performed for OFF-OFF configuration}
+\end{table}
+\section{Future Work}
 
-%------------------------------------------------------------------------
-\section{Conclusions (and Future Work)}
-\label{sec:conclusions}
-
-%%%%%%%%% APPENDIX - TAKEN FROM ANOTHER TEMPLATE!!
-\appendix
-\section{Appendices}
-\label{sec:appendix}
-Appendices are material that can be read, and include lemmas, formulas, proofs, and tables that are not critical to the reading and understanding of the paper. 
-Appendices should be \textbf{uploaded as supplementary material} when submitting the paper for review.
-Upon acceptance, the appendices come after the references, as shown here.
-
-\paragraph{\LaTeX-specific details:}
-Use {\small\verb|\appendix|} before any appendix section to switch the section numbering over to letters.
-
-\section{Supplemental Material}
-\label{sec:supplemental}
-Submissions may include\cite{GeoTran}\cite{CenterLoss}\cite{BucciROS}\cite{OldROS}\cite{CarlucciJigsaw} non-readable supplementary material used in the work and described in the paper.
-Any accompanying software and/or data should include licenses and documentation of research review as appropriate.
-Supplementary material may report preprocessing decisions, model parameters, and other details necessary for the replication of the experiments reported in the paper.
-Seemingly small preprocessing decisions can sometimes make a large difference in performance, so it is crucial to record such decisions to precisely characterize state-of-the-art methods.
-
-Nonetheless, supplementary material should be supplementary (rather than central) to the paper.
-\textbf{Submissions that misuse the supplementary material may be rejected without review.}
-Supplementary material may include explanations or details of proofs or derivations that do not fit into the paper, lists of
-features or feature templates, sample inputs and outputs for a system, pseudo-code or source code, and data.
-(Source code and data should be separate uploads, rather than part of the paper).
-
-The paper should not rely on the supplementary material: while the paper may refer to and cite the supplementary material and the supplementary material will be available to the reviewers, they will not be asked to review the supplementary material.
+Here we should write how a better way of separation is required and more training might help.
 

### 2022-02-09 paper/main.tex
Rewording

@@
 \begin{abstract}
-  Lorem ipsum dolor sit amet, consectetur adipisci elit, sed do eiusmod tempor incidunt ut labore et dolore magna aliqua.
-  Ut enim ad minim veniam, quis nostrum exercitationem ullamco laboriosam, nisi ut aliquid ex ea commodi consequatur.
-  Duis aute irure reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur.
-  Excepteur sint obcaecat cupiditat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.
+  Performance loss over the change of domain in deep learning applications is a common problem.
+  Solving the issues usually relies on adapting the model to the new domain having at disposal large and labeled datasets, which is not always the case or cost-effective.
+  In this paper we propose a new approach to the problem, to adapt in a robust manner a model to the new domain while not needing large amounts of data thanks to a self-supervised task.
+  Experiments conducted on the Office-Home dataset show really promising results.
 \end{abstract}
@@
   \mathcal{L}_{C_1} = -\sum_{i\in\mathcal{D}_s} {\bf y}_i^s \log \tilde{\bf y}_i^s
+  \label{eq:baseloss_class}
 \end{equation}
-\label{eq:baseloss_class}
 
@@
   \mathcal{L}_{R_1} = -\alpha_1\sum_{i\in\mathcal{\tilde{D}}_s} {\bf y}_i^s \log \tilde{{\bf z}}_i^s
+  \label{eq:baseloss_rot}
 \end{equation}
-\label{eq:baseloss_rot}
 
@@
   \mathcal{L}_{R_1}^* = -\alpha_1\sum_{i\in\mathcal{D}_s} {\bf y}_i^s \log \tilde{{\bf z}}_i^s+\lambda_1||{\bf v}_i^s-\gamma({\bf z}_i^s)||_2^2
+  \label{eq:center_loss}
 \end{equation}
-\label{eq:center_loss}
 
@@
   \end{cases}
+  \label{eq:sample_separation}
 \end{equation}
-\label{eq:sample_separation}
 
@@
 
-\subsection{Performance Metric}
-\label{sec:performance_metric}
+In this phase, two "new" datasets are used.
+The first one is $\mathcal{D}_s^*$, composed as $\mathcal{D}_s \cup \mathcal{D}_t^{unk}$.
+Note that since $\mathcal{D}_t$ is an unlabeled dataset but $\mathcal{D}_s^*$ is a labeled one, all samples in $\mathcal{D}_t^{unk}$ are simply labeled as unknowns.
+The second one is $\mathcal{D}_t^{knw}$ which is still an unlabeled dataset.
+Here we also introduce two new classifiers, $C_2$ and $R_2$.
+$C_2$ is the object classifier, but while $C_1$ had a $|\mathcal{C}_s|$-dimensional output, having to accomodate the new "Unknown" class, it has a $|\mathcal{C}_s|+1$-dimensional output.
+$R_2$ instead is the rotation classifier, which in this step is always single-headed and has its own weight $\alpha_2$.
+These two classifiers try to minimize the objective function described in equations \ref{eq:baseloss_class} and \ref{eq:baseloss_rot}.
+One of the main differences between the two steps is that while in the first one we used $C_1$ to regularize the rotation task, here we use $R_2$ to regularize the main classification task.
 
-Evaluating model perfomance requires finding a balance between two metrics:
-the first one is {\it OS*}, the share of correctly classified samples;
-the second one is {\it UNK}, the share of correclty rejected samples.
-One common problem is a model never confident enough to reject a sample as unknown, thus possibly achieving high {\it OS*} scores but near-zero {\it UNK}, and the opposite one, a model rejecting every given sample achieving perfect {\it UNK} but zero {\it OS*} scores.
+\subsection{Performance Metrics}
+\label{sec:performance_metrics}
+
+Evaluating model perfomance requires finding a balance between two values:
+{\it OS*}, the share of correctly classified samples;
+{\it UNK}, the share of correclty rejected samples.
+A model never confident enough to reject a sample as unknown could still achieve high {\it OS*} scores and near-zero {\it UNK}, while a model marking every given sample as unkwnown will achieve perfect {\it UNK} and zero {\it OS*}.
 To compare models in a robust manner, we picked an harmonic mean between {\it OS*} and {\it UNK}, defined as $HOS = 2\frac{OS^*\times UNK}{OS^*+UNK}$.
@@
 
-Here we should write how a better way of separation is required and more training might help.
+The results show that self-supervision technique can help in domain adaptation task and open-set classification tasks.
+A few critical points still remain on our method of study and proposed solution.
+The most important one is probably parameter choosing for different models, as we have seen that variations cause huge differences in results and sequential optimization of parameter is a sub-optimal heuristic.
+Furthermore, having the model to learn two different tasks at once, it could be useful to use a slower learning model at the expense of longer training times.
 

### 2022-02-10 paper/main.tex
Abstract rephrase

@@
 \begin{abstract}
-  Performance loss over the change of domain in deep learning applications is a common problem.
-  Solving the issues usually relies on adapting the model to the new domain having at disposal large and labeled datasets, which is not always the case or cost-effective.
-  In this paper we propose a new approach to the problem, to adapt in a robust manner a model to the new domain while not needing large amounts of data thanks to a self-supervised task.
-  Experiments conducted on the Office-Home dataset show really promising results.
+  Performance loss over domain change is a common problem in machine learning applications.
+  Solving the issue usually relies on adapting the model to the new domain by having at disposal large and labeled datasets, either rare or costly to acquire.
+  In this paper we propose a new approach, adapting models to the new domains while not needing relying on labeled data thanks to a self-supervision.
+  Experiments conducted on the Office-Home dataset show interesting results and method effectiveness.
 \end{abstract}

### 2022-02-10 paper/main.tex
Introduction rephrase

@@
 \label{sec:intro}
-Classical Machine Learning in the past years have made some oversimplified assumptions actually detached 
-from the usage of Artificial Intelligent systems in everyday real world and the problems they bring.
+Classical machine learning in the past years has made some oversimplified assumptions actually detached % Punteggiatura?
+from the usage of artificial intelligence systems in everyday real world and the problems they come with.
 
-The firt assumption is that the training and test sets come from the same distributions.
-Therefore, a model learned from the labeled training data is expected to perform well on the test data.
-However, this assumption may not always hold in real-world applications where the training and the 
-test data fall from different distributions and in this case naively applying the trained model on 
-the new dataset may cause degradation in the performance. To solve this problem we can make use of 
-Domain Adaptation, where our goal is to train a neural network on a source dataset for which labels 
-are available, and test a good accuracy on the target dataset, which is related but
-significantly different from the source dataset, and whose label or annotation is not available. 
-Generally it seeks to learn a model from a source labeled data that can be generalized to a target domain
-by minimizing the difference between domain distributions and enforcing feature extractor to extract 
-similar features for source and target domain images.
-As underlined in \cite{domainAdaptFarahani}, feature-based adaptation approaches aim to map the source data into the target data
-by learning a transformation that extracts invariant feature representation across domains, transforming
-the original features into a new feature space and then minimize the gap between domains in the new
-representation space in an optimization procedure, while preserving the underlying structure of the
-original data.
+The first assumption is that training and test sets come from the same distributions:
+a model trained on labeled data is expected to perform as well as on the test data.
+However, this assumption not always holds in real-world applications, 
+where naively applying the trained model on a new dataset may cause degradation in the performance.
+To solve this problem Domain Adaptation is widely used, 
+where the goal is to train a neural network on a source dataset for which labels are available and search for good performance on a target dataset, 
+which is related to but significantly different from the source dataset, 
+and whose label or annotation is not available. 
+Generally this is done by by minimizing the difference between domain distributions and enforcing the recognition of domain invariant patterns in both domains. 
+As underlined in \cite{domainAdaptFarahani}, 
+this is usually achieved by mapping source and target data by learning transformations for extracting such features and minimizing the gap between domains in the new representation space in an optimization procedure,
+while preserving the underlying structure of the original data.
 
-Secondly, in real-world recognition/classification tasks it is usually difficult to collect 
-training samples to exhaust all classes when training a recognizer or classifier.
-A more realistic scenario is open set recognition (OSR) \cite{OSRsurvey}, where incomplete knowledge
-of the world exists at training time, and unknown classes can be submitted to an algorithm
-during testing, requiring the classifiers to not only accurately classify the seen classes
-but also effectively deal with unseen ones, which otherwise drastically weakens the robustness
-of the methods. On the contrary this system should reject unknown/unseen classes at test time and separate
-the known and unknown samples.
-As underlined by \cite{OSRclassRec}, existing open-set classifiers rely on deep networks trained in 
-a supervised manner on known classes in the training set; this causes specialization of learned
-representations to known classes and makes it hard to distinguish unknowns from knowns.
+Secondly, 
+in real-world classification tasks it is usually difficult to collect training samples to exhaust all classes when training a model.
+A more realistic scenario is open set recognition (OSR) \cite{OSRsurvey},
+where incomplete knowledge of the world exists at training time and unknown classes can be injected during testing, 
+requiring classifiers to not only accurately classify the seen classes but also effectively deal with unseen ones,
+which would otherwise drastically weaken the robustness of the methods.
+On the contrary this system should reject unknown classes at test time and separate the known and unknown samples.
+As underlined by \cite{OSRclassRec}, 
+existing open-set classifiers rely on deep networks trained in a supervised fashion on known classes in the training set;
+this causes specialization of learned representations to known classes and makes it hard to distinguish the unknowns from the knowns.
 
-To solve these significant issues this method is focused on a self-supervised task. 
-Self-supervised Learning is an unsupervised learning method where the supervised learning 
-task is created out of the unlabelled input data. This task could be as simple as given 
-the upper-half of the image, predict the lower-half of the same image.
-Supervised learning requires usually a lot of labelled data and getting good quality labelled 
-data is an expensive and time-consuming task. On the other hand, the unlabelled data is readily
-available in abundance.
-The fundamental idea for self-supervised learning is to create some auxiliary pre-text task
-for the model from the input data itself such that while solving the auxiliary task,
-the model learns the underlying structure of the data (for instance the high-level knowledge, correlations,
-metadata embedded in the data).
-This type of learning was recently used for Domain Adaptation, learning robust cross-domain features
-and supporting generalization \cite{CarlucciJigsaw,SelfSupervisedXu}, and also for some Open Set problems specialized for anomaly detection
-and discriminate normal and anomalous data \cite{bergman2020classificationbased,dectionGeometric}.
+To solve these significant issues our method is focused on a self-supervised task. 
+Self-supervised learning is an unsupervised learning technique where the supervised task is created out of the unlabeled input data. 
+This task could be as simple as predicting the lower half of an image being given the upper half of the same.
+Supervised learning requires both labeled and high quality data,
+usually very expensive, 
+whereas unlabeled data is often readily available in abundance.
+The fundamental idea behind self-supervised learning is creating some auxiliary task from input data so that,
+by solving such task,
+the model can learn the underlying structure of the data,
+for instance high-level knowledge, correlations, and metadata embedded in the data.
+This type of learning was recently used for Domain Adaptation, 
+learning robust cross-domain features and supporting generalization \cite{CarlucciJigsaw,SelfSupervisedXu},
+and also for some Open Set problems specialized in anomaly detection and discriminating anomalous data \cite{bergman2020classificationbased,dectionGeometric}.
 
-The approach presented in this paper brings these topics together in the so called Open-Set Domain 
-Adaptation (OSDA) problem. A two-stage method is hence proposed, aiming to identify and isolate unknown
-class samples in the first stage, before reducing in the second stage the domain shift between the source 
-domain and the knwon target domain to avoid negative transfer.
-All this is done in both stages using a modified version of the rotation task as self-supervised model,
+The approach presented in this paper brings these topics together in the so called Open-Set Domain Adaptation (OSDA) problem. 
+A two-stage method is hence proposed, 
+aiming to identify and isolate unknown class samples in the first stage, 
+before reducing in the second stage the domain gap between the source domain and the known target domain to avoid negative transfer.
+This is done in both stages using a modified version of the rotation task as self-supervised model,
 predicting the relative rotation between an image and its rotated version.
-Finally a classifier is used to predict if each target sample belongs either to one of the knwon classes
-or to an unknown class, being in the latter case rejected.
+Finally a classifier is used to predict if each target sample belongs either to one of the knwon classes or to an unknown class, 
+being rejected in the latter case.
 
-The method was evaluated on the Office-Home benchmark \cite{venkateswara2017deep} with a specific OSDA metric.
+The method was evaluated on the Office-Home benchmark \cite{OfficeHomeDataset} with a specific OSDA metric.
 
-ADD HERE RESULTS AND A BRIEF OF CONCLUSIVE IDEAS (ALSO POSSIBLE FUTURE WORKS)!!
+{\bf ADD HERE RESULTS AND A BRIEF OF CONCLUSIVE IDEAS (ALSO POSSIBLE FUTURE WORKS)!!}
 

### 2022-02-10 paper/main.tex
Experiments + Method Rephrase

@@
 \label{sec:problemformulation}
-Our starting point is the source dataset, defined as $\mathcal{D}_s = \{({\bf x}_i^s, y_i^s)\}_{i=1}^{N_S} \sim p_s$, where each element ${\bf x}_i^s$ belonging to any $y_i^s$ is a sample from the source domain $S$.
-This dataset has a target counterpart, $\mathcal{D}_t = \{{\bf x}_i^t\}_{i=1}^{N_t} \sim p_t$ which is unlabeled.
+Our starting point is the source dataset, 
+defined as $\mathcal{D}_s = \{({\bf x}_i^s, y_i^s)\}_{i=1}^{N_S} \sim p_s$, 
+where each element ${\bf x}_i^s$ belonging to class $y_i^s$ is a sample from the source domain {\it S}.
+This dataset has a target counterpart, 
+$\mathcal{D}_t = \{{\bf x}_i^t\}_{i=1}^{N_t} \sim p_t$ which is unlabeled instead.
 In OSDA we have that $p_s \neq p_t$.
-The source dataset $\mathcal{D}_s$ is associated with a set of known classes, $\mathcal{C}_s$, which can also be found in the target dataset $\mathcal{D}_t$, but is supposedly smaller.
-Hence we have that $|\mathcal{C}_s| < |\mathcal{C}_t|$ and that $\mathcal{C}_s \subset \mathcal{C}_t$.
-In a setting of domain adaptation, we further have that $p_t^s \neq p_s$, the target distribution of the known source classes
-A metric for measuring how different two domain are is the openness betweeen source and target domain\cite{bendale2015open}, defined as $\displaystyle \mathbb{O} = 1-\frac{\mathcal{C}_s}{\mathcal{C}_t}$.
+The source dataset $\mathcal{D}_s$ is associated with a set of known classes $\mathcal{C}_s$, 
+which can also be found in the target dataset $\mathcal{D}_t$ but is supposedly smaller.
+In other words,
+$|\mathcal{C}_s| < |\mathcal{C}_t|$ and $\mathcal{C}_s \subset \mathcal{C}_t$.
+In domain adaptation, 
+we further have that the target distribution of the known source classes differs from the target distribution of known classes,
+so $p_t^s \neq p_s$, 
+A metric to measure how different two domains are is the openness betweeen source and target domain\cite{bendale2015open}, 
+defined as $\displaystyle \mathbb{O} = 1-\frac{\mathcal{C}_s}{\mathcal{C}_t}$.
 When $\mathbb{O} > 0$, we're dealing with an OSDA problem.
@@
 \label{sec:apporach}
-To tackle the task, we chose to split it in two different steps.
-First we have to train the model to separate between the known classes ($\mathcal{C}_s$) and the unknown classes ($\mathcal{C}_{t\setminus s})$ in a reliable enough way.
-This is achieved by using a semi-supervised task, by training to model to both recognize a sample class and its correct orientation.
-The second step is similar to a classic CSDA problem, where we train the model on a union of both source and target datasets.
+The task is split in two separate stages.
+First, 
+we have to train the model to separate between the known classes ($\mathcal{C}_s$) and the unknown classes ($\mathcal{C}_{t\setminus s})$ in a reliable way.
+This is achieved via the self-supervised task,
+training the model to both recognize the class of a sample and its relative orientation.
+Secondly,
+we train the model on a union of both source and target datasets,
+to reject samples when they are not part of the known classes $\mathcal{C}_s$.
 
@@
 
-Let's denote with $rot({\bf x}, i)$ the rotation of the sample image {\bf x} by $i\times 90$ degrees clockwise.
-This is the self-supervised part of our proposed model as rotations $i \in [0, 3]$ can be randomly generated and then predicted.
-To avoid situations where the objective orientation of a sample would be a too complicated task, even for a human being, we also feed in input to the model the un-rotated image features.
-Alternatively, instead to have the model predict the rotation of a sample for any class, we also try using a different head for each one of the known classes $\mathcal{C}_s$, along with different loss functions.
+We denote with $rot({\bf x}, k)$ the rotation of the sample image {\bf x} by $k\times 90$ degrees clockwise.
+This is the self-supervised part of our proposed model as rotation indices $k \in [0, 3]$ can be randomly generated and then predicted.
+Relative rotation,
+meaning that both original and rotated features are supplied to the model,
+is preferred over just using rotated features as some objects might not have an absolute correct orientation.
+Alternatively, 
+instead of having the model predict the rotation of a sample for any class using the same classifier, 
+we also try using a different head for each one of the known classes $\mathcal{C}_s$.
 
@@
 
-To separate samples we train the model on an enhanced version of $\mathcal{D}_s$, $\tilde{\mathcal{D}_s} = \{({\bf x}_i^s, {\bf \tilde x}_i^s, z_i^s)\}_{i=1}^{N_s}$ where ${\bf \tilde x}_i^s$ is the rotated version of ${\bf x}_i^s$ and $z_i^s$ is the rotation index associated to image $i$.
-The network is composed by an extractor $E$ and two classifiers, $R_1$ and $C_1$ in its standard form.
-When using a multi-head rotation classifier, it is composed of $|\mathcal{C}_s|+1$ heads for the rotation task, and an additional one for the classification task.
-When using a multi-head predictor, which head to use during separation is chosen by the object classifier $C_1$.
-The features of both original and rotated image are used to predict the rotation as ${\bf \tilde z}_s = softmax(R_1([E({\bf x}^s), E({\bf\tilde x}^s)]))$ in the single-head case and using the $j$-th head as ${\bf\tilde{z}}_s = softmax(R_{1,j}[E({\bf x}^s), E({\bf\tilde{x}}^s)])$ in the multi-head case.
-Classes are predicted only using un-rotated features as $\tilde{\bf y}^s = softmax(C_1(E({\bf x}_i^s)))$.
-The model is training by minimizing an objective function defined as $\mathcal{L}_1 = \mathcal{L}_{C_1} + \mathcal{L}_{R_1}$.
-This is the sum of two cross-entropy loss functions as in:
+Separating samples requires iterating over $\tilde{\mathcal{D}_s} = \{({\bf x}_i^s, {\bf \tilde x}_i^s, z_i^s)\}_{i=1}^{N_s}$,
+where ${\bf \tilde x}_i^s$ is the $z_i^s\times 90$ degrees rotated version of ${\bf x}_i^s$.
+The network is composed by an extractor $E$ and two classifiers, 
+$R_1$ and $C_1$.
+$C_1$ is the object classifier, 
+assigning image labes $\tilde{y}_i^s \in \{0, \dots, |\mathcal{C}_s|\}$,
+while $R_1$ is the relative rotation classifier,
+assigning rotation indices $\tilde{z}_i^s \in [0, 3]$.
+${\bf\tilde{z}}_i^s$ and ${\bf\tilde{y}}_i^s$ are the vector representations of $\tilde{z}_i^s$ and $\tilde{y}_i^s$.
+The multi-head rotation classifier uses $|\mathcal{C}_s|$ heads for the rotation task.
+In this case, 
+which head to use during separation is up to the object classifier $C_1$.
+Object predictions are made as ${\bf\tilde{x}}_i^s = softmax(E({\bf x}_i^s))$,
+while relative rotation predictions are computed as ${\bf \tilde z}_s = softmax(R_1([E({\bf x}^s), E({\bf\tilde x}^s)]))$.
+If a multi-head rotation classifier is used,
+the $j = y_i^s$ head is used as ${\bf\tilde{z}}_s = softmax(R_{1,j}[E({\bf x}^s), E({\bf\tilde{x}}^s)])$.
+The model is trained to minimizing the objective function $\mathcal{L}_1 = \mathcal{L}_{C_1} + \mathcal{L}_{R_1}$.
+This is the sum of two cross-entropy loss functions:
 
@@
 Where $\alpha_1$ is a weight associated to the rotation task.
-We also try using an extended rotation objective function $\mathcal{L}_{R_1}^*$ also implementing a center loss function\cite{CenterLoss}:
+We also try using an extended rotation loss function $\mathcal{L}_{R_1}^*$ implementing an additional center loss\cite{CenterLoss} term:
 
@@
 
-Here {\bf $v_i$} is the penultimate layer of the rotation classifier, called {\it features}, and $\gamma({\bf z}_i)$ gives the center of the features ${\bf v}_i$ associated to class $i$ and $||\cdot||_2^2$ is the $l$-2 norm and $\lambda_1$ is the weight associated with this extension of the loss function.
+Here ${\bf v_i}$ is the penultimate layer of the rotation classifier,
+called features, 
+$\gamma({\bf z}_i)$ is the center of the features associated to class $i$,
+$||\cdot||_2^2$ is the $l$-2 norm and $\lambda_1$ is the weight associated with the center loss term.
 
-When training is completed, we can start separating samples.
-To do so, we get the normality score $\mathcal{N}(\cdot)$ which is defined as the maximum prediction of the rotation classifier, $\mathcal{N}({\bf\tilde{x}}_i^s) = \max({\bf\tilde{z}}_i^t)$.
-To tell wheter a sample belongs to the known samples of the target domain $\mathcal{D}_t^{knw}$ or the unknown one $\mathcal{D}_t^{unk}$ requires choosing a threshold $\tilde{\mathcal{N}}$.
-Then we can simply separate as:
+When training is completed, 
+we can start separating samples.
+To do so,
+normality scores $\mathcal{N}(\cdot)$ are used,
+defined as the maximum prediction of the rotation classifier:
+$\mathcal{N}({\bf\tilde{x}}_i) = \max({\bf\tilde{z}}_i)$.
+To predict wheter a sample belongs to the known samples of the target domain $\mathcal{D}_t^{knw}$ or the unknown ones $\mathcal{D}_t^{unk}$ requires picking a threshold $\tilde{\mathcal{N}}$.
+The separation is then done as:
 
@@
   \begin{cases}
-    {\bf\tilde x}_i^t \in \mathcal{D}_t^{knw} & \text{ if } \mathcal{N}({\bf\tilde x}_i^s) \geq \tilde{\mathcal{N}} \\
-    {\bf\tilde x}_i^t \in \mathcal{D}_t^{unk} & \text{ if } \mathcal{N}({\bf\tilde x}_i^s) < \tilde{\mathcal{N}}
+    {\bf x}_i^t \in \mathcal{D}_t^{knw} & \text{ if } \mathcal{N}({\bf\tilde x}_i^t) \geq \tilde{\mathcal{N}} \\
+    {\bf x}_i^t \in \mathcal{D}_t^{unk} & \text{ if } \mathcal{N}({\bf\tilde x}_i^t) < \tilde{\mathcal{N}}
   \end{cases}
@@
 
-When employing a multi-head architecture, we need to choose which one of the $|\mathcal{C}_s|$ heads to use for the classification task.
-Head $R_{1,j}$ is used by picking $j$ as $\displaystyle j = \arg\max_j {\bf\tilde{y}}_i^t$.
+When using a multi-head rotation classifier, 
+it is required to choose among the $|\mathcal{C}_s|$ possible heads to make the prediction.
+Head $R_{1,j}$ is used by choosing $j$ as $\displaystyle j = \arg\max_j {\bf\tilde{y}}_i^t$.
 
@@
 
-In this phase, two "new" datasets are used.
+In this phase,
+we build two "new" datasets.
 The first one is $\mathcal{D}_s^*$, composed as $\mathcal{D}_s \cup \mathcal{D}_t^{unk}$.
-Note that since $\mathcal{D}_t$ is an unlabeled dataset but $\mathcal{D}_s^*$ is a labeled one, all samples in $\mathcal{D}_t^{unk}$ are simply labeled as unknowns.
-The second one is $\mathcal{D}_t^{knw}$ which is still an unlabeled dataset.
-Here we also introduce two new classifiers, $C_2$ and $R_2$.
-$C_2$ is the object classifier, but while $C_1$ had a $|\mathcal{C}_s|$-dimensional output, having to accomodate the new "Unknown" class, it has a $|\mathcal{C}_s|+1$-dimensional output.
-$R_2$ instead is the rotation classifier, which in this step is always single-headed and has its own weight $\alpha_2$.
-These two classifiers try to minimize the objective function described in equations \ref{eq:baseloss_class} and \ref{eq:baseloss_rot}.
-One of the main differences between the two steps is that while in the first one we used $C_1$ to regularize the rotation task, here we use $R_2$ to regularize the main classification task.
+Since $\mathcal{D}_t$ is an unlabeled dataset but $\mathcal{D}_s^*$ is a labeled one,
+samples in $\mathcal{D}_t^{unk}$ are labeled as unknowns.
+The second one is $\mathcal{D}_t^{knw}$.
+Here we also use two new classifiers,
+$C_2$ and $R_2$,
+similarly to how they were used in the first phase but with $C_2$ predicting $|\mathcal{C}_s|+1$ classes to accomodate unknown predictions.
+In this step $R_2$ is always single-headed and has its own weight $\alpha_2$.
+The objective function is the same described in equations \ref{eq:baseloss_class} and \ref{eq:baseloss_rot}.
+The main difference here is that $C_2$ is actually trained to recognize unknown classes,
+on both domains.
 
@@
 Evaluating model perfomance requires finding a balance between two values:
-{\it OS*}, the share of correctly classified samples;
-{\it UNK}, the share of correclty rejected samples.
-A model never confident enough to reject a sample as unknown could still achieve high {\it OS*} scores and near-zero {\it UNK}, while a model marking every given sample as unkwnown will achieve perfect {\it UNK} and zero {\it OS*}.
-To compare models in a robust manner, we picked an harmonic mean between {\it OS*} and {\it UNK}, defined as $HOS = 2\frac{OS^*\times UNK}{OS^*+UNK}$.
-This type of mean is more biased towards the lowest of the two scores, resulting in a more severe evaluation of models.
+{\it OS*}, 
+the fraction of correctly classified samples,
+and {\it UNK}, 
+the fraction of correclty rejected samples.
+A model not confident enough to reject a sample could still achieve high {\it OS*} values but near-zero {\it UNK},
+while a model rejecting every  sample as unkwnown will achieve perfect {\it UNK} and zero {\it OS*}.
+To compare models we use the harmonic mean between {\it OS*} and {\it UNK}, 
+defined as $HOS = 2\frac{OS^*\times UNK}{OS^*+UNK}$.
+This is because this kind of mean tends gives a bigger weight to the smaller values,
+resulting in a more severe evaluation of models.
 
@@
 
-Our model is tested on the {\it Office-Home} dataset\cite{OfficeHomeDataset}, which features $65$ classes of images over four different domains: Art (A), Clipart (C), Product (P) and Real World (R).
-We set the first $45$ classes to be known while the remaining $20$ are unknown.
-After each epoch performed during the domain alignment phase, a validation run is performed on the entire original target dataset.
-For each experiment, we report both the best achieved HOS and the last reported HOS.
-As separation is crucial for the model effectiveness, we also report the computer AUROC score for the first part.
+Our model is tested on the {\it Office-Home} dataset\cite{OfficeHomeDataset}, 
+which features 65 classes of images over four different domains: Art (A), Clipart (C), Product (P) and Real World (R).
+We set the first 45 classes to be known while the remaining 20 are unknown.
+For each experiment, 
+we report both the best achieved HOS as well as the last reported HOS.
+As separation is crucial for the model effectiveness,
+ we also report the computer AUROC score for the first part.
 
@@
 \label{sec:results}
-Table \ref{tab:results} contains the results for all 12 (ne abbiamo provati davvero 12???) possible domain shifts, as well as perfomance differences when using multi-head rotation classifiers and center loss.
-Each mode has a specific configuration further discussed in \ref{sec:ablation_study}.
+Table \ref{tab:results} contains the results for all 12 {\bf (ne abbiamo provati davvero 12???)} available domain shifts,
+as well as perfomance differences when using multi-head rotation classifiers and center loss.
+Further details are to be found in \ref{sec:ablation_study}.
+We can notice that multi-headed models are more capable of correctly discriminating between known and unknown samples,
+ultimately resulting in better domain alignment.
+A further advantage is given when combined with center loss.
 

### 2022-02-10 paper/main.tex
Implementation Details Rephrase #1

@@
 as well as perfomance differences when using multi-head rotation classifiers and center loss.
-Further details are to be found in \ref{sec:ablation_study}.
+Further details are to be found in section \ref{sec:implementation_details}.
 We can notice that multi-headed models are more capable of correctly discriminating between known and unknown samples,
@@
 A further advantage is given when combined with center loss.
+AUROC values are computed at the end of the separation stage, 
+while HOS values are sampled at regular times on the entire original target dataset.
 
@@
     \hline
-    Source & Target & AUROC & HOS & HOS$_{Best}$ \\
+    Source & Target & AUROC & HOS & HOS* \\
     S & T & 50\% & 30\% & 30\% \\
@@
   \end{tabular}
-  \caption{\label{tab:results}Test Caption}
+  \caption{\centering\label{tab:results}Results for domain alignment. AUROC is the area under the ROC. HOS is latest achieved HOS, HOS* the best achieved through all epochs.}
 \end{table}
@@
 \section{Implementation Details}
+\label{sec:implementation_details}
 \subsection{Model Parameters}
@@
 
-All models were run using a Stochastic Gradient Descent with batch size 32, a weight decay of 0.0005 and momentum set to 0.9.
-For single-headed models, the base learning rate is set to 0.001 and for multi-headed models it is set to 0.003.
-This is because multi-headed models take a longer time to converge.
-All rotation classifier have the learning rate set to a tenth of the base learning rate.
-Learning rates are reduced by a factor of 10 after 90\% of epochs.
+All models were run using stochastic gradient descent with batch size 32,
+a weight decay of 0.0005 and momentum of 0.9.
+For single-headed models, 
+a base learning rate of 0.001 is used,
+while for multi-headed models it is set to 0.003.
+This is because only one head of the heads is trained with each samples,
+so the process needs to be sped up.
+Rotation classifier use a learning rate set to a tenth of the base learning rate.
+A step learning rate scheduler is used, reducing it by a factor of 10 after 90\% of epochs.
 All models are run for 50 epochs for the first step described in \ref{eq:sample_separation} and for 25 epochs for the second step described in \ref{sec:domain_alignment}.
-For model using the center loss, a centroid learning rate of 0.5 is used.
-Other parameters are configuration-sepcific and reported in table \ref{tab:params}.
-When considering a "No Rotation" model, it is meant that $\alpha_2 = 0$ is used.
+For model using the center loss a centroid learning rate of 0.5 is used.
+All other parameters are configuration-sepcific and are reported in table \ref{tab:params}.
+"No Rotation" model is the same as a single-head without center loss model with $\alpha_2 = 0$.
+
+% % %
+
+{\it Extractor E}: The extractor employed is a ResNet-34{\bf[Inserire cit a ResNet]} {\bf è pretrained???} {\bf ma 34 o 18???} for all classifiers.
+
+{\it Classifier $C_1$, $C_2$}: $C_1$ is composed of a 45 dimensional output. 
+All unknown samples are mapped as belonging to class 45.
+$C_1$ is used as a starting point for $C_2$.
+As no unknowns are present on the source dataset (they are removed),
+the weight of unknwon samples in the second step is set to {\bf spiegare come è bilanciato} while for all other classes it is set to 1.
+A single fully connected layer $512\to 45$ with batch-norm is used.
+
+{\it Classifier $R_1$, $R_2$}: 
+$R_1$ and $R_2$ are composed by a $1024\to 256$  and a $256\to 4$ fully connected layers, named {\it Discriminators}.
+The 256-dimensional output are the features used by the center loss for inferring class centers.
+If multi-head is used, each head is a separate discriminator.
+$R_2$ is always a single-head classifier, even if using a multi-head rotation classifier.
 
@@
 \label{sec:ablation_study}
-As shown by table \ref{tab:results}, different architectures greatly improve performance, and as shown by table \ref{tab:params} each one has its set of optimal parameters.
-To choose the best parameters, a sequential approach is followed, by optimizing one parameter at the time.
-The order of optimization followed is: $\alpha_1$, $\lambda_1$, $\mathcal{\tilde N}$, $\alpha_2$.
-Models not using center loss skip the $\lambda_1$ optimization.
-Ablation study were run on two domain shift, Art $\to$ Clipart and Clipart $\to$ Art.
-In table \ref{tab:ablation_params} we report the steps followed, picking the parameter that gives the highest mean HOS between the two shifts.
+As shown in table \ref{tab:results} different architectures give different results, 
+and as shown in table \ref{tab:params} each one requires a different set of parameters.
+To choose optimal parameters a sequential approach is followed, 
+by optimizing one parameter at the time.
+The order of optimization followed is: 
+$\alpha_1$, $\lambda_1$, $\mathcal{\tilde N}$, $\alpha_2$.
+Models not using center loss just skip the $\lambda_1$ optimization.
+Ablation study were run on two domain shifts, 
+Art $\to$ Clipart and Clipart $\to$ Product.
+In table \ref{tab:ablation_params} we report the steps followed.
 All other settings follow what is reported in \ref{sec:model_parameters}.
-For compactness, here are the final results of the data otherwise reported from \ref{tab:ablationoffoff} on.
+The result here obtained are the same reported in table \ref{tab:params}.
 
@@
   \centering
-  \begin{tabular}[h]{||c|c|c|c||c||}
+  \begin{tabular}[h]{||c|c|c||c|c||}
     \hline

### 2022-02-11 paper/main.tex
Picture???
Abastract section updated

@@
 \begin{abstract}
-  Performance loss over domain change is a common problem in machine learning applications.
-  Solving the issue usually relies on adapting the model to the new domain by having at disposal large and labeled datasets, either rare or costly to acquire.
-  In this paper we propose a new approach, adapting models to the new domains while not needing relying on labeled data thanks to a self-supervision.
-  Experiments conducted on the Office-Home dataset show interesting results and method effectiveness.
+  In machine learning applications, domain adaptation (DA) techniques try to mitigate the problem of having different domains in the training and test data.
+  Another common problem is represented by the presence of more semantic classes in the test data, which are unknown
+  and completely new to the developed models. The latter problem comes under the name of novelty or anomaly detection.
+  In real world scenarios, it is becoming extremely common suffering of both problems.
+  \textit{Open-Set Domain Adaptation (OSDA)} methods try to tackle these problems by jointly adapting a labeled source domain to an unlabeled target domain
+  while performing novelty detection. We propose a new method leveraging a self-supervised technique, rotation recognition, constisting in first performing
+  novelty detection on the target data and then aligning the two domains avoiding potential negative adaptation.
+  Furthermore, we assess the performance using a new metric which represents in a balanced way the ability to jointly solve the two problems.
+  Experiments conducted on the Office-Home benchmark show interesting results and method effectiveness.
+
+  % Performance loss over domain change is a common problem in machine learning applications.
+  % Solving the issue usually relies on adapting the model to the new domain by having at disposal large and labeled datasets, either rare or costly to acquire.
+  % In this paper we propose a new approach, adapting models to the new domains while not needing relying on labeled data thanks to a self-supervision.
+  % Experiments conducted on the Office-Home dataset show interesting results and method effectiveness.
 \end{abstract}
@@
 \label{sec:domain_alignment}
+
+\begin{figure*}
+  \includegraphics[width=\textwidth ]{scheme.png}
+  \caption{\label{fig:separation} Schema representing the target images separation process}
+\end{figure*}
 

### 2022-02-11 paper/main.tex
Abastract updated

@@
   In real world scenarios, it is becoming extremely common suffering of both problems.
-  \textit{Open-Set Domain Adaptation (OSDA)} methods try to tackle these problems by jointly adapting a labeled source domain to an unlabeled target domain
+  \textit{Open-Set Domain Adaptation (OSDA)} methods try to tackle these problems by jointly adapting a model trained on a labeled source domain to an unlabeled target domain
   while performing novelty detection. We propose a new method leveraging a self-supervised technique, rotation recognition, constisting in first performing
@@
 \label{sec:intro}
+
 Classical machine learning in the past years has made some oversimplified assumptions actually detached % Punteggiatura?

### 2022-02-11 paper/main.tex
introduction reviewed

@@
 \label{sec:intro}
+Nowadays, the widespread usage of deep neural networks to accomplish computer vision tasks has brought huge benefits.
+In real world applications, as the tasks to cope with are becoming more and more challenging, machine learning methods commonly suffer of a gap between the performance
+obtained during the development, and the actual performance observed in real usages.
 
-Classical machine learning in the past years has made some oversimplified assumptions actually detached % Punteggiatura?
-from the usage of artificial intelligence systems in everyday real world and the problems they come with.
+One of the problems which is causing this loss of performance is the domain gap between the training data and the actual observed data. Intuitively, if we train a model on a specific domain,
+such as employing real world pictures depicting real objects, for example to perform classification, we expect that the model will perform well on a fairly large variety of test cases.
+However, the actual data present a huge variety on the domains while still representing the same semantic classes that we want to predict.
+For example, we may want to be capable of predicting that both an image of a real elephant and a drawing of an elephant are containing the semantic class \textit{elephant}.
+Domain adaptation techniques have been developing in recent years to reduce the domain gap between a labeled source domain and one or more unlabeled target domains.
+Generally, this is done by enforcing the learning of domain-invariant patterns of both domains.
+As underlined in \cite{domainAdaptFarahani}, this is usually achieved by learning a transformation function which projects both the source and target domain data in a
+new space where we jointly maintain the underlying structure of the original data while reducing the domain gap by removing the domain-specific information.
 
-The first assumption is that training and test sets come from the same distributions:
-a model trained on labeled data is expected to perform as well as on the test data.
-However, this assumption not always holds in real-world applications, 
-where naively applying the trained model on a new dataset may cause degradation in the performance.
-To solve this problem Domain Adaptation is widely used, 
-where the goal is to train a neural network on a source dataset for which labels are available and search for good performance on a target dataset, 
-which is related to but significantly different from the source dataset, 
-and whose label or annotation is not available. 
-Generally this is done by by minimizing the difference between domain distributions and enforcing the recognition of domain invariant patterns in both domains. 
-As underlined in \cite{domainAdaptFarahani}, 
-this is usually achieved by mapping source and target data by learning transformations for extracting such features and minimizing the gap between domains in the new representation space in an optimization procedure,
-while preserving the underlying structure of the original data.
+Another big issue encountered in real world usages is the presence of additional anomaly semantic classes on the observed data.
+The problem comes under the name of \textit{Open-Set Recognition (OSR)} \cite{OSRsurvey}, where we require not only to accurately classify the known seen classes, but also
+effectively deal with unknown ones, which would otherwise drastically weaken the robustness of the methods.
 
-Secondly, 
-in real-world classification tasks it is usually difficult to collect training samples to exhaust all classes when training a model.
-A more realistic scenario is open set recognition (OSR) \cite{OSRsurvey},
-where incomplete knowledge of the world exists at training time and unknown classes can be injected during testing, 
-requiring classifiers to not only accurately classify the seen classes but also effectively deal with unseen ones,
-which would otherwise drastically weaken the robustness of the methods.
-On the contrary this system should reject unknown classes at test time and separate the known and unknown samples.
-As underlined by \cite{OSRclassRec}, 
-existing open-set classifiers rely on deep networks trained in a supervised fashion on known classes in the training set;
-this causes specialization of learned representations to known classes and makes it hard to distinguish the unknowns from the knowns.
+The jointly presence and accounting of the two described problems has been emerged as a new sub-field of computer vision with the name of \textit{Open-Set Domain Adaptation (OSDA)}.
+As a consequence, if we try to reduce the domain gap between the whole target domain and the source domain, we will observe a negative adaptation due to the unwanted alignment between
+the data belonging to the anomaly semantic classes and the source classes we want to model and predict.
+For this reason, it is important to first perform anomaly detection of the additional set of novelty classes, translating the problem into a \textit{Closed-Set Domain Adaptation (CSDA)} one,
+and next do the alignment between the source and the target domain identified as known.
 
-To solve these significant issues our method is focused on a self-supervised task. 
-Self-supervised learning is an unsupervised learning technique where the supervised task is created out of the unlabeled input data. 
-This task could be as simple as predicting the lower half of an image being given the upper half of the same.
-Supervised learning requires both labeled and high quality data,
-usually very expensive, 
-whereas unlabeled data is often readily available in abundance.
-The fundamental idea behind self-supervised learning is creating some auxiliary task from input data so that,
-by solving such task,
-the model can learn the underlying structure of the data,
-for instance high-level knowledge, correlations, and metadata embedded in the data.
-This type of learning was recently used for Domain Adaptation, 
+Common machine learning methods usually leverage huge manually annotated datasets to perform well on the given tasks.
+However, acquiring annotated material is usually very costly and difficult, moreover, relying on such data may not be scalable in large applications on the long run.
+Thus, recently, unsupervised learning techniques are becoming crucial to cope with the aforementioned problems.
+One of those is self-supervised learning, which consists in creating new automatically labeled data starting from the original unlabeled data.
+The fundamental idea is creating some auxiliary task from input data so that,
+by solving such task, the model can learn the underlying structure of the data,
+for instance high-level knowledge, correlations, and metadata embedded.
+This type of learning has been recently used for Domain Adaptation, 
 learning robust cross-domain features and supporting generalization \cite{CarlucciJigsaw,SelfSupervisedXu},
@@
 
-The approach presented in this paper brings these topics together in the so called Open-Set Domain Adaptation (OSDA) problem. 
+The approach presented in this paper combines the power of the self-supervised learning with the standard supervised learning approach for semantic class recognition.
 A two-stage method is hence proposed, 
@@
 before reducing in the second stage the domain gap between the source domain and the known target domain to avoid negative transfer.
-This is done in both stages using a modified version of the rotation task as self-supervised model,
+This is done in both stages using a modified version of the rotation task as self-supervised method,
 predicting the relative rotation between an image and its rotated version.
-Finally a classifier is used to predict if each target sample belongs either to one of the knwon classes or to an unknown class, 
+Finally, a classifier is used to predict if each target sample belongs either to one of the knwon classes or to an unknown class, 
 being rejected in the latter case.
+We evaluate the method on the Office-Home benchmark \cite{OfficeHomeDataset} exploiting a new OSDA metric.
 
-The method was evaluated on the Office-Home benchmark \cite{OfficeHomeDataset} with a specific OSDA metric.
+To wrap up, our \textbf{main contributions} are: 
+\begin{enumerate}
+  \item we define a new method to tackle OSDA problems which exploits the rotation recognition task to perform both the known/unknown target separation
+and the domain adaptation;
+  \item we introduce a new OSDA metric which properly balances the measure of both the performance on predicting the known classes and the performance on doing the unknown rejection;
+  \item we conduct an extensive ablation over the hyperparameters for different variants of the self-supervised task underlying the benefits of some techniques over others.
+\end{enumerate}
 
-{\bf ADD HERE RESULTS AND A BRIEF OF CONCLUSIVE IDEAS (ALSO POSSIBLE FUTURE WORKS)!!}
+% Classical machine learning in the past years has made some oversimplified assumptions actually detached % Punteggiatura?
+% from the usage of artificial intelligence systems in everyday real world and the problems they come with.
+
+% The first assumption is that training and test sets come from the same distributions:
+% a model trained on labeled data is expected to perform as well as on the test data.
+% However, this assumption not always holds in real-world applications, 
+% where naively applying the trained model on a new dataset may cause degradation in the performance.
+% To solve this problem Domain Adaptation is widely used, 
+% where the goal is to train a neural network on a source dataset for which labels are available and search for good performance on a target dataset, 
+% which is related to but significantly different from the source dataset, 
+% and whose label or annotation is not available. 
+% Generally this is done by by minimizing the difference between domain distributions and enforcing the recognition of domain invariant patterns in both domains. 
+% As underlined in \cite{domainAdaptFarahani}, 
+% this is usually achieved by mapping source and target data by learning transformations for extracting such features and minimizing the gap between domains in the new representation space in an optimization procedure,
+% while preserving the underlying structure of the original data.
+
+% Secondly, 
+% in real-world classification tasks it is usually difficult to collect training samples to exhaust all classes when training a model.
+% A more realistic scenario is open set recognition (OSR) \cite{OSRsurvey},
+% where incomplete knowledge of the world exists at training time and unknown classes can be injected during testing, 
+% requiring classifiers to not only accurately classify the seen classes but also effectively deal with unseen ones,
+% which would otherwise drastically weaken the robustness of the methods.
+% On the contrary this system should reject unknown classes at test time and separate the known and unknown samples.
+% As underlined by \cite{OSRclassRec}, 
+% existing open-set classifiers rely on deep networks trained in a supervised fashion on known classes in the training set;
+% this causes specialization of learned representations to known classes and makes it hard to distinguish the unknowns from the knowns.
+
+% To solve these significant issues our method is focused on a self-supervised task. 
+% Self-supervised learning is an unsupervised learning technique where the supervised task is created out of the unlabeled input data. 
+% This task could be as simple as predicting the lower half of an image being given the upper half of the same.
+% Supervised learning requires both labeled and high quality data,
+% usually very expensive, 
+% whereas unlabeled data is often readily available in abundance.
+% The fundamental idea behind self-supervised learning is creating some auxiliary task from input data so that,
+% by solving such task,
+% the model can learn the underlying structure of the data,
+% for instance high-level knowledge, correlations, and metadata embedded in the data.
+% This type of learning was recently used for Domain Adaptation, 
+% learning robust cross-domain features and supporting generalization \cite{CarlucciJigsaw,SelfSupervisedXu},
+% and also for some Open Set problems specialized in anomaly detection and discriminating anomalous data \cite{bergman2020classificationbased,dectionGeometric}.
+
+% The approach presented in this paper brings these topics together in the so called Open-Set Domain Adaptation (OSDA) problem. 
+% A two-stage method is hence proposed, 
+% aiming to identify and isolate unknown class samples in the first stage, 
+% before reducing in the second stage the domain gap between the source domain and the known target domain to avoid negative transfer.
+% This is done in both stages using a modified version of the rotation task as self-supervised model,
+% predicting the relative rotation between an image and its rotated version.
+% Finally a classifier is used to predict if each target sample belongs either to one of the knwon classes or to an unknown class, 
+% being rejected in the latter case.
+
+% The method was evaluated on the Office-Home benchmark \cite{OfficeHomeDataset} with a specific OSDA metric.
+
+% {\bf ADD HERE RESULTS AND A BRIEF OF CONCLUSIVE IDEAS (ALSO POSSIBLE FUTURE WORKS)!!}
 

### 2022-02-11 paper/main.tex
3.1 Problem formulation and 3.2 Approach reviewed

@@
 \label{sec:problemformulation}
-Our starting point is the source dataset, 
-defined as $\mathcal{D}_s = \{({\bf x}_i^s, y_i^s)\}_{i=1}^{N_S} \sim p_s$, 
-where each element ${\bf x}_i^s$ belonging to class $y_i^s$ is a sample from the source domain {\it S}.
-This dataset has a target counterpart, 
-$\mathcal{D}_t = \{{\bf x}_i^t\}_{i=1}^{N_t} \sim p_t$ which is unlabeled instead.
-In OSDA we have that $p_s \neq p_t$.
+We define as $\mathcal{D}_s = \{({\bf x}_i^s, y_i^s)\}_{i=1}^{N_S} \sim p_s$ the source dataset whose distribution of samples and labels is $p_s$,
+while $\mathcal{D}_t = \{{\bf x}_i^t\}_{i=1}^{N_t} \sim p_t$ is the unlabeled target dataset drawn from distribution $p_t$.
+
 The source dataset $\mathcal{D}_s$ is associated with a set of known classes $\mathcal{C}_s$,
-which can also be found in the target dataset $\mathcal{D}_t$ but is supposedly smaller.
+whereas the target dataset $\mathcal{D}_t$ contains a set of classes $\mathcal{C}_t = \mathcal{C}_s \cup \mathcal{C}_{t \setminus s}$.
 In other words,
 $|\mathcal{C}_s| < |\mathcal{C}_t|$ and $\mathcal{C}_s \subset \mathcal{C}_t$.
-In domain adaptation, 
-we further have that the target distribution of the known source classes differs from the target distribution of known classes,
-so $p_t^s \neq p_s$, 
-A metric to measure how different two domains are is the openness betweeen source and target domain\cite{bendale2015open}, 
+
+In OSDA we have that $p_s \neq p_t$.
+Moreover, it holds that $p_s \neq p_t^{\mathcal{C}_s}$, where $p_t^{\mathcal{C}_s}$ denotes the distribution of the target domain if we restrict to
+the shared classes $\mathcal{C}_s$.
+
+Summarizing, in OSDA tasks, we have both a domain gap ($p_s \neq p_t^{\mathcal{C}_s}$)
+and a category gap ($\mathcal{C}_s \neq \mathcal{C}_t$). Moreover, the goal is to assign the target samples either to a category ${i \in \mathcal{C}_s}$,
+or to reject them as {\it unknown}.
+A metric to measure the complexity of the OSDA problem is the {\it openness} betweeen the source and the target domain \cite{bendale2015open}, 
 defined as $\displaystyle \mathbb{O} = 1-\frac{\mathcal{C}_s}{\mathcal{C}_t}$.
-When $\mathbb{O} > 0$, we're dealing with an OSDA problem.
+When $\mathbb{O} > 0$, we are dealing with an OSDA problem, otherwise we are in a in a CSDA setting.
 
@@
 \label{sec:apporach}
-The task is split in two separate stages.
-First, 
-we have to train the model to separate between the known classes ($\mathcal{C}_s$) and the unknown classes ($\mathcal{C}_{t\setminus s})$ in a reliable way.
-This is achieved via the self-supervised task,
-training the model to both recognize the class of a sample and its relative orientation.
-Secondly,
-we train the model on a union of both source and target datasets,
-to reject samples when they are not part of the known classes $\mathcal{C}_s$.
+The proposed method is split in two sequential stages. First, to avoid negative transfer during the domain alignment step, we want a model
+that is able to separate the target dataset into $\mathcal{D}_{t, unknown}$ and $\mathcal{D}_{t, known}$. To do that, we leverage the
+power of the rotation pre-text task to perform the separation.
+Next, in the second stage, we can close the gap between the source domain and the target domain exploiting $\mathcal{D}_{t, known}$
+using the same self-supervised task. Furthermore, we leverage $\mathcal{D}_{t, unknown}$ to learn the additional {\it unknown} class.
 

### 2022-02-11 paper/main.tex
3.3 Rotation Recognition reviewed

@@
 defined as $\displaystyle \mathbb{O} = 1-\frac{\mathcal{C}_s}{\mathcal{C}_t}$.
-When $\mathbb{O} > 0$, we are dealing with an OSDA problem, otherwise we are in a in a CSDA setting.
+When $\mathbb{O} > 0$, we are dealing with an OSDA problem, otherwise we are in a CSDA setting.
 
@@
 
-We denote with $rot({\bf x}, k)$ the rotation of the sample image {\bf x} by $k\times 90$ degrees clockwise.
-This is the self-supervised part of our proposed model as rotation indices $k \in [0, 3]$ can be randomly generated and then predicted.
-Relative rotation,
-meaning that both original and rotated features are supplied to the model,
-is preferred over just using rotated features as some objects might not have an absolute correct orientation.
-Alternatively, 
-instead of having the model predict the rotation of a sample for any class using the same classifier, 
-we also try using a different head for each one of the known classes $\mathcal{C}_s$.
+We denote with $rot({\bf x}, k)$ the rotating function of a sample image {\bf x} by $k\times 90$ degrees clockwise.
+The self-supervised pre-text task consists in generating a random rotation index $k \in [0, 3]$ that then becomes
+the label for the rotated version of the image ${\bf \tilde{x}} = rot({\bf x}, k)$.
+Then, the task becomes a standard classification of the correct rotation index ($\mathcal{C}_r = \{0, 1, 2, 3\}$).
+
+{\it Relative orientation:}
+more precisely, we exploit a relative rotation task,
+implying that both the features of the original and rotated image are supplied to the rotation classifier.
+This is preferred over the absolute rotation task as some objects might not have an absolute coherent orientation
+inside the dataset
+(e.g. a pen may be present in different rotated versions inside the dataset).
+
+{\it Multi-head rotation classifier:}
+alternatively, 
+instead of having a single rotation head predicting the rotation of a sample regardless of its semantic class, 
+we also try using a different head for each known class $\in \mathcal{C}_s$, each one responsible of predicting the rotation
+of the images belonging to that semantic class.
+This variation can mitigate the problem of trying to predict the rotation of a larger number
+of semantic classes. Infact, as the number of semantic classes grows,
+the problem of predicting the relative orientation becomes more difficult.
+The application of the rotation recognition pre-text task allows to effectively favor and force the model to learn
+domain-independent patterns, which are crucial to perform the novelty detection in a cross-domain fashion and, moreover,
+to successfully perform the domain alignment.
+To provide an explanation of why this applies, we can think that a rotation classifier needs to focus on discriminative patterns to
+successfully perform the rotation predictions, such as shapes, edges, and high-level object relative position like the position of the eyes
+w.r.t nose.
+The method and its effectiveness is further illustrated in \cite{OldROS}. 
+We will further discuss possible improvements and variants in {\bf PLEASE COMPLETE}.
 

### 2022-02-11 paper/main.tex
fixed self-supervised learnign statement

@@
 However, acquiring annotated material is usually very costly and difficult, moreover, relying on such data may not be scalable in large applications on the long run.
-Thus, recently, unsupervised learning techniques are becoming crucial to cope with the aforementioned problems.
-One of those is self-supervised learning, which consists in creating new automatically labeled data starting from the original unlabeled data.
+Thus, recently, a commonly employed approach is self-supervised learning, which consists in creating new automatically labeled data starting from the original unlabeled data.
 The fundamental idea is creating some auxiliary task from input data so that,

### 2022-02-11 paper/main.tex
fixed student ids

@@
 Italy\\
-{\tt\small \{s286302,s292477,s292459,s292477\}@studenti.polito.it <- Riordinare}
+{\tt\small \{s286302,s292477,s292459,292435\}@studenti.polito.it <- Riordinare}
 % For a paper whose authors are all at the same institution,

### 2022-02-11 paper/main.tex
small fix

@@
 or to reject them as {\it unknown}.
-A metric to measure the complexity of the OSDA problem is the {\it openness} betweeen the source and the target domain \cite{bendale2015open}, 
+A metric to measure the complexity of an OSDA problem is the {\it openness} betweeen the source and the target domain \cite{bendale2015open}, 
 defined as $\displaystyle \mathbb{O} = 1-\frac{\mathcal{C}_s}{\mathcal{C}_t}$.

### 2022-02-11 paper/main.tex
small fix v2

@@
 more precisely, we exploit a relative rotation task,
-implying that both the features of the original and rotated image are supplied to the rotation classifier.
+which implies that both the features of the original and rotated image are supplied to the rotation classifier.
 This is preferred over the absolute rotation task as some objects might not have an absolute coherent orientation

### 2022-02-11 paper/main.tex
step1 fixed up to centroid

@@
 The proposed method is split in two sequential stages. First, to avoid negative transfer during the domain alignment step, we want a model
-that is able to separate the target dataset into $\mathcal{D}_{t, unknown}$ and $\mathcal{D}_{t, known}$. To do that, we leverage the
+that is able to separate the target dataset into $\mathcal{D}_t^{unk}$ and $\mathcal{D}_t^{knw}$. To do that, we leverage the
 power of the rotation pre-text task to perform the separation.
-Next, in the second stage, we can close the gap between the source domain and the target domain exploiting $\mathcal{D}_{t, known}$
-using the same self-supervised task. Furthermore, we leverage $\mathcal{D}_{t, unknown}$ to learn the additional {\it unknown} class.
+Next, in the second stage, we can close the gap between the source domain and the target domain exploiting $\mathcal{D}_t^{knw}$
+using the same self-supervised task. Furthermore, we leverage $\mathcal{D}_t^{unk}$ to learn the additional {\it unknown} class.
 
@@
 
-\subsection{Step I: Sample Separation}
+\subsection{Step I: target known/unknown separation}
 
-Separating samples requires iterating over $\tilde{\mathcal{D}_s} = \{({\bf x}_i^s, {\bf \tilde x}_i^s, z_i^s)\}_{i=1}^{N_s}$,
+To perform the target separation we train a CNN iterating on $\tilde{\mathcal{D}_s} = \{({\bf x}_i^s, {\bf \tilde x}_i^s, z_i^s)\}_{i=1}^{N_s}$,
 where ${\bf \tilde x}_i^s$ is the $z_i^s\times 90$ degrees rotated version of ${\bf x}_i^s$.
-The network is composed by an extractor $E$ and two classifiers, 
-$R_1$ and $C_1$.
-$C_1$ is the object classifier, 
-assigning image labes $\tilde{y}_i^s \in \{0, \dots, |\mathcal{C}_s|\}$,
-while $R_1$ is the relative rotation classifier,
-assigning rotation indices $\tilde{z}_i^s \in [0, 3]$.
-${\bf\tilde{z}}_i^s$ and ${\bf\tilde{y}}_i^s$ are the vector representations of $\tilde{z}_i^s$ and $\tilde{y}_i^s$.
-The multi-head rotation classifier uses $|\mathcal{C}_s|$ heads for the rotation task.
-In this case, 
-which head to use during separation is up to the object classifier $C_1$.
-Object predictions are made as ${\bf\tilde{x}}_i^s = softmax(E({\bf x}_i^s))$,
-while relative rotation predictions are computed as ${\bf \tilde z}_s = softmax(R_1([E({\bf x}^s), E({\bf\tilde x}^s)]))$.
-If a multi-head rotation classifier is used,
-the $j = y_i^s$ head is used as ${\bf\tilde{z}}_s = softmax(R_{1,j}[E({\bf x}^s), E({\bf\tilde{x}}^s)])$.
-The model is trained to minimizing the objective function $\mathcal{L}_1 = \mathcal{L}_{C_1} + \mathcal{L}_{R_1}$.
+The CNN is made of a feature extractor $E$ and two heads: $R_1$ and $C_1$.
+$C_1$ is the object classifier, which assigns to image ${\bf x}_i^s$ a predicted semantic class label,
+while $R_1$ is the relative rotation classifier, which assigns to the rotated image ${\bf \tilde x}_i^s$ a predicted rotation label.
+To keep the notation clear, we define as ${\bf y_i}$ and ${\bf z_i}$ the one-hot vector representations of the corresponding scalar labels.
+Notice that the multi-head rotation classifier internally uses $|\mathcal{C}_s|$ different heads for the rotation task.
+In this case, the head selected to perform the rotation prediction is up to the object classifier $C_1$ (during inference and not during training).
+
+The object class vector of predicted probabilities is computed as ${\bf \hat{y}_i^s} = softmax(C_1(E({\bf x_i^s})))$, while the vector of predicted probabilities
+for rotation label is computed from the stacked features of the original and rotated image ${\bf \hat{z}_i^s} = softmax(R_1([E({\bf x_i^s}), E({\bf \tilde{x}_i^s})]))$.
+The model is trained to minimize the objective function $\mathcal{L}_1 = \mathcal{L}_{C_1} + \mathcal{L}_{R_1}$.
 This is the sum of two cross-entropy loss functions:
@@
 \begin{equation}
-  \mathcal{L}_{C_1} = -\sum_{i\in\mathcal{D}_s} {\bf y}_i^s \log \tilde{\bf y}_i^s
+  \mathcal{L}_{C_1} = -\sum_{i\in\mathcal{D}_s} {\bf y}_i^s \log \hat{\bf y}_i^s
   \label{eq:baseloss_class}
@@
 \begin{equation}
-  \mathcal{L}_{R_1} = -\alpha_1\sum_{i\in\mathcal{\tilde{D}}_s} {\bf y}_i^s \log \tilde{{\bf z}}_i^s
+  \mathcal{L}_{R_1} = -\alpha_1\sum_{i\in\mathcal{\tilde{D}}_s} {\bf y}_i^s \log \hat{{\bf z}}_i^s
   \label{eq:baseloss_rot}
@@
 \begin{equation}
-  \mathcal{L}_{R_1}^* = -\alpha_1\sum_{i\in\mathcal{D}_s} {\bf y}_i^s \log \tilde{{\bf z}}_i^s+\lambda_1||{\bf v}_i^s-\gamma({\bf z}_i^s)||_2^2
+  \mathcal{L}_{R_1}^* = -\alpha_1\sum_{i\in\mathcal{\tilde{D}}_s} {\bf y}_i^s \log \hat{{\bf z}}_i^s+\lambda_1||{\bf v}_i^s-\gamma({\bf z}_i^s)||_2^2
   \label{eq:center_loss}
@@
 
-Here ${\bf v_i}$ is the penultimate layer of the rotation classifier,
-called features, 
-$\gamma({\bf z}_i)$ is the center of the features associated to class $i$,
+Here ${\bf v_i}$ is the output of the penultimate layer of $R_1$,
+$\gamma({\bf z}_i)$ is the centroid of the features associated to class $i$,
 $||\cdot||_2^2$ is the $l$-2 norm and $\lambda_1$ is the weight associated with the center loss term.

### 2022-02-11 paper/main.tex
fixed center loss statement

@@
 Here ${\bf v_i}$ is the output of the penultimate layer of $R_1$,
-$\gamma({\bf z}_i)$ is the centroid of the features associated to class $i$,
+$\gamma({\bf z}_i)$ is the centroid of the features associated to class $i$
+(notice that the centroid is relative to a different rotation class $i$ in the multi-head variant)
 $||\cdot||_2^2$ is the $l$-2 norm and $\lambda_1$ is the weight associated with the center loss term.

### 2022-02-11 paper/main.tex
Some small fixes to pedices and vectors

@@
 Italy\\
-{\tt\small \{s286302,s292477,s292459,292435\}@studenti.polito.it <- Riordinare}
+{\tt\small \{s286302,s292477,s292459,292435\}@studenti.polito.it}
 % For a paper whose authors are all at the same institution,
@@
 \label{sec:problemformulation}
-We define as $\mathcal{D}_s = \{({\bf x}_i^s, y_i^s)\}_{i=1}^{N_S} \sim p_s$ the source dataset whose distribution of samples and labels is $p_s$,
+We define as $\mathcal{D}_s = \{({\bf x}_i^s, y_i^s)\}_{i=1}^{N_s} \sim p_s$ the source dataset whose distribution of samples and labels is $p_s$,
 while $\mathcal{D}_t = \{{\bf x}_i^t\}_{i=1}^{N_t} \sim p_t$ is the unlabeled target dataset drawn from distribution $p_t$.
@@
 \begin{equation}
-  \mathcal{L}_{R_1} = -\alpha_1\sum_{i\in\mathcal{\tilde{D}}_s} {\bf y}_i^s \log \hat{{\bf z}}_i^s
+  \mathcal{L}_{R_1} = -\alpha_1\sum_{i\in\mathcal{\tilde{D}}_s} {\bf z}_i^s \log \hat{{\bf z}}_i^s
   \label{eq:baseloss_rot}
@@
 \begin{equation}
-  \mathcal{L}_{R_1}^* = -\alpha_1\sum_{i\in\mathcal{\tilde{D}}_s} {\bf y}_i^s \log \hat{{\bf z}}_i^s+\lambda_1||{\bf v}_i^s-\gamma({\bf z}_i^s)||_2^2
+  \mathcal{L}_{R_1}^* = -\alpha_1\sum_{i\in\mathcal{\tilde{D}}_s} {\bf z}_i^s \log \hat{{\bf z}}_i^s+\lambda_1||{\bf v}_i^s-\gamma({\bf z}_i^s)||_2^2
   \label{eq:center_loss}

### 2022-02-11 paper/main.tex
minor fixes

@@
 $\gamma({\bf z}_i)$ is the centroid of the features associated to class $i$
-(notice that the centroid is relative to a different rotation class $i$ in the multi-head variant)
+(notice that the centroid is relative to a different rotation class $i$ in the multi-head variant),
 $||\cdot||_2^2$ is the $l$-2 norm and $\lambda_1$ is the weight associated with the center loss term.

### 2022-02-11 paper/main.tex
fixed center loss loss formula
renamed lambda_1 into lambda

--- 2022-02-11 paper/main.tex
@@
 \begin{equation}
-  \mathcal{L}_{R_1}^* = -\alpha_1\sum_{i\in\mathcal{\tilde{D}}_s} {\bf z}_i^s \log \hat{{\bf z}}_i^s+\lambda_1||{\bf v}_i^s-\gamma({\bf z}_i^s)||_2^2
+  \mathcal{L}_{R_1}^* = \sum_{i\in\mathcal{\tilde{D}}_s} -\alpha_1{\bf z}_i^s \log \hat{{\bf z}}_i^s+\lambda||{\bf v}_i^s-\gamma({\bf z}_i^s)||_2^2
   \label{eq:center_loss}
@@
 $\gamma({\bf z}_i)$ is the centroid of the features associated to class $i$
-(notice that the centroid is relative to a different rotation class $i$ in the multi-head variant)
-$||\cdot||_2^2$ is the $l$-2 norm and $\lambda_1$ is the weight associated with the center loss term.
+(notice that the centroid is relative to a different rotation class $i$ in the multi-head variant),
+$||\cdot||_2^2$ is the $l$-2 norm and $\lambda$ is the weight associated with the center loss term.
 

### 2022-02-11 paper/main.tex
finished review of Step I

@@
 When training is completed, 
-we can start separating samples.
+we can start separating the target samples into known and unknown.
 To do so,
-normality scores $\mathcal{N}(\cdot)$ are used,
+{\it normality scores} $\mathcal{N}(\cdot)$ are used,
 defined as the maximum prediction of the rotation classifier:
-$\mathcal{N}({\bf\tilde{x}}_i) = \max({\bf\tilde{z}}_i)$.
-To predict wheter a sample belongs to the known samples of the target domain $\mathcal{D}_t^{knw}$ or the unknown ones $\mathcal{D}_t^{unk}$ requires picking a threshold $\tilde{\mathcal{N}}$.
-The separation is then done as:
+$\mathcal{N}({\bf\tilde{x}}_i) = \max({\bf\hat{z}}_i)$.
+Notice that, for each target sample, all the four rotations are applied and the resulting normality score for the sample
+is computed as the mean of the four normality scores.
+To decide if a target sample belongs to a known semantic class or not, we compare the normality score with a threshold $\tilde{\mathcal{N}}$.
 
@@
 it is required to choose among the $|\mathcal{C}_s|$ possible heads to make the prediction.
-Head $R_{1,j}$ is used by choosing $j$ as $\displaystyle j = \arg\max_j {\bf\tilde{y}}_i^t$.
+Head $R_{1,j}$ is used where $\displaystyle j = \arg\max_j \{{\bf\hat{y}}_{i, [j]}^t\}_{j=0}^{|\mathcal{C}_s|-1}$
+($j$ is the component $j$ of the vector).
 

### 2022-02-12 paper/main.tex
updated Step I

@@
 
+The key idea behind the normality score is that, if $R_1$ is confident enough on its predicted rotation,
+it is likely that it has managed to successfully recognize the rotation.
+Since $R_1$ has learned the domain-independent patterns of the known classes from the source dataset up to this point,
+it should be able to recognize the rotations applied only to images belonging to such classes.
+
 \subsection{Step II: Domain Alignment}

### 2022-02-12 paper/main.tex
Step II reviewed

@@
 The proposed method is split in two sequential stages. First, to avoid negative transfer during the domain alignment step, we want a model
-that is able to separate the target dataset into $\mathcal{D}_t^{unk}$ and $\mathcal{D}_t^{knw}$. To do that, we leverage the
+that is able to separate the target dataset into $\mathcal{D}_t^{unk}$, which contains images belonging to unknown classes,
+and $\mathcal{D}_t^{knw}$, which contains only images belonging to the known classes. To do that, we leverage the
 power of the rotation pre-text task to perform the separation.
@@
 
-\subsection{Step II: Domain Alignment}
+\subsection{Step II: domain alignment}
 \label{sec:domain_alignment}
@@
 
-In this phase,
-we build two "new" datasets.
-The first one is $\mathcal{D}_s^*$, composed as $\mathcal{D}_s \cup \mathcal{D}_t^{unk}$.
-Since $\mathcal{D}_t$ is an unlabeled dataset but $\mathcal{D}_s^*$ is a labeled one,
-samples in $\mathcal{D}_t^{unk}$ are labeled as unknowns.
-The second one is $\mathcal{D}_t^{knw}$.
-Here we also use two new classifiers,
-$C_2$ and $R_2$,
-similarly to how they were used in the first phase but with $C_2$ predicting $|\mathcal{C}_s|+1$ classes to accomodate unknown predictions.
-In this step $R_2$ is always single-headed and has its own weight $\alpha_2$.
-The objective function is the same described in equations \ref{eq:baseloss_class} and \ref{eq:baseloss_rot}.
-The main difference here is that $C_2$ is actually trained to recognize unknown classes,
-on both domains.
+In this step,
+having separated the target into a known part $\mathcal{D}_t^{knw}$,
+and an unknown part $\mathcal{D}_t^{unk}$,
+we arrange two new datasets in order to perform the domain alignment while also learning
+the unknown class.
+The first one is $\mathcal{D}_s^*$, composed as $\mathcal{D}_s \cup \mathcal{D}_t^{unk}$,
+which contains the original source images plus the target images identified as unknown classes.
+We thus set the labels for $\mathcal{D}_t^{unk}$ as the class {\it unknown}.
+The second one is $\mathcal{D}_t^{knw}$, which can be used to perform the domain alignment
+without the risk of negative transfer.
+While the feature extractor $E$ is inherited from the previous stage and leverages the previous training phase,
+we also use two new classifiers,
+$C_2$ and $R_2$.
+They are similar to the previous classifiers but they have two important differences.
+$C_2$ now has a $(|\mathcal{C}_s|+1)$-dimensional output to accomodate also the unknown class predictions and also
+benefits from the previous learning,
+while $R_2$ is always a single-head rotation classifier and starts the learning from scratch.
+The training phase is the same as before with the difference that we do not have the center loss this time.
+We also employ a different hyperparameter $\alpha_2$ to weigh the rotation classifier loss contribution.
+The objective function is again $\mathcal{L}_2 = \mathcal{L}_{C_2} + \mathcal{L}_{R_2}$,
+where the two contributions are identical to equations \ref{eq:baseloss_class} and \ref{eq:baseloss_rot}.
+We report the $\mathcal{L}_{R_2}$ loss contributions to make clear the usage of $\alpha_2$ and we
+recall that $\mathcal{L}_{C_2}$ is now computed using the new arranged dataset $\mathcal{D}_s^*$.
+
+\begin{equation}
+  \mathcal{L}_{R_2} = -\alpha_2\sum_{i\in\mathcal{D}_t^{knw}} {\bf z}_i^s \log \hat{{\bf z}}_i^s
+  \label{eq:baseloss_rot2}
+\end{equation}
 

### 2022-02-12 paper/main.tex
Step II updated

@@
 where the two contributions are identical to equations \ref{eq:baseloss_class} and \ref{eq:baseloss_rot}.
-We report the $\mathcal{L}_{R_2}$ loss contributions to make clear the usage of $\alpha_2$ and we
+We report the $\mathcal{L}_{R_2}$ loss contribution to make clear the usage of $\alpha_2$ and we
 recall that $\mathcal{L}_{C_2}$ is now computed using the new arranged dataset $\mathcal{D}_s^*$.

### 2022-02-12 paper/main.tex
3.6 Performance metrics reviewed

@@
 
-\subsection{Performance Metrics}
+\subsection{Performance metrics}
 \label{sec:performance_metrics}
 
-Evaluating model perfomance requires finding a balance between two values:
-{\it OS*}, 
-the fraction of correctly classified samples,
-and {\it UNK}, 
-the fraction of correclty rejected samples.
-A model not confident enough to reject a sample could still achieve high {\it OS*} values but near-zero {\it UNK},
-while a model rejecting every  sample as unkwnown will achieve perfect {\it UNK} and zero {\it OS*}.
-To compare models we use the harmonic mean between {\it OS*} and {\it UNK}, 
-defined as $HOS = 2\frac{OS^*\times UNK}{OS^*+UNK}$.
-This is because this kind of mean tends gives a bigger weight to the smaller values,
-resulting in a more severe evaluation of models.
+To have a meaningful comparison of the effectiveness
+of the models to solve OSDA problems, we need to resort to a metric which
+correctly measures the goodness of our predictions.
+The difficulty lies on the joint presence of two, usually conflicting, goals.
+We recall that an OSDA problem is characterized by the concurrent presence of
+a domain difference and a class set difference.
+The final goal is to correctly classify the samples belonging to known classes
+while rejecting the samples of unknown classes.
+The performance of both the goals are typically taken into account by two metrics, {\it OS*},
+which is the fraction of the correctly classified samples belonging to known classes, and {\it UNK},
+which in contrast is the accuracy over the correctly rejected samples.
+Since the goals are usually conflicting, we need an overall metric which is able to correctly balance
+the two contributions, providing low values if at least one of the two is low.
+We therefore pick the harmonic mean of the two contributions, defined as $HOS = 2\frac{OS^*\times UNK}{OS^*+UNK}$.
+We underline that $HOS$ is a more severe and fair metric to effectively measure the goodness of a model to perform well
+on a given OSDA problem because, from the definition of the harmonic mean, it tends to give a bigger weight to the smaller values.
 

### 2022-02-12 paper/main.tex
Benchmark section reviewed

@@
 
+Lastly, we also exploit the AUROC metric to assess the goodness of the system in separating
+the target into a known and unknown part.
+
 \section{Experiments}
@@
 
-\subsection{Dataset}
+\subsection{Benchmark}
 \label{sec:dataset}
 
-Our model is tested on the {\it Office-Home} dataset\cite{OfficeHomeDataset}, 
-which features 65 classes of images over four different domains: Art (A), Clipart (C), Product (P) and Real World (R).
-We set the first 45 classes to be known while the remaining 20 are unknown.
-For each experiment, 
-we report both the best achieved HOS as well as the last reported HOS.
-As separation is crucial for the model effectiveness,
- we also report the computer AUROC score for the first part.
+We evaluate the effectiveness of our proposed method exploiting the {\it Office-Home} {\bf INSERT REFERENCE} benchmark dataset,
+widely used to assess the performance for OSDA settings.
+The dataset is characterized by four different domains: Art (A), Clipart (C), Product (P) and Real World (R), and
+each domain contains the same 65 object class categories.
+We underline that the large domain gaps and the number of classes make the benchmark challenging.
+For the experiments, we fix the first 45 classes (in alphabetical order) as the known classes ($\mathcal{C}_s$),
+and the remaining 20 classes as the unknown ones ($\mathcal{C}_{t \setminus s}$).
+For each experiment, we collect the HOS value achieved after the last training epoch of the step 2,
+along with the AUROC value computed after the step 1, crucial to assess the goodness
+of the system's components responsible for the separation of the target.
 

### 2022-02-12 paper/main.tex
Implementation details

@@
 \subsection{Rotation Recognition}
+\label{sec:rotrecognition}
 
@@
 \subsection{Step I: target known/unknown separation}
+\label{sec:stepone}
 
@@
 
+\subsection{Implementation Details}
+\label{sec:implementation_details}
+
+As we have already seen in section \ref{sec:method}, the network is composed of a feature extractor $E$, and two heads, $C_{1/2}$ and $R_{1/2}$.
+For the feature extraction, we employ a ResNet-18 ({\bf INSERT REF}) pre-trained on ImageNet.
+All the experiments are run training with a batch size equals to 32 and using a stochastic gradient descent optimization strategy
+with a weight decay of 0.0005 and a momentum of 0.9.
+The learning rate is set to 0.001 in the cases where we use a single-head rotation classifier as $R_1$, and 0.003 in the multi-head case.
+The reason of this choice lies on the fact that, with a multi-head rotation classifier, we have to train 45 heads instead of a single one,
+so the training process needs to be speeded up.
+Moreover, we set a learning rate 10 times lower for the feature extractor weights.
+We also decrease the learning rate using a step learning rate scheduler, which reduces it by a factor of 10 after 90\% of total epochs.
+All models are trained for 50 epochs for the step one and for 25 epochs for the step two.
+For models using the center loss a centroid learning rate of 0.001 is used.
+The other hyperparameters are analyzed performing an ablation on section {\bf INSERT REF}.
+
+{\it Feature extractor E}: ResNet-18 pre-trained on ImageNet. It is also shared between step 1 and step 2.
+
+{\it Classifier $C_1$}:
+It is a simple linear classifier with a 45-dimensional output.
+
+{\it Classifier $C_2$}:
+Like $C_1$ but with a 46-dimensional output to consider also the unknown class. Furthermore, it leverages the learning already performed on $C_1$.
+It is worth noting that we rebalance the weight of the loss computed on samples belonging to the class unknown in the following way.
+After having separated the target into $\mathcal{D}_t^{knw}$ and $\mathcal{D}_t^{unk}$,
+we select the weight as $\frac{\mathcal{\bar{D}}_s}{|\mathcal{D}_t^{unk}|}$,
+where ${\mathcal{\bar{D}}_s}$ is the average number of samples contained in the source known classes.
+This ensures that we correctly balance the unknown class during training in a way which is independent
+on the number of identified target unknown samples during the separation.
+
+{\it Classifier $R_1$, $R_2$}: 
+they are composed by a linear layer $1024\to 256$, followed by a batch normalization layer and a leaky relu activation.
+The last layer is then a linear one for the actual classification $256\to 4$.
+The 256-dimensional output are the features used by the center loss for inferring class centroids.
+$R_2$ is always a single-head classifier, even if using a multi-head rotation classifier.
+
 \subsection{Results}
@@
 \end{table}
-
-\section{Implementation Details}
-\label{sec:implementation_details}
-\subsection{Model Parameters}
-\label{sec:model_parameters}
-
-All models were run using stochastic gradient descent with batch size 32,
-a weight decay of 0.0005 and momentum of 0.9.
-For single-headed models, 
-a base learning rate of 0.001 is used,
-while for multi-headed models it is set to 0.003.
-This is because only one head of the heads is trained with each samples,
-so the process needs to be sped up.
-Rotation classifier use a learning rate set to a tenth of the base learning rate.
-A step learning rate scheduler is used, reducing it by a factor of 10 after 90\% of epochs.
-All models are run for 50 epochs for the first step described in \ref{eq:sample_separation} and for 25 epochs for the second step described in \ref{sec:domain_alignment}.
-For model using the center loss a centroid learning rate of 0.5 is used.
-All other parameters are configuration-sepcific and are reported in table \ref{tab:params}.
-"No Rotation" model is the same as a single-head without center loss model with $\alpha_2 = 0$.
-
-% % %
-
-{\it Extractor E}: The extractor employed is a ResNet-34{\bf[Inserire cit a ResNet]} {\bf è pretrained???} {\bf ma 34 o 18???} for all classifiers.
-
-{\it Classifier $C_1$, $C_2$}: $C_1$ is composed of a 45 dimensional output. 
-All unknown samples are mapped as belonging to class 45.
-$C_1$ is used as a starting point for $C_2$.
-As no unknowns are present on the source dataset (they are removed),
-the weight of unknwon samples in the second step is set to {\bf spiegare come è bilanciato} while for all other classes it is set to 1.
-A single fully connected layer $512\to 45$ with batch-norm is used.
-
-{\it Classifier $R_1$, $R_2$}: 
-$R_1$ and $R_2$ are composed by a $1024\to 256$  and a $256\to 4$ fully connected layers, named {\it Discriminators}.
-The 256-dimensional output are the features used by the center loss for inferring class centers.
-If multi-head is used, each head is a separate discriminator.
-$R_2$ is always a single-head classifier, even if using a multi-head rotation classifier.
 

### 2022-02-12 ROS_AMLProject/eval_target.py
implement vis features

@@ -29,6 +29,8 @@ def target_separation(args, E, C, R, target_loader_eval, device, rand):
     ground_truths = []
     normality_scores = []
 
+    all_features, all_labels = [], []
+
     with torch.no_grad():
         for batch_samples, batch_labels, batch_samples_rot_0, batch_labels_rot_0, batch_samples_rot_90, batch_labels_rot_90,\
             batch_samples_rot_180, batch_labels_rot_180, batch_samples_rot_270, batch_labels_rot_270 in tqdm(target_loader_eval):
@@ -59,7 +61,7 @@ def target_separation(args, E, C, R, target_loader_eval, device, rand):
             predicted_labels = torch.argmax(C_scores, dim=1)
 
             # Use R1 to get the scores
-            R_scores_0 = R(E_output_conc_0, predicted_labels)
+            R_features_0, R_scores_0 = R.forward_extended(E_output_conc_0, predicted_labels)
             R_scores_90 = R(E_output_conc_90, predicted_labels)
             R_scores_180 = R(E_output_conc_180, predicted_labels)
             R_scores_270 = R(E_output_conc_270, predicted_labels)
@@ -79,6 +81,8 @@ def target_separation(args, E, C, R, target_loader_eval, device, rand):
             ground_truths.append(batch_labels.item())
             normality_scores.append(n_score.item())
 
+            all_features.append(R_features_0.data.numpy())
+
     ground_truths = np.array(ground_truths, dtype=np.int)
     normality_scores = np.array(normality_scores)
 
@@ -96,6 +100,11 @@ def target_separation(args, E, C, R, target_loader_eval, device, rand):
     for ns in normality_scores:
         print(f"{ns:.3f}, ", end="")
     print()
+
+    #plot features
+    all_features = np.concatenate(all_features, 0)
+    all_labels = ground_truths
+    plot_features(all_features, all_labels, num_classes=2)
 
     # Compute AUC-ROC value
     auc = roc_auc_score(ground_truths, normality_scores)
@@ -225,6 +234,26 @@ def draw_ROC(args, llr, labels, color=None, recognizer_name=""):
     fig_path = args.plot_path + "_sep_roc.png"
     plt.savefig(fig_path)
     plt.show()
+
+def plot_features(args,features, labels, num_classes):
+    """Plot features on 2D plane.
+    Args:
+        features: (num_instances, num_features).
+        labels: (num_instances). 
+    """
+    colors = ['C0', 'C1']
[…]

### 2022-02-12 paper/main.tex
Figures and tables

@@
 \usepackage{booktabs}
-
+\usepackage{subcaption}
+\usepackage{caption}
 % It is strongly recommended to use hyperref, especially for the review version.
@@
 
-We evaluate the effectiveness of our proposed method exploiting the {\it Office-Home} {\bf INSERT REFERENCE} benchmark dataset,
+We evaluate the effectiveness of our proposed method exploiting the {\it Office-Home} \cite{OfficeHomeDataset} benchmark dataset,
 widely used to assess the performance for OSDA settings.
@@
 As we have already seen in section \ref{sec:method}, the network is composed of a feature extractor $E$, and two heads, $C_{1/2}$ and $R_{1/2}$.
-For the feature extraction, we employ a ResNet-18 ({\bf INSERT REF}) pre-trained on ImageNet.
+For the feature extraction, we employ a ResNet-18\cite{ResNet18} pre-trained on ImageNet.
 All the experiments are run training with a batch size equals to 32 and using a stochastic gradient descent optimization strategy
@@
 \label{sec:results}
-Table \ref{tab:results} contains the results for all 12 {\bf (ne abbiamo provati davvero 12???)} available domain shifts,
+\begin{figure*}[h!]
+  \centering
+  \begin{subfigure}[b]{0.35\textwidth}
+    \includegraphics[trim=0 0 0 2cm, clip, width=\linewidth]{hos-a1.png}
+  \end{subfigure}
+  \begin{subfigure}[b]{0.35\textwidth}
+    \includegraphics[trim=0 0 0 2cm, clip, width=\linewidth]{hos-a2.png}
+  \end{subfigure}
+  \begin{subfigure}[b]{0.35\textwidth}
+    \includegraphics[trim=0 0 0 2cm, clip, width=\linewidth]{hos-l.png}
+  \end{subfigure}
+  \begin{subfigure}[b]{0.35\textwidth}
+    \includegraphics[trim=0 0 0 2cm, clip, width=\linewidth]{hos-th.png}
+  \end{subfigure}
+  \caption{\label{figurelabel} Test Caption}
+\end{figure*}
+
+Table \ref{tab:results} contains the results for all 12 available domain shifts,
 as well as perfomance differences when using multi-head rotation classifiers and center loss.
@@
 while HOS values are sampled at regular times on the entire original target dataset.
+
+\subsection{Ablation Study}
+\label{sec:ablation_study}
+As shown in table \ref{tab:results} different architectures give different results, 
+and as shown in table \ref{tab:params} each one requires a different set of parameters.
+To choose optimal parameters a sequential approach is followed, 
+by optimizing one parameter at the time.
+The order of optimization followed is: 
+$\alpha_1$, $\lambda_1$, $\mathcal{\tilde N}$, $\alpha_2$.
+Models not using center loss just skip the $\lambda_1$ optimization.
+Ablation study were run on two domain shifts, 
+Art $\to$ Clipart and Clipart $\to$ Product.
+In table \ref{tab:ablation_params} we report the steps followed.
+All other settings follow what is reported in \ref{sec:model_parameters}.
+The result here obtained are the same reported in table \ref{tab:params}.
+
+\section{Future Work}
+
+The results show that self-supervision technique can help in domain adaptation task and open-set classification tasks.
+A few critical points still remain on our method of study and proposed solution.
+The most important one is probably parameter choosing for different models, as we have seen that variations cause huge differences in results and sequential optimization of parameter is a sub-optimal heuristic.
+Furthermore, having the model to learn two different tasks at once, it could be useful to use a slower learning model at the expense of longer training times.
+\newpage
+\appendix
+\section{Test}
+
+\begin{table}
+  \centering
+  \begin{tabular}[h]{||c|c|c||c||}
+    \hline
+    \multicolumn{4}{||c||}{OFF-OFF} \\
+    \hline
+    $\alpha_1$ & $\mathcal{\tilde N}$ & $\alpha_2$ & HOS$_{mean}$\\    
+    \hline
+    \hline
+    \multicolumn{4}{||c||}{Picking $\alpha_1$} \\
+    \hline
+    {\bf 1.0}  & \multirow{4}{*}{0.6} & \multirow{4}{*}{3.0} & {\bf 40.27\%} \\
+    3.0  & & & 22.69\% \\
+    5.0  & & & 18.78\% \\
+    10.0 & & & 9.99\% \\
+    \hline
+    \hline
+    \multicolumn{4}{||c||}{Picking $\mathcal{\tilde N}$} \\
+    \hline
+    \multirow{4}{*}{1.0} & 0.50 & \multirow{4}{*}{3.0}  & 28.05\%\\
+    & 0.55 & & 34.73\% \\
+    & 0.60 & & 40.27\% \\
+    & 0.65 & & 43.16\% \\
+    \hline
+    \hline
+    \multicolumn{4}{||c||}{Picking $\alpha_2$} \\
+    \hline
+    \multirow{7}{*}{1.0} & \multirow{7}{*}{0.7} & 0.1 & 42.79\%\\
+    && 1.0 & 44.35\% \\
+    && 2.0 & 43.53\% \\
+    && {\bf 3.0} & {\bf 44.38}\% \\
+    && 4.0 & 43.12\% \\
+    && 5.0 & 41.97\% \\
+    && 10.0 & 42.01\% \\
+    \hline
+  \end{tabular}
+  \caption{\centering\label{tab:ablationoffoff} Hyperparameters picking process for configuration Multi-Head Off and Center-Loss Off}
+\end{table}
+
+\begin{table}
+  \centering
+  \begin{tabular}[h]{||c|c|c||c||}
+    \hline
+    \multicolumn{4}{||c||}{ON-OFF} \\
+    \hline
+    $\alpha_1$ & $\mathcal{\tilde N}$ & $\alpha_2$ & HOS$_{mean}$\\    
+    \hline
+    \hline
+    \multicolumn{4}{||c||}{Picking $\alpha_1$} \\
+    \hline
+    {\bf 1.0}  & \multirow{4}{*}{0.6} & \multirow{4}{*}{3.0} & {\bf 43.48\%} \\
+    3.0  & & & 38.45\% \\
+    5.0  & & & 37.61\% \\
+    10.0 & & & 33.23\% \\
+    \hline
+    \hline
+    \multicolumn{4}{||c||}{Picking $\mathcal{\tilde N}$} \\
+    \hline
+    \multirow{6}{*}{1.0} & 0.4 & \multirow{6}{*}{3.0}  & 38.40\%\\
+    & 0.45 & & 42.40\% \\
+    & 0.5 & & 43.48\% \\
+    & 0.55 & & 46.21\% \\
+    & {\bf0.6} & & {\bf 50.17\%} \\
+    & 0.65 & & 45.82\% \\
+    \hline
+    \hline
+    \multicolumn{4}{||c||}{Picking $\alpha_2$} \\
+    \hline
+    \multirow{7}{*}{1.0} & \multirow{7}{*}{0.7} & 0.1 & 46.02\%\\
+    && 1.0 & 47.71\% \\
+    && 2.0 & 46.56\% \\
+    && {\bf 3.0} & {\bf 50.17\%} \\
+    && 4.0 & 46.57\% \\
+    && 5.0 & 47.52\% \\
+    && 10.0 & 44.56\% \\
+    \hline
+  \end{tabular}
+  \caption{\centering\label{tab:ablationonoff} Hyperparameters picking process for configuration Multi-Head On and Center-Loss Off}
+\end{table}
+
+\begin{table}
+  \centering
+  \begin{tabular}[h]{||c|c|c|c||c||}
+    \hline
+    \multicolumn{5}{||c||}{ON-ON} \\
+    \hline
+    $\alpha_1$ & $\lambda_1$ & $\mathcal{\tilde N}$ & $\alpha_2$ & HOS$_{mean}$ \\
+    \hline
+    \hline
+    \multicolumn{5}{||c||}{Picking $\alpha_1$} \\
+    \hline
+    1.0 & \multirow{4}{*}{0.01} & \multirow{4}{*}{0.05} & \multirow{4}{*}{3.0} & 44.90\% \\
+    {\bf 3.0} & && & {\bf 45.33\%} \\
+    5.0 & && & 42.41\% \\
+    10.0 & && & 37.15\% \\
+    \hline
+    \hline
+    \multicolumn{5}{||c||}{Picking $\lambda_1$} \\
+    \hline
+    \multirow{5}{*}{3} & 0.0001 & \multirow{5}{*}{0.5} & \multirow{5}{*}{3.0} & 39.90\% \\
+    & 0.001 & & & 36.71\% \\
+    & 0.01 & & & 45.33\% \\
+    & {\bf 0.05 }& & & {\bf 46.63\%} \\
+    & 0.1 & & & 37.44\% \\
+    \hline
+    \hline
+    \multicolumn{5}{||c||}{Picking $\mathcal{\tilde N}$} \\
+    \hline
+    \multirow{5}{*}{3} & \multirow{5}{*}{0.05} & 0.4 & \multirow{5}{*}{3.0} & 44.32\% \\
+    & & 0.45 & & 45.13\% \\
+    & & 0.5 & & 46.63\% \\
+    & & 0.55 & & 47.09\% \\
+    & & {\bf 0.6} & & {\bf 49.78\%} \\
+    \hline
+    \hline
+    \multicolumn{5}{||c||}{Picking $\alpha_2$} \\
+    \hline
+    \multirow{7}{*}{3} & \multirow{7}{*}{0.05} & \multirow{7}{*}{0.6} & 0.1 & 45.73\% \\
+    & & & 1.0 & 45.23\% \\
+    & & & 2.0 & 45.76\% \\
+    & & & {\bf 3.0} & {\bf 49.78\%} \\
+    & & & 4.0 & 46.20\% \\
+    & & & 5.0 & 48.60\% \\
+    & & & 10.0 & 44.14\% \\
+    \hline
+  \end{tabular}
+  \caption{\centering\label{tab:ablationonon} Hyperparameters picking process for configuration Multi-Head On and Center-Loss On}
+\end{table}
 
@@
 
-\begin{table}
-  \centering
-  \begin{tabular}[b]{||c|c|c|c|c|c||}
-    \hline
-    MH & CL & $\alpha_1$ & $\alpha_2$ & $\lambda_1$ & $\mathcal{\tilde N}$ \\
-    \hline
-    Off & Off & 0.0 & 0.0 & 0.0 & 0.0 \\
-    On & Off & 0.0 & 0.0 & 0.0 & 0.0 \\
-    Off & On & 0.0 & 0.0 & 0.0 & 0.0 \\
-    On & On & 0.0 & 0.0 & 0.0 & 0.0 \\
-    \hline
-  \end{tabular}
-  \caption{\label{tab:params}Model Parameters}
-\end{table}
-
-\subsection{Ablation Study}
-\label{sec:ablation_study}
-As shown in table \ref{tab:results} different architectures give different results, 
-and as shown in table \ref{tab:params} each one requires a different set of parameters.
-To choose optimal parameters a sequential approach is followed, 
-by optimizing one parameter at the time.
-The order of optimization followed is: 
-$\alpha_1$, $\lambda_1$, $\mathcal{\tilde N}$, $\alpha_2$.
-Models not using center loss just skip the $\lambda_1$ optimization.
-Ablation study were run on two domain shifts, 
-Art $\to$ Clipart and Clipart $\to$ Product.
-In table \ref{tab:ablation_params} we report the steps followed.
-All other settings follow what is reported in \ref{sec:model_parameters}.
-The result here obtained are the same reported in table \ref{tab:params}.
-
-\begin{table}
-  \centering
-  \begin{tabular}[h]{||c|c|c||c|c||}
-    \hline
-    \multicolumn{5}{||c||}{MH OFF CL OFF} \\
-    \hline
-    $\alpha_1$ & $\mathcal{\tilde N}$ & $\alpha_2$  & AUROC & HOS$_{mean}$\\    
-    \hline
-    \hline
-    \multicolumn{5}{||c||}{Picking $\alpha_1$} \\
-    \hline
-    1.0 & \multirow{4}{*}{0.5} & \multirow{4}{*}{3.0} & 0.5 & 30\% \\
-    3.0 & & & 0.5 & 30\% \\
-    5.0 & & & 0.5 & 30\% \\
-    10.0 & & & 0.5 & 30\% \\
-    \hline
-    \hline
-    \multicolumn{5}{||c||}{Picking $\mathcal{\tilde N}$} \\
-    \hline
-    \multirow{4}{*}{1.0} & 0.40 & \multirow{4}{*}{3.0} & 0.5 & 50\%\\
-    & 0.50 && 0.5 & 50\% \\
-    & 0.55 && 0.5 & 50\% \\
-    & 0.60 && 0.5 & 50\% \\
-    \hline
-    \hline
-    \multicolumn{5}{||c||}{Picking $\alpha_2$} \\
-    \hline
-    \multirow{4}{*}{1.0} & \multirow{4}{*}{0.6} & 1.0 & 0.5 & 50\%\\
-    && 3.0 & 0.5 & 50\% \\
-    && 5.0 & 0.5 & 50\% \\
-    && 10.0 & 0.5 & 50\% \\
-    \hline
-    \hline
-    \multicolumn{5}{||c||}{Final Parameters} \\
-    \hline
-    1.0 & 0.6 & 3.0 & 0.5 & 50\%\\
-    \hline
-  \end{tabular}
-  \caption{\label{tab:ablationoffoff} Ablation performed for OFF-OFF configuration}
-\end{table}
-\section{Future Work}
-
-The results show that self-supervision technique can help in domain adaptation task and open-set classification tasks.
-A few critical points still remain on our method of study and proposed solution.
-The most important one is probably parameter choosing for different models, as we have seen that variations cause huge differences in results and sequential optimization of parameter is a sub-optimal heuristic.
-Furthermore, having the model to learn two different tasks at once, it could be useful to use a slower learning model at the expense of longer training times.
-
 %%%%%%%%% REFERENCES

### 2022-02-12 ROS_AMLProject/eval_target.py
bug fix

@@ -6,6 +6,7 @@ from sklearn.metrics import roc_auc_score
 from tqdm import tqdm
 import numpy as np
 from torch import nn
+#from tsnecuda import TSNE
 
 import matplotlib.pyplot as plt
 
@@ -81,7 +82,7 @@ def target_separation(args, E, C, R, target_loader_eval, device, rand):
             ground_truths.append(batch_labels.item())
             normality_scores.append(n_score.item())
 
-            all_features.append(R_features_0.data.numpy())
+            all_features.append(R_features_0.data.cpu().numpy())
 
     ground_truths = np.array(ground_truths, dtype=np.int)
     normality_scores = np.array(normality_scores)
@@ -103,6 +104,9 @@ def target_separation(args, E, C, R, target_loader_eval, device, rand):
 
     #plot features
     all_features = np.concatenate(all_features, 0)
+    print(f"Feature shape:{all_features.shape}")
+    #all_features_embedded = TSNE().fit_transform(all_features)
+    #print(f"Feature shape:{all_features_embedded.shape}")
     all_labels = ground_truths
     plot_features(all_features, all_labels, num_classes=2)
 

### 2022-02-12 ROS_AMLProject/eval_target.py
bug fix v2

@@ -82,7 +82,7 @@ def target_separation(args, E, C, R, target_loader_eval, device, rand):
             ground_truths.append(batch_labels.item())
             normality_scores.append(n_score.item())
 
-            all_features.append(R_features_0.data.cpu().numpy())
+            all_features.append(R_features_0.cpu().data.numpy())
 
     ground_truths = np.array(ground_truths, dtype=np.int)
     normality_scores = np.array(normality_scores)

### 2022-02-12 ROS_AMLProject/eval_target.py
bug fix v3

@@ -82,7 +82,7 @@ def target_separation(args, E, C, R, target_loader_eval, device, rand):
             ground_truths.append(batch_labels.item())
             normality_scores.append(n_score.item())
 
-            all_features.append(R_features_0.cpu().data.numpy())
+            all_features.append(R_features_0.data.cpu().numpy())
 
     ground_truths = np.array(ground_truths, dtype=np.int)
     normality_scores = np.array(normality_scores)

### 2022-02-12 ROS_AMLProject/eval_target.py
bug fix v4

@@ -108,7 +108,7 @@ def target_separation(args, E, C, R, target_loader_eval, device, rand):
     #all_features_embedded = TSNE().fit_transform(all_features)
     #print(f"Feature shape:{all_features_embedded.shape}")
     all_labels = ground_truths
-    plot_features(all_features, all_labels, num_classes=2)
+    plot_features(args,all_features, all_labels, num_classes=2)
 
     # Compute AUC-ROC value
     auc = roc_auc_score(ground_truths, normality_scores)

### 2022-02-12 ROS_AMLProject/eval_target.py
version tsne

@@ -6,7 +6,7 @@ from sklearn.metrics import roc_auc_score
 from tqdm import tqdm
 import numpy as np
 from torch import nn
-#from tsnecuda import TSNE
+from tsnecuda import TSNE
 
 import matplotlib.pyplot as plt
 
@@ -105,10 +105,10 @@ def target_separation(args, E, C, R, target_loader_eval, device, rand):
     #plot features
     all_features = np.concatenate(all_features, 0)
     print(f"Feature shape:{all_features.shape}")
-    #all_features_embedded = TSNE().fit_transform(all_features)
-    #print(f"Feature shape:{all_features_embedded.shape}")
+    all_features_embedded = TSNE().fit_transform(all_features)
+    print(f"Feature shape:{all_features_embedded.shape}")
     all_labels = ground_truths
-    plot_features(args,all_features, all_labels, num_classes=2)
+    plot_features(args,all_features_embedded, all_labels, num_classes=2)
 
     # Compute AUC-ROC value
     auc = roc_auc_score(ground_truths, normality_scores)

### 2022-02-12 paper/main.tex
Results table

@@
 \usepackage{multirow}
+\usepackage{float}
 
@@
 For models using the center loss a centroid learning rate of 0.001 is used.
-The other hyperparameters are analyzed performing an ablation on section {\bf INSERT REF}.
+The other hyperparameters are analyzed performing an ablation on appendix \ref{sec:tables}.
 
@@
 \label{sec:results}
-\begin{figure*}[h!]
+\begin{figure}[!htb]
   \centering
-  \begin{subfigure}[b]{0.35\textwidth}
+  \begin{subfigure}[!htb]{0.35\textwidth}
     \includegraphics[trim=0 0 0 2cm, clip, width=\linewidth]{hos-a1.png}
   \end{subfigure}
-  \begin{subfigure}[b]{0.35\textwidth}
+  \begin{subfigure}[!htb]{0.35\textwidth}
     \includegraphics[trim=0 0 0 2cm, clip, width=\linewidth]{hos-a2.png}
   \end{subfigure}
-  \begin{subfigure}[b]{0.35\textwidth}
+  \begin{subfigure}[!htb]{0.35\textwidth}
     \includegraphics[trim=0 0 0 2cm, clip, width=\linewidth]{hos-l.png}
   \end{subfigure}
-  \begin{subfigure}[b]{0.35\textwidth}
+  \begin{subfigure}[!htb]{0.35\textwidth}
     \includegraphics[trim=0 0 0 2cm, clip, width=\linewidth]{hos-th.png}
   \end{subfigure}
-  \caption{\label{figurelabel} Test Caption}
-\end{figure*}
+  \caption{\centering\label{figurelabel} HOS values for different parameters. For full reference see appendix \ref{sec:tables}}
+\end{figure}
 
@@
 Furthermore, having the model to learn two different tasks at once, it could be useful to use a slower learning model at the expense of longer training times.
+
+%%%%%%%%% REFERENCES
+{\small
+\bibliographystyle{ieee_fullname}
+\bibliography{egbib}
+}
+
 \newpage
 \appendix
-\section{Test}
+\section{Tables}
+\label{sec:tables}
+
+This section contains tables \ref{tab:ablationoffoff}, \ref{tab:ablationonoff} and \ref{tab:ablationonon} report the hyperparameters optimization sequence, while tables \ref{tab:results} report the final values for each domain shift with the chosen hyperparameters.
 
@@
 
-\begin{table}
+\begin{table*}
   \centering
-  \begin{tabular}[t]{||c|c|c||c|c||}
+  \begin{tabular}[t]{||c||c|c|c|c||c|c|c|c||c|c|c|c||}
     \hline
-    \multicolumn{5}{||c||}{Single-Head, CE Loss} \\
+    \multicolumn{13}{||c||}{Results} \\
     \hline
-    Source & Target & AUROC & HOS & HOS* \\
-    S & T & 50\% & 30\% & 30\% \\
-    S & T & 50\% & 30\% & 30\% \\
-    S & T & 50\% & 30\% & 30\% \\
+    \multirow{2}{*}{Shift}   & \multicolumn{4}{|c||}{Single-Head, No Center Loss} & \multicolumn{4}{|c||}{Multi-Head, No Center Loss} & \multicolumn{4}{|c||}{Multi-Head, Center Loss} \\
+            & AUROC & HOS   & UNK   & OS*   & AUROC & HOS   & UNK   & OS*   & AUROC & HOS   & UNK   & OS*   \\
     \hline
+    A$\to$C & 52.07 & 44.76 & 58.65 & 36.19 & 57.46 & 46.64 & 62.95 & 37.04 & 59.77 & 52.68 & 62.73 & 45.40 \\
+    A$\to$P & 50.84 & 51.27 & 57.56 & 46.23 & 56.31 & 54.13 & 60.42 & 49.03 & 56.86 & 52.46 & 63.35 & 44.77 \\
+    A$\to$R & ??.?? & ??.?? & ??.?? & ??.?? & 59.88 & 56.60 & 53.18 & 60.65 & 58.86 & 61.67 & 66.82 & 57.26 \\
+    C$\to$A & 49.52 & 41.74 & 43.10 & 40.47 & 55.28 & 42.63 & 51.57 & 36.33 & 55.76 & 46.84 & 60.19 & 38.35 \\
+    C$\to$P & 54.42 & 46.99 & 41.51 & 54.15 & 59.13 & 51.88 & 60.03 & 45.69 & 58.35 & 52.69 & 62.19 & 45.72 \\
+    C$\to$R & 53.43 & 46.18 & 38.64 & 57.39 & 60.75 & 56.00 & 61.29 & 51.63 & 59.15 & 55.97 & 63.18 & 50.25 \\
+    P$\to$A & 48.32 & 37.07 & 33.70 & 41.20 & 55.62 & 41.72 & 48.90 & 36.39 & 53.50 & 40.97 & 49.53 & 34.94 \\
+    P$\to$C & 47.76 & 43.99 & 48.42 & 40.31 & 56.77 & 46.10 & 55.11 & 39.65 & ??.?? & ??.?? & ??.?? & ??.?? \\
+    P$\to$R & 50.37 & 34.14 & 22.88 & 67.27 & 59.68 & 48.41 & 40.91 & 59.30 & 61.10 & 56.22 & 56.89 & 55.58 \\
+    R$\to$A & 49.39 & 25.08 & 15.99 & 58.19 & 58.47 & 45.00 & 39.50 & 52.43 & 57.98 & 48.92 & 45.61 & 52.77 \\
+    R$\to$C & 49.80 & 46.70 & 48.27 & 45.23 & 57.02 & 49.00 & 42.82 & 57.34 & 57.09 & 48.69 & 61.11 & 40.47 \\
+    R$\to$P & 54.10 & 23.37 & 13.89 & 73.69 & 62.33 & 50.31 & 39.51 & 69.27 & 63.96 & 59.64 & 54.40 & 66.02 \\
     \hline
-    \multicolumn{5}{||c||}{Multi-Head, CE Loss} \\
-    \hline
-    Source & Target & AUROC & HOS & HOS* \\
-    S & T & 50\% & 30\% & 30\% \\
-    S & T & 50\% & 30\% & 30\% \\
-    S & T & 50\% & 30\% & 30\% \\
-    \hline
-    \hline
-    \multicolumn{5}{||c||}{Single-Head, CE+C Loss} \\
-    \hline
-    Source & Target & AUROC & HOS & HOS* \\
-    S & T & 50\% & 30\% & 30\% \\
-    S & T & 50\% & 30\% & 30\% \\
-    S & T & 50\% & 30\% & 30\% \\
-    \hline
-    \hline
-    \multicolumn{5}{||c||}{Multi-Head, CE+C Loss} \\
-    \hline
-    Source & Target & AUROC & HOS & HOS* \\
-    S & T & 50\% & 30\% & 30\% \\
-    S & T & 50\% & 30\% & 30\% \\
-    S & T & 50\% & 30\% & 30\% \\
-    \hline 
-    \hline
-    \multicolumn{5}{||c||}{No Rotation} \\
-    \hline
-    Source & Target & AUROC & HOS & HOS$_{Best}$ \\
-    S & T & 50\% & 30\% & 30\% \\
-    S & T & 50\% & 30\% & 30\% \\
-    S & T & 50\% & 30\% & 30\% \\
+    AVG     & ??.?? & ??.?? & ??.?? & ??.?? & 52.23 & 49.03 & 51.35 & 49.56 & ??.?? & ??.?? & ??.?? & ??.?? \\ 
     \hline
   \end{tabular}
-  \caption{\centering\label{tab:results}Results for domain alignment. AUROC is the area under the ROC. HOS is latest achieved HOS, HOS* the best achieved through all epochs.}
-\end{table}
-
-%%%%%%%%% REFERENCES
-{\small
-\bibliographystyle{ieee_fullname}
-\bibliography{egbib}
-}
+  \caption{\centering\label{tab:results}Results for each configuration and each domain shift. All values are percentages.}
+\end{table*}
 

### 2022-02-12 paper/main.tex
addded related works

@@
 \label{sec:relatedwork}
+\textbf{Closed-Set Domain Adaptation}
+Unsupervised domain adaptation is the setting where labeled training data is 
+available on a source domain, but the goal is to have good performance on a 
+target domain with only unlabeled data and with a different marginal distribution
+of data from the source dataset. The aim is to align the learned representations 
+of the source and target domains.
 
+Methods for unsupervised domain adaptation in computer vision can be divided into 
+three broad classes. The first class aims to induce alignment between the
+source and the target domains in some feature space optimizing for some
+measurement of distributional discrepancy. \cite{bousmalis2016domain,long2015learning,long2017deep,ganin2015unsupervised,hoffman2017cycada}
+
+The second class of methods directly transforms the source images to resemble 
+the target images with generative models \cite{taigman2016unsupervised,tzeng2017adversarial,bousmalis2017unsupervised}. 
+While similar to the first class in the philosophy of alignment, 
+these methods operate on image pixels directly instead of an intermediate 
+representation space, and therefore can benefit from an additional
+round of adaptation in some representation space. Since they rely on generative 
+models, large-scale datasets must train the generative model robustly.
+Such methods often require complex methods of optimization.
+
+The third class of methods uses a model trained on the labeled source data to 
+estimate labels on the target data, then trains on some of those estimated 
+pseudo-labels (e.g. the most confident ones), therefore bootstrapping through the 
+unlabeled target data. Sometimes called self-ensembling \cite{french2018selfensembling}, this technique is borrowed from semi-supervised learning, 
+where it is called co-training \cite{saito2017asymmetric,zou2018domain,chen2017rethinking}
+
+In contrast, the presented method uses a Self-Supervised approach, already presented in 
+the recent years by many other works \cite{sun2019unsupervised,yue2021prototypical,saito2020universal,BAFFOUR2022126,kim2020crossdomain,ieeeopensetselfsup} . Self-supervised methods use pretext tasks 
+(e.g., image rotation, jigsaw puzzle \cite{CarlucciJigsaw}, mutual information (MI) \cite{selfsupfeng}, 
+and instance discrimination \cite{chen2020simple}) to learn high-level feature representation in 
+source and target domains by jointly training a shared feature extractor.
+
+\textbf{Open Set Recognition}
+The objective of Open Set Recognition (OSR) is to learn a classifier that can 
+reject the unknown samples while classifying the known classes accurately.
+
+The problem was first formulated in \cite{firstPaperOSR}, where authors 
+pointed out the possibility of an open-set sample generating a very high 
+activation score for one of the known class categories. 
+Since then, several other works have analyzed this challenge in the context 
+of deep networks \cite{perera2019deep},\cite{hein2019relu}
+
+In \cite{bendale2015open}, OpenMax was proposed as an alternative to the SoftMax operator using 
+a statistical method apportion class probabilities to the open-set class. 
+A k + 1 classifier for a k class problem was used where the extra class was treated
+as the open-set class.
+
+In \cite{ge2017generative}, a Generative Adversarial Network (GAN) based framework was used to estimate
+open-set class activations.
+
+\cite{kong2021opengan} achieve strong OSR performance by using an adversarially 
+trained discriminator to delineate closed from open-set images,
+leveraging real open-set images for model selection
+
+Other approaches include reconstruction based methods 
+\cite{yoshihashi2019classificationreconstruction}
+which use poor test-time reconstruction as an open-set indicator, 
+and prototype-based methods \cite{shu2020podn} 
+which represent known classes with learned prototypes, and identify open-set images
+based on distances to the prototypes.
+
+In the recent years different works to a Self-Supervised solution, used also in the 
+presented method, engaging in learning representations that are invariant to the 
+transformations of the input data and improving separation of classes from each other 
+and from open-set samples \cite{dhamija2021selfsupervised,jia2021selfsupervised,Perera_2020_CVPR,GeoTran}
+
+\textbf{Self-supervised Learning}
+The emerging field of self-supervised learning uses the machinery of supervised 
+learning on problems where external supervision is not available. 
+The idea is to use data itself as supervision for auxiliary (also called “pretext”) 
+tasks that learn deep feature representations which will hopefully be informative 
+for downstream “real” tasks.
+Many such auxiliary tasks have been proposed in the literature, including
+image colorization \cite{zhang2016colorful,larsson2017learning}, patch location 
+prediction \cite{doersch2016unsuperviseddoersch2017multitask},
+image jigsaw puzzle [\cite{noroozi2017unsupervised}, image inpainting \cite{pathak2016context},
+contrastive learning \cite{oord2019representation}, geometric transformations \cite{dosovitskiy2015discriminative}. Another geometric 
+transformation task is rotation recognition \cite{OldROS}, where input images
+are rotated by multiples of 90° and the network is trained to predict the rotation
+angle pf each image. This pretext task has been successfully used for both anomaly
+detection \cite{golan2018deep} and closed-set domain adaptation \cite{selfsupxu}
+
+\textbf{Open Set Domain Adaptation}
+Open Set Domain Adaptation (OSDA) is a challenging domain adaptation setting 
+which allows the existence of unknown classes on the target domain.
+The term "OSDA" was first introduced by Busto and Gall \cite{firstosda} that
+considered the setting where each domain contains, in addition to the shared
+categories, a set of private categories. The currently accepted defiition of OSDA
+was introduced by Saito et al. \cite{saito2018open} that considered the target as 
+containing all the source categories and additional set of private categories 
+that should be considered unknown, presenting Open Set
+Back-Propagation (OSBP) \cite{saito2018open} as an adversarial method 
+to increase the prediction variances so that the generator can choose to align 
+a target sample with the source known or reject it as an unknown target samples.
+Separate To Adapt (STA) \cite{sat} train a multi-binary classifier to progressively 
+separate the samples of unknown and known classes.
+Universal Adaptation Network (UAN) \cite{uan}, originally proposed for the universal 
+domain adaptation setting that is a superset of OSDA, quantify the sample-level 
+transferability and recognize the unknown samples based on the transferability.
+Attract or Distract (AoD) \cite{feng2019attract} starts with a mild alignment with 
+a procedure similar to \cite{saito2018open} refining the decision by using 
+metric learning to reduce the intra-class distance in known classes and push 
+the unknown class away from the known classes.
+Jing \etal \cite{Jing_Li_Zhu_Ding_Lu_Yang_2021} have recently proposed a method
+to recognize the unknown samples according to the centroid deviation angles and
+employing the statistical Extreme Value Theory to recognize the unknown 
+samples that are misclassified into known classes.
+The approach that we are going to present is instead based on a self-supervision 
+task, the rotation recognition, used to both separate known and unknown target 
+samples and align the known source and target distributions.
 \section{Method}
@@
 Table \ref{tab:results} contains the results for all 12 available domain shifts,
-as well as perfomance differences when using multi-head rotation classifiers and center loss.
-Further details are to be found in section \ref{sec:implementation_details}.
-We can notice that multi-headed models are more capable of correctly discriminating between known and unknown samples,
+as well as perfomance differences when using multi-head rotation classifiers and center loss,
+as described in the previous section.
+Multi-headed models are more capable of correctly discriminating between known and unknown samples,
 ultimately resulting in better domain alignment.
-A further advantage is given when combined with center loss.
+This effect is amplified when also using center loss.
 AUROC values are computed at the end of the separation stage, 

### 2022-02-12 paper/main.tex
added cit file

@@
 
-In \cite{bendale2015open}, OpenMax was proposed as an alternative to the SoftMax operator using 
-a statistical method apportion class probabilities to the open-set class. 
-A k + 1 classifier for a k class problem was used where the extra class was treated
-as the open-set class.
-
 In \cite{ge2017generative}, a Generative Adversarial Network (GAN) based framework was used to estimate
@@
 image colorization \cite{zhang2016colorful,larsson2017learning}, patch location 
-prediction \cite{doersch2016unsuperviseddoersch2017multitask},
+prediction \cite{doersch2016unsupervised, doersch2017multitask},
 image jigsaw puzzle [\cite{noroozi2017unsupervised}, image inpainting \cite{pathak2016context},
@@
 w.r.t nose.
-The method and its effectiveness is further illustrated in \cite{OldROS}. 
-We will further discuss possible improvements and variants in {\bf PLEASE COMPLETE}.
+The method and its effectiveness is further illustrated in \cite{OldROS},
+and further improvements will be discussed in \ref{sec:future_work}.
 
@@
 \section{Future Work}
+\label{sec:future_work}
 

### 2022-02-12 paper/main.tex
shorter bib

--- 2022-02-12 paper/main.tex
@@
 \label{sec:relatedwork}
+\textbf{Closed-Set Domain Adaptation} is the setting where labeled training data is 
+available on a source domain, but the goal is to have good performance on a 
+unlabeled target domain with a different marginal distribution
+of data. The aim is to align the learned representations of the source and target domains.
+
+Methods for unsupervised domain adaptation in computer vision can be divided into 
+three broad classes.
+The first class aims to induce alignment in some feature space optimizing the distributional discrepancy \cite{bousmalis2016domain,long2015learning,ganin2015unsupervised,hoffman2017cycada}.
+The second class of methods directly transforms the source images to resemble 
+the target images with generative models \cite{taigman2016unsupervised,tzeng2017adversarial,bousmalis2017unsupervised}, 
+operating on image pixels directly instead of an intermediate 
+representation space.
+The third class uses a model trained on the labeled source data to 
+estimate labels on the target data, then trains on some of those estimated 
+pseudo-labels (e.g. the most confident ones), therefore bootstrapping through the 
+unlabeled target data. This technique is borrowed from semi-supervised learning, 
+where it is called co-training \cite{saito2017asymmetric,zou2018domain,chen2017rethinking}.
+
+In contrast, the presented method uses a Self-Supervised approach, already presented in 
+the recent years by many other works \cite{sun2019unsupervised,saito2020universa,yue2021prototypical}.
+using pretext tasks (e.g., image rotation, jigsaw puzzle \cite{CarlucciJigsaw}, mutual information (MI) \cite{selfsupfeng}, instance discrimination \cite{chen2020simple}) to learn high-level feature representation in
+source and target domains by jointly training a shared feature extractor.
+
+\textbf{Open Set Recognition} (OSR) has the objective of learning a classifier 
+that can reject the unknown samples while classifying the known classes accurately.
+
+The problem was first formulated in \cite{firstPaperOSR} and since then, several other works have analyzed this challenge in the context 
+of deep networks \cite{perera2019deep, hein2019relu, bendale2015open}.
+Some techinques presented in the past were focus on an adversarial approach to 
+delineate closed from open-set images \cite{ge2017generative, kong2021opengan}.
+Other approaches include reconstruction based methods 
+\cite{yoshihashi2019classificationreconstruction}
+which use poor test-time reconstruction as an open-set indicator.
+
+In the recent years different works to a Self-Supervised solution, used also in the 
+presented method, engaging in learning invariant representations to the 
+transformations of the input data, improving separation of classes from each other 
+and from open-set samples \cite{dhamija2021selfsupervised,jia2021selfsupervised,GeoTran}.
+
+\textbf{Self-supervised Learning} is an emerging field focused on using 
+data itself as supervision for auxiliary (also called “pretext”) 
+tasks that learn deep feature representations, which will hopefully be informative 
+for downstream “real” tasks.
+Many such auxiliary tasks have been proposed in the literature, including
+image colorization \cite{zhang2016colorful},
+image jigsaw puzzle [\cite{noroozi2017unsupervised}, image inpainting \cite{pathak2016context},
+contrastive learning \cite{oord2019representation}, geometric transformations \cite{dosovitskiy2015discriminative}.
+
+Another geometric transformation task is rotation recognition \cite{OldROS}, where input images
+are rotated by multiples of 90° and the network is trained to predict the rotation
+angle pf each image. This pretext task has been successfully used for both anomaly
+detection \cite{golan2018deep} and closed-set domain adaptation \cite{selfsupxu}.
+
+\textbf{Open Set Domain Adaptation} (OSDA) is a challenging domain adaptation 
+setting which allows the existence of unknown classes on the target domain.
+The term "OSDA" was first introduced by Busto and Gall \cite{firstosda}, but the 
+currently accepted definition was introduced by Saito \etal \cite{saito2018open} considering the target as 
+containing all the source categories and additional set of private categories 
+that should be considered unknown. They have presented Open Set
+Back-Propagation (OSBP) \cite{saito2018open} as an adversarial method 
+to increase the prediction variances so that the generator can choose if accept Ornot a target saple.
+Separate To Adapt (STA) \cite{sat} train a multi-binary classifier to progressively 
+separate the samples of unknown and known classes.
+Universal Adaptation Network (UAN) \cite{uan}, originally proposed for the universal 
+domain adaptation setting that is a superset of OSDA, quantify the sample-level 
+transferability and recognize the unknown samples based on it.
+Attract or Distract (AoD) \cite{feng2019attract} refine the decision by using 
+metric learning to reduce the intra-class distance in known classes and push 
+the unknown class away from the known classes.
+Jing \etal \cite{Jing_Li_Zhu_Ding_Lu_Yang_2021} have recently proposed a method
+to recognize the unknown samples according to the centroid deviation angles and
+employing the statistical Extreme Value Theory to recognize the unknown 
+samples that are misclassified into known classes.
+
+The approach that we are going to present is instead based on a Self-Supervision 
+task, the rotation recognition, used to both separate known and unknown target 
+samples and align the known source and target distributions.
 

### 2022-02-13 paper/main.tex
add image step 1
Updated results table

@@
 \begin{figure*}
+  \includegraphics[width=\textwidth ]{scheme_step1.png}
+  \caption{\label{fig:separation} Schema representing the step 1 training}
+\end{figure*}
+
+\begin{figure*}
   \includegraphics[width=\textwidth ]{scheme.png}
@@
 Furthermore, having the model to learn two different tasks at once, it could be useful to use a slower learning model at the expense of longer training times.
+Another observation that we can make based 
+on gathered data is the impact that the threshold 
+choice have during the target separation step.
+This is ascrivable to a weak normality score 
+that may need particular attention in order to develop
+a model able to reduce negative transfer.
 
@@
     \hline
-    \multirow{4}{*}{1.0} & 0.50 & \multirow{4}{*}{3.0}  & 28.05\%\\
+    \multirow{6}{*}{1.0} & 0.50 & \multirow{6}{*}{3.0}  & 28.05\%\\
     & 0.55 & & 34.73\% \\
@@
     & 0.65 & & 43.16\% \\
+    & {\bf 0.70} & & {\bf 44.38\%} \\
+    & 0.75 & & 43.87\% \\
     \hline
@@
     A$\to$P & 50.84 & 51.27 & 57.56 & 46.23 & 56.31 & 54.13 & 60.42 & 49.03 & 56.86 & 52.46 & 63.35 & 44.77 \\
-    A$\to$R & ??.?? & ??.?? & ??.?? & ??.?? & 59.88 & 56.60 & 53.18 & 60.65 & 58.86 & 61.67 & 66.82 & 57.26 \\
+    A$\to$R & 27.94 & 68.13 & 17.58 & 52.25 & 59.88 & 56.60 & 53.18 & 60.65 & 58.86 & 61.67 & 66.82 & 57.26 \\
     C$\to$A & 49.52 & 41.74 & 43.10 & 40.47 & 55.28 & 42.63 & 51.57 & 36.33 & 55.76 & 46.84 & 60.19 & 38.35 \\
@@
     P$\to$A & 48.32 & 37.07 & 33.70 & 41.20 & 55.62 & 41.72 & 48.90 & 36.39 & 53.50 & 40.97 & 49.53 & 34.94 \\
-    P$\to$C & 47.76 & 43.99 & 48.42 & 40.31 & 56.77 & 46.10 & 55.11 & 39.65 & ??.?? & ??.?? & ??.?? & ??.?? \\
+    P$\to$C & 47.76 & 43.99 & 48.42 & 40.31 & 56.77 & 46.10 & 55.11 & 39.65 & 58.64 & 46.81 & 60.95 & 37.99 \\
     P$\to$R & 50.37 & 34.14 & 22.88 & 67.27 & 59.68 & 48.41 & 40.91 & 59.30 & 61.10 & 56.22 & 56.89 & 55.58 \\
@@
     \hline
-    AVG     & ??.?? & ??.?? & ??.?? & ??.?? & 52.23 & 49.03 & 51.35 & 49.56 & ??.?? & ??.?? & ??.?? & ??.?? \\ 
+    AVG     & 49.00 & 42.45 & 36.68 & 51.05 & 52.23 & 49.03 & 51.35 & 49.56 & 58.42 & 51.96 & 58.91 & 47.46 \\ 
     \hline

### 2022-02-13 paper/main.tex
Updated Images

@@
 
+\begin{figure}
+  \includegraphics[trim= 0cm 0cm 0cm 0cm, clip, width=\linewidth]{scheme_step1.png}
+  \caption{\label{fig:separation} Schema representing the step 1 training}
+\end{figure}
+
 To perform the target separation we train a CNN iterating on $\tilde{\mathcal{D}_s} = \{({\bf x}_i^s, {\bf \tilde x}_i^s, z_i^s)\}_{i=1}^{N_s}$,
@@
 
-\begin{figure*}
-  \includegraphics[width=\textwidth ]{scheme_step1.png}
-  \caption{\label{fig:separation} Schema representing the step 1 training}
-\end{figure*}
-
-\begin{figure*}
-  \includegraphics[width=\textwidth ]{scheme.png}
-  \caption{\label{fig:separation} Schema representing the target images separation process}
-\end{figure*}
+\begin{figure}[t]
+  \includegraphics[trim= 0cm 0cm 0cm 0cm, clip, width=\linewidth ]{scheme.png}
+  \caption{\label{fig:separation}\centering Schema representing the target images separation process}
+\end{figure}
 
@@
 recall that $\mathcal{L}_{C_2}$ is now computed using the new arranged dataset $\mathcal{D}_s^*$.
+
+\begin{figure}[ht]
+  \includegraphics[trim= 5.2cm 0cm 2cm 0cm, clip, width=\linewidth ]{scheme_step2.png}
+  \caption{\label{fig:step2}\centering Test Caption}
+\end{figure}
 
@@
   \end{subfigure}
-  \caption{\centering\label{figurelabel} HOS values for different parameters. For full reference see appendix \ref{sec:tables}}
+  \caption{\centering\label{fig:hyperparams} HOS values for different parameters. For full reference see appendix \ref{sec:tables}}
 \end{figure}
@@
 As shown in table \ref{tab:results} different architectures give different results, 
-and as shown in table \ref{tab:params} each one requires a different set of parameters.
+and as shown in image \ref{fig:hyperparams} each one requires a different set of parameters.
 To choose optimal parameters a sequential approach is followed, 
@@
 Art $\to$ Clipart and Clipart $\to$ Product.
-In table \ref{tab:ablation_params} we report the steps followed.
-All other settings follow what is reported in \ref{sec:model_parameters}.
-The result here obtained are the same reported in table \ref{tab:params}.
+In appendix \ref{sec:tables} we report the steps followed for each configuration.
 
@@
 
-\newpage
 \appendix
@@
 
-\begin{table}
+\begin{table}[hb!]
   \centering
@@
 
-\begin{table}
+\begin{table}[t!]
+  \vspace{-1.7cm}
   \centering

### 2022-02-13 paper/main.tex
Updated BibTex and Citations

@@
 learning robust cross-domain features and supporting generalization \cite{CarlucciJigsaw,SelfSupervisedXu},
-and also for some Open Set problems specialized in anomaly detection and discriminating anomalous data \cite{bergman2020classificationbased,dectionGeometric}.
+and also for some Open Set problems specialized in anomaly detection and discriminating anomalous data \cite{bergman2020classificationbased,GeoTran}.
 
@@
 In contrast, the presented method uses a Self-Supervised approach, already presented in 
-the recent years by many other works \cite{sun2019unsupervised,saito2020universa,yue2021prototypical}.
+the recent years by many other works \cite{sun2019unsupervised,saito2020universal,yue2021prototypical}.
 using pretext tasks (e.g., image rotation, jigsaw puzzle \cite{CarlucciJigsaw}, mutual information (MI) \cite{selfsupfeng}, instance discrimination \cite{chen2020simple}) to learn high-level feature representation in
@@
 angle pf each image. This pretext task has been successfully used for both anomaly
-detection \cite{golan2018deep} and closed-set domain adaptation \cite{selfsupxu}.
+detection \cite{GeoTran} and closed-set domain adaptation \cite{SelfSupervisedXu}.
 
@@
   \includegraphics[trim= 0cm 0cm 0cm 0cm, clip, width=\linewidth]{scheme_step1.png}
-  \caption{\label{fig:separation} Schema representing the step 1 training}
+  \caption{\label{fig:step1} Schema representing the step 1 training}
 \end{figure}

### 2022-02-13 paper/main.tex
Updated Images
Updated Captions

@@
   \item we introduce a new OSDA metric which properly balances the measure of both the performance on predicting the known classes and the performance on doing the unknown rejection;
-  \item we conduct an extensive ablation over the hyperparameters for different variants of the self-supervised task underlying the benefits of some techniques over others.
+  \item we conduct an extensive ablation over the hyper-parameters for different variants of the self-supervised task underlying the benefits of some techniques over others.
 \end{enumerate}
 
-% Classical machine learning in the past years has made some oversimplified assumptions actually detached % Punteggiatura?
-% from the usage of artificial intelligence systems in everyday real world and the problems they come with.
-
-% The first assumption is that training and test sets come from the same distributions:
-% a model trained on labeled data is expected to perform as well as on the test data.
-% However, this assumption not always holds in real-world applications, 
-% where naively applying the trained model on a new dataset may cause degradation in the performance.
-% To solve this problem Domain Adaptation is widely used, 
-% where the goal is to train a neural network on a source dataset for which labels are available and search for good performance on a target dataset, 
-% which is related to but significantly different from the source dataset, 
-% and whose label or annotation is not available. 
-% Generally this is done by by minimizing the difference between domain distributions and enforcing the recognition of domain invariant patterns in both domains. 
-% As underlined in \cite{domainAdaptFarahani}, 
-% this is usually achieved by mapping source and target data by learning transformations for extracting such features and minimizing the gap between domains in the new representation space in an optimization procedure,
-% while preserving the underlying structure of the original data.
-
-% Secondly, 
-% in real-world classification tasks it is usually difficult to collect training samples to exhaust all classes when training a model.
-% A more realistic scenario is open set recognition (OSR) \cite{OSRsurvey},
-% where incomplete knowledge of the world exists at training time and unknown classes can be injected during testing, 
-% requiring classifiers to not only accurately classify the seen classes but also effectively deal with unseen ones,
-% which would otherwise drastically weaken the robustness of the methods.
-% On the contrary this system should reject unknown classes at test time and separate the known and unknown samples.
-% As underlined by \cite{OSRclassRec}, 
-% existing open-set classifiers rely on deep networks trained in a supervised fashion on known classes in the training set;
-% this causes specialization of learned representations to known classes and makes it hard to distinguish the unknowns from the knowns.
-
-% To solve these significant issues our method is focused on a self-supervised task. 
-% Self-supervised learning is an unsupervised learning technique where the supervised task is created out of the unlabeled input data. 
-% This task could be as simple as predicting the lower half of an image being given the upper half of the same.
-% Supervised learning requires both labeled and high quality data,
-% usually very expensive, 
-% whereas unlabeled data is often readily available in abundance.
-% The fundamental idea behind self-supervised learning is creating some auxiliary task from input data so that,
-% by solving such task,
-% the model can learn the underlying structure of the data,
-% for instance high-level knowledge, correlations, and metadata embedded in the data.
-% This type of learning was recently used for Domain Adaptation, 
-% learning robust cross-domain features and supporting generalization \cite{CarlucciJigsaw,SelfSupervisedXu},
-% and also for some Open Set problems specialized in anomaly detection and discriminating anomalous data \cite{bergman2020classificationbased,dectionGeometric}.
-
-% The approach presented in this paper brings these topics together in the so called Open-Set Domain Adaptation (OSDA) problem. 
-% A two-stage method is hence proposed, 
-% aiming to identify and isolate unknown class samples in the first stage, 
-% before reducing in the second stage the domain gap between the source domain and the known target domain to avoid negative transfer.
-% This is done in both stages using a modified version of the rotation task as self-supervised model,
-% predicting the relative rotation between an image and its rotated version.
-% Finally a classifier is used to predict if each target sample belongs either to one of the knwon classes or to an unknown class, 
-% being rejected in the latter case.
-
-% The method was evaluated on the Office-Home benchmark \cite{OfficeHomeDataset} with a specific OSDA metric.
-
-% {\bf ADD HERE RESULTS AND A BRIEF OF CONCLUSIVE IDEAS (ALSO POSSIBLE FUTURE WORKS)!!}
-
-%------------------------------------------------------------------------
 \section{Related Work}
@@
   \includegraphics[trim= 0cm 0cm 0cm 0cm, clip, width=\linewidth]{scheme_step1.png}
-  \caption{\label{fig:step1} Schema representing the step 1 training}
+  \caption{\label{fig:step1} Schema of the learning process for the model in Step I.}
 \end{figure}
@@
   \includegraphics[trim= 0cm 0cm 0cm 0cm, clip, width=\linewidth ]{scheme.png}
-  \caption{\label{fig:separation}\centering Schema representing the target images separation process}
+  \caption{\label{fig:separation}\centering Schema of the separation process into known and unkown samples on target images}
 \end{figure}
@@
 The training phase is the same as before with the difference that we do not have the center loss this time.
-We also employ a different hyperparameter $\alpha_2$ to weigh the rotation classifier loss contribution.
+We also employ a different hyper-parameter $\alpha_2$ to weigh the rotation classifier loss contribution.
 The objective function is again $\mathcal{L}_2 = \mathcal{L}_{C_2} + \mathcal{L}_{R_2}$,
@@
   \includegraphics[trim= 5.2cm 0cm 2cm 0cm, clip, width=\linewidth ]{scheme_step2.png}
-  \caption{\label{fig:step2}\centering Test Caption}
+  \caption{\label{fig:step2}\centering Schema of the learning process of the model in Step II}
 \end{figure}
@@
 For models using the center loss a centroid learning rate of 0.001 is used.
-The other hyperparameters are analyzed performing an ablation on appendix \ref{sec:tables}.
+The other hyper-parameters are analyzed performing an ablation on appendix \ref{sec:tables}.
 
@@
   \end{subfigure}
-  \caption{\centering\label{fig:hyperparams} HOS values for different parameters. For full reference see appendix \ref{sec:tables}}
+  \caption{\centering\label{fig:hyperparams} HOS values for different hyper-parameters. For full details see appendix \ref{sec:tables}}
 \end{figure}
@@
 {\small
+\nocite{BucciROS}
 \bibliographystyle{ieee_fullname}
@@
 
-This section contains tables \ref{tab:ablationoffoff}, \ref{tab:ablationonoff} and \ref{tab:ablationonon} report the hyperparameters optimization sequence, while tables \ref{tab:results} report the final values for each domain shift with the chosen hyperparameters.
+This section contains tables \ref{tab:ablationoffoff}, \ref{tab:ablationonoff} and \ref{tab:ablationonon} report the hyper-parameters optimization sequence, while tables \ref{tab:results} report the final values for each domain shift with the chosen hyper-parameters.
 
@@
   \end{tabular}
-  \caption{\centering\label{tab:ablationoffoff} Hyperparameters picking process for configuration Multi-Head Off and Center-Loss Off}
+  \caption{\centering\label{tab:ablationoffoff} Hyper-parametr optimization process for configuration Multi-Head Off and Center-Loss Off}
 \end{table}
@@
   \end{tabular}
-  \caption{\centering\label{tab:ablationonoff} Hyperparameters picking process for configuration Multi-Head On and Center-Loss Off}
+  \caption{\centering\label{tab:ablationonoff} Hyper-parameters optimization process for configuration Multi-Head On and Center-Loss Off}
 \end{table}
@@
   \end{tabular}
-  \caption{\centering\label{tab:ablationonon} Hyperparameters picking process for configuration Multi-Head On and Center-Loss On}
+  \caption{\centering\label{tab:ablationonon} Hyper-parameters optimization process for configuration Multi-Head On and Center-Loss On}
 \end{table}
@@
   \end{tabular}
-  \caption{\centering\label{tab:results}Results for each configuration and each domain shift. All values are percentages.}
+  \caption{\centering\label{tab:results}Final results for the three configurations on all domain shifts. All values are percentages.}
 \end{table*}

### 2022-02-13 paper/main.tex
Updated sections

@@
 \usepackage{float}
+\usepackage{url}
 
@@
 Italy\\
-{\tt\small \{s286302,s292477,s292459,292435\}@studenti.polito.it}
+{\tt\small s\{286302,292477,292459,292435\}@studenti.polito.it}
 % For a paper whose authors are all at the same institution,
@@
   Experiments conducted on the Office-Home benchmark show interesting results and method effectiveness.
-
-  % Performance loss over domain change is a common problem in machine learning applications.
-  % Solving the issue usually relies on adapting the model to the new domain by having at disposal large and labeled datasets, either rare or costly to acquire.
-  % In this paper we propose a new approach, adapting models to the new domains while not needing relying on labeled data thanks to a self-supervision.
-  % Experiments conducted on the Office-Home dataset show interesting results and method effectiveness.
+  Full code for our proposed method is made publicly available \url{https://github.com/coccocarmiano/AML2021}
 \end{abstract}
@@
 Generally, this is done by enforcing the learning of domain-invariant patterns of both domains.
-As underlined in \cite{domainAdaptFarahani}, this is usually achieved by learning a transformation function which projects both the source and target domain data in a
-new space where we jointly maintain the underlying structure of the original data while reducing the domain gap by removing the domain-specific information.
 
-Another big issue encountered in real world usages is the presence of additional anomaly semantic classes on the observed data.
-The problem comes under the name of \textit{Open-Set Recognition (OSR)} \cite{OSRsurvey}, where we require not only to accurately classify the known seen classes, but also
-effectively deal with unknown ones, which would otherwise drastically weaken the robustness of the methods.
+Another big issue,
+named {\textit Open-Set Recognition (OSR)} \cite{OSRsurvey},
+features the presence of additional anomalous semantic classes in the observed data and requires to both accurately classify
+known observed samples and also reject the ones from unknown classes.
 
-The jointly presence and accounting of the two described problems has been emerged as a new sub-field of computer vision with the name of \textit{Open-Set Domain Adaptation (OSDA)}.
-As a consequence, if we try to reduce the domain gap between the whole target domain and the source domain, we will observe a negative adaptation due to the unwanted alignment between
-the data belonging to the anomaly semantic classes and the source classes we want to model and predict.
-For this reason, it is important to first perform anomaly detection of the additional set of novelty classes, translating the problem into a \textit{Closed-Set Domain Adaptation (CSDA)} one,
-and next do the alignment between the source and the target domain identified as known.
+The joint presence and accounting of these two problems has been formalized as a new sub-field of computer vision with the name of \textit{Open-Set Domain Adaptation (OSDA)}.
+As a consequence, 
+if we try to reduce the domain gap between the whole target and the source domain, 
+we will observe an unwanted alignment between
+the data belonging to anomalous semantic classes and the source classes we want to model and predict.
+For this reason, 
+it is important to first perform anomaly detection of the additional set of unknown classes
+and then do the alignment between the source and the target domain identified as known
+translating the problem into a \textit{Closed-Set Domain Adaptation (CSDA)} one.
 
 Common machine learning methods usually leverage huge manually annotated datasets to perform well on the given tasks.
-However, acquiring annotated material is usually very costly and difficult, moreover, relying on such data may not be scalable in large applications on the long run.
-Thus, recently, a commonly employed approach is self-supervised learning, which consists in creating new automatically labeled data starting from the original unlabeled data.
-The fundamental idea is creating some auxiliary task from input data so that,
-by solving such task, the model can learn the underlying structure of the data,
-for instance high-level knowledge, correlations, and metadata embedded.
+However, 
+acquiring such data is often very costly and relying on this data may not be scalable in large applications on the long run.
+Recently, 
+a commonly employed approach is self-supervised learning, 
+which consists in creating new automatically labeled data starting from the original unlabeled data.
+The fundamental idea is creating some auxiliary task from input data so that the model can learn the underlying structure of the data,
+such as high-level knowledge, correlations, and metadata embedded.
 This type of learning has been recently used for Domain Adaptation, 
@@
 The approach presented in this paper combines the power of the self-supervised learning with the standard supervised learning approach for semantic class recognition.
-A two-stage method is hence proposed, 
-aiming to identify and isolate unknown class samples in the first stage, 
-before reducing in the second stage the domain gap between the source domain and the known target domain to avoid negative transfer.
-This is done in both stages using a modified version of the rotation task as self-supervised method,
+We propose a two stage method aiming to identify and isolate unknown class samples in the first stage, 
+and reducing the domain gap between domains in the second stage to avoid negative transfer.
+This is done by using a modified version of the rotation task as self-supervised method,
 predicting the relative rotation between an image and its rotated version.
-Finally, a classifier is used to predict if each target sample belongs either to one of the knwon classes or to an unknown class, 
+Finally, a classifier is used to predict if each target sample belongs to either one of the knwon classes or to an unknown class, 
 being rejected in the latter case.
-We evaluate the method on the Office-Home benchmark \cite{OfficeHomeDataset} exploiting a new OSDA metric.
+We evaluate the method on the Office-Home benchmark \cite{OfficeHomeDataset} using a new OSDA metric.
 
@@
 delineate closed from open-set images \cite{ge2017generative, kong2021opengan}.
-Other approaches include reconstruction based methods 
-\cite{yoshihashi2019classificationreconstruction}
-which use poor test-time reconstruction as an open-set indicator.
 
@@
 image colorization \cite{zhang2016colorful},
-image jigsaw puzzle [\cite{noroozi2017unsupervised}, image inpainting \cite{pathak2016context},
-contrastive learning \cite{oord2019representation}, geometric transformations \cite{dosovitskiy2015discriminative}.
+image jigsaw puzzle [\cite{noroozi2017unsupervised}, geometric transformations \cite{dosovitskiy2015discriminative}.
 
@@
 This effect is amplified when also using center loss.
-AUROC values are computed at the end of the separation stage, 
-while HOS values are sampled at regular times on the entire original target dataset.
+AUROC and HOS values are taken at the end of the relative stages.
 
@@
 \label{sec:ablation_study}
-As shown in table \ref{tab:results} different architectures give different results, 
-and as shown in image \ref{fig:hyperparams} each one requires a different set of parameters.
-To choose optimal parameters a sequential approach is followed, 
-by optimizing one parameter at the time.
-The order of optimization followed is: 
-$\alpha_1$, $\lambda_1$, $\mathcal{\tilde N}$, $\alpha_2$.
+Image \ref{fig:hyperparams} summarizes the parameter optimization process where a sequential approach is followed.
+For each configuration one hyper-parameter is optimized at a time,
+following the order
+$\alpha_1$, $\lambda_1$, $\mathcal{\tilde N}$, $\alpha_2$ and picking the parameter giving the highest HOS.
 Models not using center loss just skip the $\lambda_1$ optimization.
@@
 Art $\to$ Clipart and Clipart $\to$ Product.
-In appendix \ref{sec:tables} we report the steps followed for each configuration.
+In appendix \ref{sec:tables} tables \ref{tab:ablationoffoff}, \ref{tab:ablationonoff} and \ref{tab:ablationonon} report all the steps followed for each configuration.
+This information is also summarized in figure \ref{fig:hyperparams}.
+We can notice that most of the optimal parameters are shared between configurations,
+an exception being the normality score $\mathcal{\tilde N}$ on a single-headed configuration.
+This is due to the fact that having to use only one head for all classes it is better to be very confident about classyfing a sample as known.
+Smaller $\alpha_1$ and $\alpha_2$ values are preferred as they avoid overfitting the rotation classifiers as the object classifiers take a longer time to converge.
+As center loss contributions are directly summed to the rotation classifier loss term while being much bigger, 
+much smaller values need to be used for a correct model convergence.
 
@@
 
-The results show that self-supervision technique can help in domain adaptation task and open-set classification tasks.
-A few critical points still remain on our method of study and proposed solution.
-The most important one is probably parameter choosing for different models, as we have seen that variations cause huge differences in results and sequential optimization of parameter is a sub-optimal heuristic.
-Furthermore, having the model to learn two different tasks at once, it could be useful to use a slower learning model at the expense of longer training times.
-Another observation that we can make based 
-on gathered data is the impact that the threshold 
-choice have during the target separation step.
-This is ascrivable to a weak normality score 
-that may need particular attention in order to develop
-a model able to reduce negative transfer.
+The results show that self-supervision technique can help in domain adaptation task and open-set classification tasks,
+but some critical points still remain in our method of study and proposed solution.
+The most important one is probably the parameter optimization method for different models,
+as small variations can cause huge differences in results sequentially optimizing hyper-parameters is a sub-optimal heuristic.
+Furthermore,
+having models learn different tasks simultaneosly can lead to instability, 
+so using slower learning models at the expense of longer training times can improve results.
+A criticality is represented by the normality score hyper-parameter:
+model confidence over accepting or rejecting a sample is very thight between known and unknwon samples,
+so a better function do have more spread scores can bring more efficient separation,
+ultimately resulting in a better quality input data in the second step.
+Last,
+center loss function relies on learning centroids based on sample features to predict rotation.
+This formulation requires picking a specific learning rate for such centroids,
+but we didn't run any test on how such learning rate impacts predictions or sample separability.
 
@@
 
-\begin{table}[hb!]
+\begin{table}[h!]
   \centering
@@
 \begin{table}[t!]
-  \vspace{-1.7cm}
+  \vspace{-2cm}
   \centering
@@
 
-\begin{table}[hb!]
+\begin{table}[b!]
   \centering
@@
     & & {\bf 0.6} & & {\bf 49.78\%} \\
+    & & 0.65 & & 47.23\% \\
     \hline
@@
     \hline
-    AVG     & 49.00 & 42.45 & 36.68 & 51.05 & 52.23 & 49.03 & 51.35 & 49.56 & 58.42 & 51.96 & 58.91 & 47.46 \\ 
+    AVG     & 49.00 & 42.45 & 36.68 & 51.05 & 58.23 & 49.03 & 51.35 & 49.56 & 58.42 & 51.96 & 58.91 & 47.46 \\ 
     \hline

### 2022-02-13 paper/main.tex
minor fixes

@@
 In contrast, the presented method uses a Self-Supervised approach, already presented in 
-the recent years by many other works \cite{sun2019unsupervised,saito2020universal,yue2021prototypical}.
+the recent years by many other works \cite{sun2019unsupervised,saito2020universal,yue2021prototypical}
 using pretext tasks (e.g., image rotation, jigsaw puzzle \cite{CarlucciJigsaw}, mutual information (MI) \cite{selfsupfeng}, instance discrimination \cite{chen2020simple}) to learn high-level feature representation in
@@
 
-In the recent years different works to a Self-Supervised solution, used also in the 
+In the recent years different works have landed to a Self-Supervised solution, used also in the 
 presented method, engaging in learning invariant representations to the 
@@
 image colorization \cite{zhang2016colorful},
-image jigsaw puzzle [\cite{noroozi2017unsupervised}, geometric transformations \cite{dosovitskiy2015discriminative}.
+image jigsaw puzzle \cite{noroozi2017unsupervised}, geometric transformations \cite{dosovitskiy2015discriminative}.
 
@@
 are rotated by multiples of 90° and the network is trained to predict the rotation
-angle pf each image. This pretext task has been successfully used for both anomaly
+angle of each image. This pretext task has been successfully used for both anomaly
 detection \cite{GeoTran} and closed-set domain adaptation \cite{SelfSupervisedXu}.
@@
 Back-Propagation (OSBP) \cite{saito2018open} as an adversarial method 
-to increase the prediction variances so that the generator can choose if accept Ornot a target saple.
+to increase the prediction variances so that the generator can choose if accept or not a target saple.
 Separate To Adapt (STA) \cite{sat} train a multi-binary classifier to progressively 
@@
 the problem of predicting the relative orientation becomes more difficult.
+
 The application of the rotation recognition pre-text task allows to effectively favor and force the model to learn

### 2022-02-13 paper/main.tex
minor fixes 2
minor fixes 3

@@
 Models not using center loss just skip the $\lambda_1$ optimization.
-Ablation study were run on two domain shifts, 
-Art $\to$ Clipart and Clipart $\to$ Product.
+Ablation study were run and averaged on two domain shifts, 
+Art $\to$ Clipart and Product $\to$ Clipart.
 In appendix \ref{sec:tables} tables \ref{tab:ablationoffoff}, \ref{tab:ablationonoff} and \ref{tab:ablationonon} report all the steps followed for each configuration.
@@
 an exception being the normality score $\mathcal{\tilde N}$ on a single-headed configuration.
-This is due to the fact that having to use only one head for all classes it is better to be very confident about classyfing a sample as known.
+This is due to the fact that having to use only one head for all classes it is better to be very confident about classifying a sample as known.
 Smaller $\alpha_1$ and $\alpha_2$ values are preferred as they avoid overfitting the rotation classifiers as the object classifiers take a longer time to converge.
@@
 
-\section{Future Work}
+\section{Future Work and conclusions}
 \label{sec:future_work}

### 2022-02-13 paper/main.tex
Implementation fixes and minor fixes

@@
   \item we introduce a new OSDA metric which properly balances the measure of both the performance on predicting the known classes and the performance on doing the unknown rejection;
-  \item we conduct an extensive ablation over the hyper-parameters for different variants of the self-supervised task underlying the benefits of some techniques over others.
+  \item we conduct an extensive ablation over the hyperparameters for different variants of the self-supervised task underlying the benefits of some techniques over others.
 \end{enumerate}
@@
 The training phase is the same as before with the difference that we do not have the center loss this time.
-We also employ a different hyper-parameter $\alpha_2$ to weigh the rotation classifier loss contribution.
+We also employ a different hyperparameter $\alpha_2$ to weigh the rotation classifier loss contribution.
 The objective function is again $\mathcal{L}_2 = \mathcal{L}_{C_2} + \mathcal{L}_{R_2}$,
@@
 so the training process needs to be speeded up.
-Moreover, we set a learning rate 10 times lower for the feature extractor weights.
+Moreover, we set a learning rate 10 times lower for the weights of the feature extractor and $C_{1/2}$.
 We also decrease the learning rate using a step learning rate scheduler, which reduces it by a factor of 10 after 90\% of total epochs.
@@
 For models using the center loss a centroid learning rate of 0.001 is used.
-The other hyper-parameters are analyzed performing an ablation on appendix \ref{sec:tables}.
+The other hyperparameters are analyzed performing an ablation on them,
+details can be found on the section \ref{sec:ablation_study} and the results of the ablation are
+reported on appendix \ref{sec:tables}.
 
@@
 {\it Classifier $R_1$, $R_2$}: 
-they are composed by a linear layer $1024\to 256$, followed by a batch normalization layer and a leaky relu activation.
+they are seen as discriminators composed by a linear layer $1024\to 256$,
+followed by a batch normalization layer and a leaky relu activation.
 The last layer is then a linear one for the actual classification $256\to 4$.
-The 256-dimensional output are the features used by the center loss for inferring class centroids.
+In the case of multi-head rotation classifier,
+the discriminator is then composed of $|\mathcal{C}_s|$ different linear layers, both for the first and the last one.
+Moreover, the 256-dimensional output are the features used by the center loss for inferring class centroids.
 $R_2$ is always a single-head classifier, even if using a multi-head rotation classifier.
@@
   \end{subfigure}
-  \caption{\centering\label{fig:hyperparams} HOS values for different hyper-parameters. For full details see appendix \ref{sec:tables}}
+  \caption{\centering\label{fig:hyperparams} HOS values for different hyperparameters. For full details see appendix \ref{sec:tables}}
 \end{figure}
@@
 Image \ref{fig:hyperparams} summarizes the parameter optimization process where a sequential approach is followed.
-For each configuration one hyper-parameter is optimized at a time,
+For each configuration one hyperparameter is optimized at a time,
 following the order
@@
 The most important one is probably the parameter optimization method for different models,
-as small variations can cause huge differences in results sequentially optimizing hyper-parameters is a sub-optimal heuristic.
+as small variations can cause huge differences in results sequentially optimizing hyperparameters is a sub-optimal heuristic.
 Furthermore,
@@
 so using slower learning models at the expense of longer training times can improve results.
-A criticality is represented by the normality score hyper-parameter:
+A criticality is represented by the normality score hyperparameter:
 model confidence over accepting or rejecting a sample is very thight between known and unknwon samples,
@@
 
-This section contains tables \ref{tab:ablationoffoff}, \ref{tab:ablationonoff} and \ref{tab:ablationonon} report the hyper-parameters optimization sequence, while tables \ref{tab:results} report the final values for each domain shift with the chosen hyper-parameters.
+This section contains tables \ref{tab:ablationoffoff}, \ref{tab:ablationonoff} and \ref{tab:ablationonon} report the hyperparameters optimization sequence, while tables \ref{tab:results} report the final values for each domain shift with the chosen hyperparameters.
 
@@
   \end{tabular}
-  \caption{\centering\label{tab:ablationoffoff} Hyper-parametr optimization process for configuration Multi-Head Off and Center-Loss Off}
+  \caption{\centering\label{tab:ablationoffoff} Hyperparametr optimization process for configuration Multi-Head Off and Center-Loss Off}
 \end{table}
@@
   \end{tabular}
-  \caption{\centering\label{tab:ablationonoff} Hyper-parameters optimization process for configuration Multi-Head On and Center-Loss Off}
+  \caption{\centering\label{tab:ablationonoff} Hyperparameters optimization process for configuration Multi-Head On and Center-Loss Off}
 \end{table}
@@
   \end{tabular}
-  \caption{\centering\label{tab:ablationonon} Hyper-parameters optimization process for configuration Multi-Head On and Center-Loss On}
+  \caption{\centering\label{tab:ablationonon} Hyperparameters optimization process for configuration Multi-Head On and Center-Loss On}
 \end{table}

### 2022-02-13 paper/main.tex
center loss statement and minor fixes

@@
 The method and its effectiveness is further illustrated in \cite{OldROS},
-and further improvements will be discussed in \ref{sec:future_work}.
+and further possible improvements will be discussed in section \ref{sec:future_work}.
 
@@
 $||\cdot||_2^2$ is the $l$-2 norm and $\lambda$ is the weight associated with the center loss term.
+The additional center loss contribution should favor the learning of hidden features which have
+a smaller intra-class variance, resulting in a more discriminative representation
+when combined with the standard cross-entropy loss,
+which in contrast tries to enlarge the distance between the means of the classes.
 
@@
 All models are trained for 50 epochs for the step one and for 25 epochs for the step two.
-For models using the center loss a centroid learning rate of 0.001 is used.
+For models using the center loss, a centroid learning rate of 0.001 is used.
 The other hyperparameters are analyzed performing an ablation on them,
@@
 {\it Classifier $R_1$, $R_2$}: 
-they are seen as discriminators composed by a linear layer $1024\to 256$,
+they are seen as discriminators composed by a linear layer ($1024\to 256$),
 followed by a batch normalization layer and a leaky relu activation.
-The last layer is then a linear one for the actual classification $256\to 4$.
+The last layer is then a linear one for the actual classification ($256\to 4$).
 In the case of multi-head rotation classifier,
@@
 Moreover, the 256-dimensional output are the features used by the center loss for inferring class centroids.
-$R_2$ is always a single-head classifier, even if using a multi-head rotation classifier.
+$R_2$ is always a single-head discriminator, even if using the multi-head variant.
 

### 2022-02-13 paper/main.tex
center loss restatement

@@
 and reducing the domain gap between domains in the second stage to avoid negative transfer.
+A schematic view of the stages can be seen in figures \ref{fig:step1}, \ref{fig:separation}, \ref{fig:step2}.
 This is done by using a modified version of the rotation task as self-supervised method,
@@
 $||\cdot||_2^2$ is the $l$-2 norm and $\lambda$ is the weight associated with the center loss term.
-The additional center loss contribution should favor the learning of hidden features which have
+The additional center loss contribution should favor having hidden features which have
 a smaller intra-class variance, resulting in a more discriminative representation

### 2022-02-13 paper/main.tex
results and ablation

@@
 \label{sec:results}
+
+\begin{figure}[!t]
+  \centering
+  \includegraphics[trim= 0cm 0cm 0cm 0cm, clip, width=0.8\linewidth]{results_bars.png}
+  \caption{\label{fig:results} HOS values of the different configurations over different domain shifts.}
+\end{figure}
+
+Figure \ref{fig:results} and table \ref{tab:results} summarize the performance, in terms of HOS values,
+obtained using different model configurations; in particular, we analyze the different combinations
+of having a multihead discriminator and the center loss additional contribution.
+The hyperparameters used for each model configuration are the best obtained from the ablation
+discussed in section \ref{sec:ablation_study}.
+Moreover, we report the results obtained for all the 12 available domain shifts,
+as well as the average value to have an overall performance comparison.
+As can be seen, models with a multi-head discriminator obtain better AUROC values,
+resulting in a better separability and consequently in a better domain adaptation.
+Furthermore, we notice an additional improvement with the additional center loss contribution,
+showing that it effectively improves the discriminability of the hidden features in the learning process.
+
+\subsection{Ablation Study}
+\label{sec:ablation_study}
+
 \begin{figure}[!htb]
@@
   \end{subfigure}
-  \caption{\centering\label{fig:hyperparams} HOS values for different hyperparameters. For full details see appendix \ref{sec:tables}}
+  \caption{\centering\label{fig:hyperparams} Ablation HOS values for different hyperparameters and model configurations. For the full details see appendix \ref{sec:tables}.}
 \end{figure}
 
-Table \ref{tab:results} contains the results for all 12 available domain shifts,
-as well as perfomance differences when using multi-head rotation classifiers and center loss,
-as described in the previous section.
-Multi-headed models are more capable of correctly discriminating between known and unknown samples,
-ultimately resulting in better domain alignment.
-This effect is amplified when also using center loss.
-AUROC and HOS values are taken at the end of the relative stages.
+We are now interested in conducting an ablation over the different hyperparameters for the different model configurations.
+In section \ref{sec:implementation_details} we have already discussed the architecture and the learning process,
+we thus proceed to sweep different values for all the hyperparameters to see how it affects the model performance in terms of HOS values.
+Given a specific configuration of hyperparameters values, we run the model for two domain shifts,
+Art $\to$ Clipart and Product $\to$ Clipart, and then we average the HOS values to obtain a more reliable estimate.
+We want to stress that all the hyperparameters might be highly correlated;
+therefore, a gridsearch approach would be necessary.
+However, we decide to keep a sequential ablation study,
+analyzing the effectiveness of each hyperparameter in a specific order:
+$\alpha_1$, $\lambda$, $\mathcal{\tilde N}$, $\alpha_2$.
+Once the ablation for a hyperparameter is finished,
+we fix the best value to analyze the subsequent hyperparameters.
+Image \ref{fig:hyperparams} summarizes the results of the ablation,
+while the tables containing the values can be found in appendix \ref{sec:tables}.
+First, we can observe that the performance of each hyperparameter follows a very similar trend
+indipendently from the chosen model configuration.
+An exception is the selection of a good threshold $\mathcal{\tilde N}$ to perform the
+target separation. We can see that for the configuration with a single-head and without
+the center loss contribution, it is required a larger value.
+We hypothesize that this happens as the single-head is not adequate
+to model the rotation of a large number of semantic classes.
+Infact, the model tends to give higher and less discriminant normality scores,
+achieving a worse AUROC value and performing a bad separation.
 
-\subsection{Ablation Study}
-\label{sec:ablation_study}
-Image \ref{fig:hyperparams} summarizes the parameter optimization process where a sequential approach is followed.
-For each configuration one hyperparameter is optimized at a time,
-following the order
-$\alpha_1$, $\lambda_1$, $\mathcal{\tilde N}$, $\alpha_2$ and picking the parameter giving the highest HOS.
-Models not using center loss just skip the $\lambda_1$ optimization.
-Ablation study were run and averaged on two domain shifts, 
-Art $\to$ Clipart and Product $\to$ Clipart.
-In appendix \ref{sec:tables} tables \ref{tab:ablationoffoff}, \ref{tab:ablationonoff} and \ref{tab:ablationonon} report all the steps followed for each configuration.
-This information is also summarized in figure \ref{fig:hyperparams}.
-We can notice that most of the optimal parameters are shared between configurations,
-an exception being the normality score $\mathcal{\tilde N}$ on a single-headed configuration.
-This is due to the fact that having to use only one head for all classes it is better to be very confident about classifying a sample as known.
-Smaller $\alpha_1$ and $\alpha_2$ values are preferred as they avoid overfitting the rotation classifiers as the object classifiers take a longer time to converge.
-As center loss contributions are directly summed to the rotation classifier loss term while being much bigger, 
-much smaller values need to be used for a correct model convergence.
+Smaller values of $\alpha_1$ and $\alpha_2$ are preferred as they avoid a too fast training convergence for the rotation classifier
+w.r.t the object classifier.
+Moreover, we notice that picking the right value for $\alpha_2$ provides a good improvement.
+As the center loss contribution is directly summed to the rotation classifier loss term,
+we need to pick sufficiently small values of $\lambda$ to avoid
+that it becomes too preponderant, making impossible the learning of the rotation task.
 
-\section{Future Work and conclusions}
+To sum up, we can state that different values of hyperparameters provide an unneglectable performance improvement,
+making the choice of the correct values important for the method effectiveness.
+
+\section{Future work and conclusions}
 \label{sec:future_work}
 
-The results show that self-supervision technique can help in domain adaptation task and open-set classification tasks,
+The results show that self-supervision techniques can be applied effectively in domain adaptation tasks and open-set classification tasks,
 but some critical points still remain in our method of study and proposed solution.
@@
 
-%%%%%%%%% REFERENCES
-{\small
-\nocite{BucciROS}
-\bibliographystyle{ieee_fullname}
-\bibliography{egbib}
-}
+\appendix
 
-\appendix
 \section{Tables}
@@
     \hline
-    $\alpha_1$ & $\lambda_1$ & $\mathcal{\tilde N}$ & $\alpha_2$ & HOS$_{mean}$ \\
+    $\alpha_1$ & $\lambda$ & $\mathcal{\tilde N}$ & $\alpha_2$ & HOS$_{mean}$ \\
     \hline
@@
     \hline
-    \multicolumn{5}{||c||}{Picking $\lambda_1$} \\
+    \multicolumn{5}{||c||}{Picking $\lambda$} \\
     \hline
@@
     \hline
-    AVG     & 49.00 & 42.45 & 36.68 & 51.05 & 58.23 & 49.03 & 51.35 & 49.56 & 58.42 & 51.96 & 58.91 & 47.46 \\ 
+    AVG     & 49.00 & 42.45 & 36.68 & 51.05 & 58.23 & 49.03 & 51.35 & 49.56 & {\bf 58.42} & {\bf 51.96} & 58.91 & 47.46 \\ 
     \hline
@@
 
+\clearpage
+%%%%%%%%% REFERENCES
+{\small
+\nocite{BucciROS}
+\bibliographystyle{ieee_fullname}
+\bibliography{egbib}
+}
+
 \end{document}

### 2022-02-13 paper/main.tex
future works and further adjustments

@@
 
-The results show that self-supervision techniques can be applied effectively in domain adaptation tasks and open-set classification tasks,
-but some critical points still remain in our method of study and proposed solution.
-The most important one is probably the parameter optimization method for different models,
-as small variations can cause huge differences in results sequentially optimizing hyperparameters is a sub-optimal heuristic.
+The achieved results show that self-supervision techniques can be applied effectively in domain adaptation tasks and open-set classification tasks.
+We propose a method which leverages the self-supervision power to address the two challenges exploiting the relative rotation prediction task,
+by first separating the target domain into a known and unknown part, and then by performing the domain alignment.
+Moreover, we propose a new metric to evaluate OSDA systems, HOS, which is the harmonic mean between
+the accuracy on the target known samples and the accuracy on rejecting the unknown ones.
+
+Some critical points still remain in our method of study and in our proposed solution.
+One point is the hyperparameters ablation method for different models,
+as small variations can cause huge differences in results due to
+the sequential optimization of hyperparameters.
 Furthermore,
@@
 so using slower learning models at the expense of longer training times can improve results.
-A criticality is represented by the normality score hyperparameter:
-model confidence over accepting or rejecting a sample is very thight between known and unknwon samples,
-so a better function do have more spread scores can bring more efficient separation,
-ultimately resulting in a better quality input data in the second step.
-Last,
-center loss function relies on learning centroids based on sample features to predict rotation.
-This formulation requires picking a specific learning rate for such centroids,
-but we didn't run any test on how such learning rate impacts predictions or sample separability.
+A huge criticality is represented by the normality score function,
+as simply picking the rotation prediction confidence (maximum predicted probability)
+does not provide a very discriminant score between images belonging to a known class
+and images of unknown classes.
+A better normality score function should take into considerations other factors to result in a more discriminant score.
+It is worth noting that the separation goodness influences the quality of the input material for the second step,
+resulting to be an extremely critical part for the effectiveness of the method.
+Lastly, the self-supervision task effectiveness also depends on the model architecture,
+as, for example, deeper architectures can result in a better or worse learning
+of domain-independent features, as underlined in \cite{OldROS}.
 
@@
 
-This section contains tables \ref{tab:ablationoffoff}, \ref{tab:ablationonoff} and \ref{tab:ablationonon} report the hyperparameters optimization sequence, while tables \ref{tab:results} report the final values for each domain shift with the chosen hyperparameters.
+This section contains the tables \ref{tab:ablationoffoff}, \ref{tab:ablationonoff} and \ref{tab:ablationonon}
+reporting the values of hyperparameters analyzed during the ablation,
+while the table \ref{tab:results} contains the values of the final models using the best hyperparameters,
+for each domain shift.
 
@@
 
-\begin{table}[t!]
+\begin{table}[h!]
   \vspace{-2cm}
@@
 
-\begin{table}[b!]
+\begin{table}[h!]
   \centering
